% !TEX program = pdflatex
\documentclass[11pt]{article}

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage[a4paper,margin=28mm,headheight=14pt]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{enumitem}
\usepackage{array,booktabs,longtable}
\usepackage{listings}
\usepackage{xcolor}
\usepackage{xurl}
\usepackage{hyperref}
\usepackage{fancyhdr}

\definecolor{linkblue}{RGB}{24,78,119}
\definecolor{citegreen}{RGB}{36,104,71}
\hypersetup{
  colorlinks=true,
  linkcolor=linkblue,
  citecolor=citegreen,
  urlcolor=linkblue,
  pdftitle={A Dirichlet Polya Inequality for Three-Dimensional Spherical Shells},
  pdfsubject={Self-contained review draft},
  pdfkeywords={Polya conjecture, Dirichlet Laplacian, spherical shell, eigenvalue counting}
}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\small Dirichlet P\'olya inequality for spherical shells}
\fancyhead[R]{\small Self-contained review draft}
\fancyfoot[C]{\thepage}
\fancypagestyle{plain}{%
  \fancyhf{}%
  \fancyhead[L]{\small Dirichlet P\'olya inequality for spherical shells}%
  \fancyhead[R]{\small Self-contained review draft}%
  \fancyfoot[C]{\thepage}%
}
\fancypagestyle{titlepage}{%
  \fancyhf{}%
  \fancyfoot[C]{\thepage}%
  \renewcommand{\headrulewidth}{0pt}%
}

\numberwithin{equation}{section}
\allowdisplaybreaks[2]
\setlist{itemsep=0.25em,topsep=0.45em}
\setlength{\emergencystretch}{3em}
\lstset{
  basicstyle=\ttfamily\scriptsize,
  columns=fullflexible,
  breaklines=true,
  breakatwhitespace=false,
  keepspaces=true,
  showstringspaces=false,
  frame=single,
  xleftmargin=0.5em,
  xrightmargin=0.5em
}

\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\R}{\mathbb R}
\newcommand{\N}{\mathbb N}
\newcommand{\Nzero}{\mathbb N_0}
\DeclareMathOperator{\arsinh}{arsinh}

\title{A Dirichlet P\'olya Inequality for\\Three-Dimensional Spherical Shells\\[0.4em]
\large Self-contained proof and certification manuscript}
\author{}
\date{15 July 2026}

\begin{document}

\maketitle
\thispagestyle{titlepage}

\begin{quote}
\small
\textbf{Scope and status.}
This manuscript proves a theorem for the class of genuine three-dimensional
spherical shells.  It does not claim the general P\'olya conjecture,
literature novelty, or priority.  All shell-specific analytic reductions,
regional arguments, seam assignments, exact constants, and the mathematical
contracts for the finite interval computations are stated in this single
file.  The imported background and analytic results are explicitly identified
standard Sturm--Liouville and Bessel facts and published phase, Bessel-zero,
and one-dimensional floor-sum inequalities, each quoted with its precise scope.
\end{quote}

\begin{abstract}
For \(0<r<R\), let
\[
  A_{r,R}=\{x\in\R^3:r<|x|<R\}.
\]
We prove, with the strict Dirichlet counting convention, that
\[
  N_D(A_{r,R},\Lambda)
  \le L_3|A_{r,R}|\Lambda^{3/2},
  \qquad
  L_3=\frac1{6\pi^2},
  \qquad \Lambda\ge0.
\]
The proof separates variables, converts the radial spectrum into a strict
multiplicity-weighted phase count, and combines analytic endpoint estimates,
finite angular and radial mode inventories, and a rigorously certified final
compact window.  We also give an elementary proof that no genuine spherical
shell tiles \(\R^3\) by congruent rigid-motion copies with disjoint interiors,
under either exact or almost-everywhere coverage.
\end{abstract}

\tableofcontents
\clearpage

\section{Main results and conventions}

The eigenvalues of the Dirichlet Laplacian on a bounded domain \(\Omega\) are
listed with multiplicity as
\[
  0<\lambda_1^D(\Omega)\le\lambda_2^D(\Omega)\le\cdots.
\]
Throughout we use the strict counting function
\begin{equation}
  N_D(\Omega,\Lambda)
  :=\#\{j:\lambda_j^D(\Omega)<\Lambda\}.
  \label{eq:strict-count}
\end{equation}
This convention matters at every spectral wall.  We write
\(\N=\{1,2,3,\ldots\}\) and \(\Nzero=\{0,1,2,\ldots\}\).

\begin{theorem}[Spectral inequality]
\label{thm:spectral}
For every \(0<r<R\) and every \(\Lambda\ge0\),
\begin{equation}
  \boxed{
  N_D(A_{r,R},\Lambda)
  \le \frac{2}{9\pi}(R^3-r^3)\Lambda^{3/2}
  =L_3|A_{r,R}|\Lambda^{3/2},
  \qquad L_3=\frac1{6\pi^2}.}
  \label{eq:main-theorem}
\end{equation}
\end{theorem}

\begin{theorem}[Non-tiling]
\label{thm:nontiling}
For every \(0<r<R\), no family of congruent rigid-motion copies of
\(A_{r,R}\) has pairwise-disjoint interiors and covers \(\R^3\) exactly or
up to a three-dimensional Lebesgue-null set.  The same conclusion holds when
coverage is formulated using closed shells.
\end{theorem}

The two theorems concern literally the same complete shell family.
Theorem~\ref{thm:nontiling} is logically independent of the spectral proof.

% Self-contained manuscript fragment: separated spectrum, phase reduction,
% weighted lattice reduction, and the small-hole endpoint.
% Assumes amsmath, amssymb, amsthm, mathtools and theorem environments
% theorem, proposition, lemma.

\section{Separated spectrum, phase reduction, and the small-hole endpoint}
\label{sec:sc-spectrum-small-hole}

Throughout this section
\[
  A_{\rho,1}=\{x\in\mathbb R^3:\rho<|x|<1\},
  \qquad 0<\rho<1,
\]
and the Dirichlet counting function is strict:
\[
  N_D(A_{\rho,1},K^2)
  :=\#\{j:\lambda_j^D(A_{\rho,1})<K^2\}.
\]
For \(x>0\) we use the strict positive-integer count
\begin{equation}
  [x]_<:=\#\{n\in\mathbb N:n<x\}
  =\max\{0,\lceil x\rceil-1\}.
  \label{eq:sc-strict-bracket}
\end{equation}
Thus \([m]_< =m-1\) for \(m\in\mathbb N\).  This convention is retained
at every eigenfrequency, phase level, and half-integer angular wall.

\subsection{The exact separated spectrum}

Let \(H_\rho=-\Delta^D_{A_{\rho,1}}\) be the Friedrichs operator associated
with
\[
  \mathfrak q[f]=\int_{A_{\rho,1}}|\nabla f|^2\,dx,
  \qquad D(\mathfrak q)=H_0^1(A_{\rho,1}).
\]
Choose an orthonormal spherical-harmonic basis satisfying
\[
  -\Delta_{\mathbb S^2}Y_{\ell m}
  =\ell(\ell+1)Y_{\ell m},
  \qquad \ell\in\mathbb N_0,
  \quad -\ell\le m\le\ell.
\]

\begin{proposition}[Unitary decomposition and completeness]
\label{prop:sc-separated-spectrum}
For
\[
  L_\ell=-\frac{d^2}{dr^2}+\frac{\ell(\ell+1)}{r^2},
  \qquad
  D(L_\ell)=H^2(\rho,1)\cap H_0^1(\rho,1),
\]
one has the unitary equivalence
\begin{equation}
  H_\rho\simeq
  \bigoplus_{\ell=0}^{\infty}
  \bigoplus_{m=-\ell}^{\ell}L_\ell.
  \label{eq:sc-operator-sum}
\end{equation}
The exact form domain on the right is
\begin{equation}
  \left\{(u_{\ell m}):
  \begin{array}{l}
  u_{\ell m}\in H_0^1(\rho,1),\\
  \displaystyle
  \sum_{\ell,m}\left(\|u_{\ell m}\|_2^2
  +\mathfrak a_\ell[u_{\ell m}]\right)<\infty
  \end{array}\right\},
  \label{eq:sc-global-form-domain}
\end{equation}
where
\[
  \mathfrak a_\ell[u]
  =\int_\rho^1\left(|u'|^2
  +\frac{\ell(\ell+1)}{r^2}|u|^2\right)dr.
\]
The exact operator domain is
\begin{equation}
  \left\{(u_{\ell m}):
  \begin{array}{l}
  u_{\ell m}\in D(L_\ell),\\
  \displaystyle
  \sum_{\ell,m}\left(\|u_{\ell m}\|_2^2
  +\|L_\ell u_{\ell m}\|_2^2\right)<\infty
  \end{array}\right\}.
  \label{eq:sc-global-operator-domain}
\end{equation}
Each \(L_\ell\) has positive, simple eigenvalues tending to infinity and a
complete orthonormal eigenbasis.  The full operator has compact resolvent.
\end{proposition}

\begin{proof}
Write \(x=r\omega\), so \(dx=r^2\,dr\,d\omega\), and set
\[
  R_{\ell m}(r)=\int_{\mathbb S^2}
  f(r,\omega)\overline{Y_{\ell m}(\omega)}\,d\omega,
  \qquad u_{\ell m}(r)=rR_{\ell m}(r).
\]
Fubini, Tonelli, and Parseval on \(\mathbb S^2\) give
\[
  \|f\|_{L^2(A_{\rho,1})}^2
  =\sum_{\ell,m}\int_\rho^1|R_{\ell m}(r)|^2r^2\,dr
  =\sum_{\ell,m}\int_\rho^1|u_{\ell m}(r)|^2\,dr.
\]
Conversely, if \((u_{\ell m})\) is square summable, the finite sums
\[
  f_L(r,\omega)=\frac1r
  \sum_{\ell\le L}\sum_{m=-\ell}^{\ell}
  u_{\ell m}(r)Y_{\ell m}(\omega)
\]
are Cauchy in \(L^2(A_{\rho,1})\), and their limit maps back to the given
family.  Hence the coefficient map is unitary onto the Hilbert direct sum.
Because \(r,1/r\in W^{1,\infty}(\rho,1)\), multiplication by either function
is bounded on \(H^1(\rho,1)\) and preserves the two zero endpoint traces.

For a finite smooth harmonic expansion, polar coordinates and angular
orthogonality yield
\[
  \mathfrak q[f]=\sum_{\ell,m}\int_\rho^1
  \left(r^2|R_{\ell m}'|^2
  +\ell(\ell+1)|R_{\ell m}|^2\right)dr.
\]
If \(u=rR\), then
\[
  r^2|R'|^2
  =\left|u'-\frac ur\right|^2
  =|u'|^2-\frac{(|u|^2)'}r+\frac{|u|^2}{r^2}.
\]
Since
\[
  \frac{(|u|^2)'}r
  =\left(\frac{|u|^2}{r}\right)'
  +\frac{|u|^2}{r^2}
\]
and \(u(\rho)=u(1)=0\), integration gives
\[
  \int_\rho^1r^2|R'|^2\,dr
  =\int_\rho^1|u'|^2\,dr.
\]
The angular term becomes
\(\ell(\ell+1)|u|^2/r^2\).  Closing finite harmonic expansions in the
form norm proves \eqref{eq:sc-global-form-domain}: one inclusion follows
from componentwise form convergence and Fatou's lemma, while the reverse
inclusion follows by first truncating the square-summable family in
\((\ell,m)\) and then approximating its finitely many components by
\(C_c^\infty(\rho,1)\).  The uniqueness theorem for operators associated
with closed semibounded forms gives \eqref{eq:sc-operator-sum}.

For fixed \(\ell\), the potential \(\ell(\ell+1)/r^2\) is continuous and
bounded on \([\rho,1]\).  The regular one-dimensional Dirichlet form
therefore has associated operator \(L_\ell\) with the displayed
\(H^2\cap H_0^1\) domain.  The standard domain formula for an orthogonal
operator sum gives \eqref{eq:sc-global-operator-domain}.

The embedding \(H_0^1(\rho,1)\hookrightarrow L^2(\rho,1)\) is compact, so
every block has compact resolvent.  To pass to the infinite direct sum, note
that \(r\le1\) implies
\[
  L_\ell\ge\ell(\ell+1),
  \qquad
  \|(L_\ell+1)^{-1}\|
  \le\frac1{1+\ell(\ell+1)}.
\]
The resolvent of the full operator is consequently the operator-norm limit
of its finite-\(\ell\) truncations, each of which is compact.  Hence the full
resolvent is compact.

Regular Dirichlet Sturm--Liouville theory gives a complete sequence of
simple eigenvalues in every block.  They are strictly positive because
\[
  \mathfrak a_\ell[u]\ge\int_\rho^1|u'|^2\,dr
  \ge\frac{\pi^2}{(1-\rho)^2}\|u\|_2^2.
\]
Simplicity also follows directly: two solutions of the same second-order
equation that vanish at \(r=\rho\) have proportional initial derivatives
and hence are proportional by uniqueness.  If \(u_{\ell,n}\) is a complete
radial eigenbasis, then
\[
  \frac{u_{\ell,n}(r)}rY_{\ell m}(\omega)
\]
over all \((\ell,m,n)\) is exactly the inverse image of a complete
orthonormal coordinate basis of the Hilbert direct sum.  This proves global
completeness.
\end{proof}

\begin{proposition}[Bessel determinant and strict phase enumeration]
\label{prop:sc-bessel-phase-count}
Put \(\nu=\ell+\tfrac12\).  The positive eigenfrequencies in the
\(\ell\)-th radial block are precisely the positive zeros of
\begin{equation}
  D_{\nu,\rho}(k)
  :=J_\nu(\rho k)Y_\nu(k)-Y_\nu(\rho k)J_\nu(k).
  \label{eq:sc-bessel-determinant}
\end{equation}
Every such zero is simple.  With the continuous phase branch
\begin{equation}
  J_\nu(x)+iY_\nu(x)=M_\nu(x)e^{i\theta_\nu(x)},
  \qquad M_\nu(x)>0,
  \qquad \theta_\nu(0+)=-\frac\pi2,
  \label{eq:sc-phase-branch}
\end{equation}
and
\[
  \Psi_{\nu,\rho}(K)=\theta_\nu(K)-\theta_\nu(\rho K),
  \qquad
  \gamma_{\rho,K}(\nu)=\frac{\Psi_{\nu,\rho}(K)}\pi,
\]
the exact strict count is
\begin{equation}
  N_D(A_{\rho,1},K^2)
  =\sum_{\ell=0}^{\infty}(2\ell+1)
  [\gamma_{\rho,K}(\ell+\tfrac12)]_<.
  \label{eq:sc-exact-phase-count}
\end{equation}
The sum is finite.  If \(K\) is a radial eigenfrequency in one or several
angular channels, the root at \(K\) is excluded in each such channel and the
excluded angular multiplicities add.
\end{proposition}

\begin{proof}
For \(k>0\), the physical radial equation has the general solution
\[
  R(r)=r^{-1/2}
  \bigl(c_1J_\nu(kr)+c_2Y_\nu(kr)\bigr).
\]
The two Dirichlet conditions admit a nonzero coefficient vector exactly when
\[
  \det\begin{pmatrix}
  J_\nu(\rho k)&Y_\nu(\rho k)\\
  J_\nu(k)&Y_\nu(k)
  \end{pmatrix}=D_{\nu,\rho}(k)=0.
\]
The Wronskian
\begin{equation}
  J_\nu(x)Y_\nu'(x)-J_\nu'(x)Y_\nu(x)=\frac2{\pi x}
  \label{eq:sc-bessel-wronskian}
\end{equation}
shows that the two entries in either row cannot vanish simultaneously.
Thus the determinant criterion remains exact even if the \(J_\nu\) values,
or the \(Y_\nu\) values, happen to vanish at both endpoints.

For root simplicity define the left-normalized solution
\begin{equation}
  s_\ell(r,k)=\frac{\pi\sqrt\rho}{2}\sqrt r
  \left[J_\nu(\rho k)Y_\nu(kr)
  -Y_\nu(\rho k)J_\nu(kr)\right].
  \label{eq:sc-left-normalized}
\end{equation}
Equation \eqref{eq:sc-bessel-wronskian} gives
\[
  s_\ell(\rho,k)=0,
  \qquad \partial_rs_\ell(\rho,k)=1,
  \qquad
  s_\ell(1,k)=\frac{\pi\sqrt\rho}{2}D_{\nu,\rho}(k).
\]
Let \(v=\partial_ks_\ell\).  Differentiating
\((L_\ell-k^2)s_\ell=0\) gives
\[
  (L_\ell-k^2)v=2ks_\ell,
  \qquad v(\rho,k)=\partial_rv(\rho,k)=0.
\]
At a positive determinant root, Lagrange's identity yields
\begin{equation}
  \partial_ks_\ell(1,k)\,\partial_rs_\ell(1,k)
  =2k\int_\rho^1s_\ell(r,k)^2\,dr>0.
  \label{eq:sc-root-simplicity}
\end{equation}
Thus \(\partial_ks_\ell(1,k)\ne0\), and the zero of the determinant is
simple.

At zero energy the left-normalized solution is
\[
  s_\ell(r,0)=
  \frac{\rho^{-\ell}r^{\ell+1}
  -\rho^{\ell+1}r^{-\ell}}{2\ell+1},
\]
so
\[
  s_\ell(1,0)=
  \frac{\rho^{-\ell}-\rho^{\ell+1}}{2\ell+1}>0.
\]
Equivalently, the standard small-argument expansions give
\begin{equation}
  \lim_{k\downarrow0}D_{\nu,\rho}(k)
  =\frac{\rho^{-\nu}-\rho^\nu}{\pi\nu}>0.
  \label{eq:sc-zero-determinant-limit}
\end{equation}
Hence the limiting phase level zero is not an eigenfrequency.

From \eqref{eq:sc-phase-branch},
\[
  J_\nu=M_\nu\cos\theta_\nu,
  \qquad Y_\nu=M_\nu\sin\theta_\nu,
\]
and direct substitution gives the sign-sensitive factorization
\begin{equation}
  D_{\nu,\rho}(k)
  =M_\nu(\rho k)M_\nu(k)
  \sin\Psi_{\nu,\rho}(k).
  \label{eq:sc-determinant-factorization}
\end{equation}
The Wronskian also gives
\[
  \theta_\nu'(x)=\frac2{\pi xM_\nu(x)^2}>0.
\]
Nicholson's integral representation
\[
  M_\nu(x)^2=\frac8{\pi^2}\int_0^\infty
  \cosh(2\nu t)K_0(2x\sinh t)\,dt
\]
and the strict decrease of \(K_0\) imply that \(M_\nu(x)^2\) is strictly
decreasing in \(x\).  Therefore
\begin{equation}
  \Psi_{\nu,\rho}'(k)
  =\frac2{\pi k}
  \left(M_\nu(k)^{-2}-M_\nu(\rho k)^{-2}\right)>0.
  \label{eq:sc-phase-monotonicity}
\end{equation}
The branch condition gives \(\Psi_{\nu,\rho}(0+)=0\), while the standard
large-argument Bessel expansion gives
\[
  \Psi_{\nu,\rho}(k)=(1-\rho)k+O(k^{-1})\longrightarrow\infty
\]
for fixed \(\nu\) and \(\rho\).  Hence the positive determinant roots are
uniquely indexed by
\[
  \Psi_{\ell+1/2,\rho}(k_{\ell,n})=n\pi,
  \qquad n=1,2,\ldots.
\]
Strict monotonicity gives
\[
  k_{\ell,n}<K
  \quad\Longleftrightarrow\quad
  n\pi<\Psi_{\ell+1/2,\rho}(K).
\]
The direct-sum decomposition supplies angular multiplicity \(2\ell+1\).
If the same numerical eigenvalue occurs at distinct values of \(\ell\), the
corresponding spherical-harmonic sectors are orthogonal and their
multiplicities add.  Finally,
\(\lambda_{\ell,n}\ge\ell(\ell+1)\), so only finitely many angular channels
can contribute below \(K^2\).  These observations prove
\eqref{eq:sc-exact-phase-count}, including every strict spectral wall.
\end{proof}

The only standard inputs in the preceding proof are completeness of the
spherical harmonics, regular one-dimensional Dirichlet Sturm--Liouville
theory, the Bessel equation, the Wronskian, Nicholson's representation, and
the usual small- and large-argument Bessel formulas; see \cite{DLMF}.

\subsection{Uniform phase enclosures and the strict lattice proxy}

For \(a>0\), define
\begin{equation}
  G_a(z)=
  \begin{cases}
  \displaystyle\frac1\pi\left(\sqrt{a^2-z^2}
  -z\arccos\frac za\right),&0\le z\le a,\\[1mm]
  0,&z>a.
  \end{cases}
  \label{eq:sc-model-action}
\end{equation}
For \(0\le z<a\), put
\[
  H_a(z)=\frac{3a^2+2z^2}{24\pi(a^2-z^2)^{3/2}},
\]
and define
\begin{equation}
  \mathcal F_a(z)=
  \begin{cases}
  \max\{G_a(z)-H_a(z),-1/4\},&0\le z<a,\\
  -1/4,&z\ge a.
  \end{cases}
  \label{eq:sc-auxiliary-F}
\end{equation}

We use the following published Bessel-phase result, stated here with every
hypothesis needed in the sequel.

\begin{lemma}[External uniform Bessel-phase enclosure]
\label{lem:sc-external-phase}
With the branch \eqref{eq:sc-phase-branch}, for every \(a>0\) and real
\(z\ge0\),
\begin{equation}
  \mathcal F_a(z)-\frac14
  <\frac{\theta_z(a)}\pi
  <G_a(z)-\frac14.
  \label{eq:sc-individual-phase-enclosure}
\end{equation}
If \(0<\mu<K\), \(0\le z\le K\), and
\[
  \Gamma_{K,\mu}(z)
  :=\frac{\theta_z(K)-\theta_z(\mu)}\pi,
\]
then
\begin{equation}
  0<\Gamma_{K,\mu}(z)
  <G_K(z)-\mathcal F_\mu(z)
  \le G_K(z)+\frac14.
  \label{eq:sc-global-difference-enclosure}
\end{equation}
If \(0\le z\le\mu\), including \(z=\mu\), then also
\begin{equation}
  G_K(z)-G_\mu(z)
  <\Gamma_{K,\mu}(z)
  <G_K(z)-G_\mu(z)+\frac14.
  \label{eq:sc-action-difference-enclosure}
\end{equation}
No value of the divergent expression \(H_\mu(\mu)\) is used in the last
statement.
\end{lemma}

Lemma~\ref{lem:sc-external-phase} is Theorem~5.1 and Lemma~5.2 of
\cite{FLPSannuli}, based on the real-order phase enclosures of
\cite{FLPSphase}.  The upper bound in
\eqref{eq:sc-global-difference-enclosure} follows immediately by subtracting
the lower bound for \(\theta_z(\mu)\) from the upper bound for
\(\theta_z(K)\) in \eqref{eq:sc-individual-phase-enclosure}; the correlated
two-sided estimate \eqref{eq:sc-action-difference-enclosure} is the sharper
part of the annulus result.  Both theorems are stated for real order, so the
half-integers \(z=\ell+\tfrac12\) require no interpolation.

Fix now \(K>0\), set \(\mu=\rho K\), and define
\begin{equation}
  A_{\rho,K}(z)=G_K(z)-G_\mu(z).
  \label{eq:sc-shell-action}
\end{equation}
For \(0\le z\le K\), let
\begin{equation}
  s_\mu(z)=
  \begin{cases}
  \min\{H_\mu(z),1/4\},&0\le z<\mu,\\
  1/4,&\mu\le z\le K,
  \end{cases}
  \qquad
  U_{\rho,K}(z)=A_{\rho,K}(z)+s_\mu(z).
  \label{eq:sc-optimized-proxy}
\end{equation}
The second line, rather than \(H_\mu\), is always used at \(z=\mu\).

\begin{proposition}[Strict phase-to-lattice reduction]
\label{prop:sc-phase-lattice}
For \(0<\rho<1\) and \(K>0\),
\begin{equation}
  \gamma_{\rho,K}(z)<U_{\rho,K}(z)
  \le A_{\rho,K}(z)+\frac14,
  \qquad 0\le z\le K.
  \label{eq:sc-pointwise-phase-proxy}
\end{equation}
Because every \(G_a\) is zero-extended, \(A_{\rho,K}\) is the piecewise
action \(G_K-G_{\rho K}\) below the inner interface and \(G_K\) at and
above it.  Consequently,
\begin{align}
  N_D(A_{\rho,1},K^2)
  &\le
  \sum_{\nu_\ell<K}2\nu_\ell
  [U_{\rho,K}(\nu_\ell)]_<
  \label{eq:sc-optimized-spectral-proxy}\\
  &\le
  S_{\rho,K}:=
  \sum_{\nu_\ell<K}2\nu_\ell
  \left\lfloor A_{\rho,K}(\nu_\ell)+\frac14\right\rfloor,
  \qquad \nu_\ell=\ell+\frac12.
  \label{eq:sc-coarse-spectral-proxy}
\end{align}
The cutoff is strict: an order \(\nu_\ell=K\) is inactive.  At a true phase
wall the radial count is one less than the ordinary floor; at a proxy wall
the ordinary floor in \eqref{eq:sc-coarse-spectral-proxy} is retained.
Moreover,
\begin{equation}
  \int_0^\infty2zA_{\rho,K}(z)\,dz
  =\frac{2}{9\pi}(1-\rho^3)K^3.
  \label{eq:sc-exact-action-integral}
\end{equation}
\end{proposition}

\begin{proof}
For \(0\le z<\mu\), the first upper bound in
\eqref{eq:sc-global-difference-enclosure} reads
\[
  \gamma_{\rho,K}(z)
  <A_{\rho,K}(z)+G_\mu(z)-\mathcal F_\mu(z).
\]
From \eqref{eq:sc-auxiliary-F},
\[
  G_\mu(z)-\mathcal F_\mu(z)
  =\min\{H_\mu(z),G_\mu(z)+1/4\}.
\]
The upper half of \eqref{eq:sc-action-difference-enclosure} also gives
\(\gamma_{\rho,K}(z)<A_{\rho,K}(z)+1/4\).  Taking the better of these two
strict upper bounds, and using \(G_\mu(z)+1/4\ge1/4\), gives
\[
  \gamma_{\rho,K}(z)
  <A_{\rho,K}(z)+\min\{H_\mu(z),1/4\}
  =U_{\rho,K}(z).
\]
For \(\mu\le z\le K\), one has \(G_\mu(z)=0\), and
\eqref{eq:sc-global-difference-enclosure} gives
\[
  \gamma_{\rho,K}(z)<G_K(z)+1/4=U_{\rho,K}(z).
\]

Orders \(z\ge K\) do not contribute.  Indeed,
\eqref{eq:sc-individual-phase-enclosure} gives
\[
  \frac{\theta_z(K)}\pi<-\frac14,
  \qquad
  \frac{\theta_z(\mu)}\pi>-\frac12,
\]
because \(G_K(z)=0\) and \(\mathcal F_\mu(z)=-1/4\).  Together with phase
monotonicity this yields
\[
  0<\gamma_{\rho,K}(z)<\frac14<1,
\]
so there is no positive phase level below \(K\).  This includes \(z=K\).

For positive \(x<y\), every positive integer strictly below \(x\) is also
strictly below \(y\), so \([x]_<\le[y]_<\le\lfloor y\rfloor\).  Applying
this observation to the exact phase count
\eqref{eq:sc-exact-phase-count}, and then using
\(s_\mu\le1/4\), proves
\eqref{eq:sc-optimized-spectral-proxy}--
\eqref{eq:sc-coarse-spectral-proxy} without changing either wall
convention.

Finally, scaling \(z=ax\) gives
\[
  \int_0^a2zG_a(z)\,dz
  =\frac{2a^3}{\pi}
  \left(\int_0^1x\sqrt{1-x^2}\,dx
  -\int_0^1x^2\arccos x\,dx\right).
\]
The two elementary integrals are \(1/3\) and \(2/9\), respectively; hence
the last expression is \(2a^3/(9\pi)\).  Subtracting the result with
\(a=\mu=\rho K\) from that with \(a=K\) proves
\eqref{eq:sc-exact-action-integral}.
\end{proof}

The necessity of retaining integerization can be displayed exactly.  Put
\[
  m_K=\max\{0,\lceil K-\tfrac12\rceil\},
  \qquad
  r_\mu=\max\{0,\lceil\mu-\tfrac12\rceil\}.
\]
Thus the active orders are \(\nu_0,\ldots,\nu_{m_K-1}\), and precisely the
first \(r_\mu\) of them lie strictly below \(\mu\).  Define
\[
  E_0(a)=\sum_{\nu_\ell<a}2\nu_\ell G_a(\nu_\ell)
  -\frac{2a^3}{9\pi},
  \qquad
  E_{\mathrm{mp}}(\rho,K)=E_0(K)-E_0(\mu),
\]
\[
  E_{\mathrm{ph}}
  =\sum_{\ell=0}^{r_\mu-1}(2\ell+1)
  \min\{H_\mu(\nu_\ell),1/4\}
  +\frac{m_K^2-r_\mu^2}{4}.
\]
For \(x>0\), define the strict remainder
\[
  \langle x\rangle_<:=x-[x]_<\in(0,1],
\]
so \(\langle m\rangle_<=1\) at positive integer \(m\), and set
\[
  E_{\mathrm{frac}}
  =\sum_{\nu_\ell<K}2\nu_\ell
  \langle U_{\rho,K}(\nu_\ell)\rangle_<.
\]
Expanding \(U=A+s_\mu\) term by term and using
\eqref{eq:sc-exact-action-integral} gives the exact identity
\begin{equation}
  \sum_{\nu_\ell<K}2\nu_\ell[U_{\rho,K}(\nu_\ell)]_<
  -\frac{2}{9\pi}(1-\rho^3)K^3
  =E_{\mathrm{mp}}+E_{\mathrm{ph}}-E_{\mathrm{frac}}.
  \label{eq:sc-fractional-budget}
\end{equation}
In particular, the blanket quarter-slack cost is exactly
\[
  \frac14\sum_{\ell=0}^{m_K-1}(2\ell+1)=\frac{m_K^2}{4};
\]
it cannot be discarded merely because it is of lower polynomial order for
fixed \(\rho\).

\subsection{Multiplicity reduction to shifted one-dimensional tails}

We record the two external floor-sum inequalities used in the small-hole
argument.  For integers \(a<b\), write
\begin{equation}
  \mathbf T(h;a,b)
  :=\frac12\lfloor h(a)\rfloor
  +\sum_{j=a+1}^{b-1}\lfloor h(j)\rfloor
  +\frac12\lfloor h(b)\rfloor.
  \label{eq:sc-trapezoidal-floor}
\end{equation}

\begin{lemma}[External trapezoidal floor bounds]
\label{lem:sc-external-floor-bounds}
The following statements hold.
\begin{enumerate}
  \item If \(h\) is nonnegative and concave on an integer interval
  \([a,b]\), then
  \begin{equation}
    \mathbf T(h;a,b)\le\int_a^bh(t)\,dt.
    \label{eq:sc-concave-floor-bound}
  \end{equation}
  \item Suppose \(h\) is nonnegative, decreasing, concave, and
  \(c\)-Lipschitz on an
  integer interval \([a,b]\), where \(0<c<1\).  If an integer
  \(p\in[a,b)\) is the last point of the first ordinary-floor shelf, so that
  \[
    \lfloor h(a)\rfloor=\lfloor h(p)\rfloor
    >\lfloor h(p+1)\rfloor,
  \]
  then
  \begin{equation}
    \mathbf T(h;a,b)
    \leq\int_a^b h(t)\,dt-
          \frac{1-c}{2}(b-p).
    \label{eq:sc-improved-concave-floor-bound}
  \end{equation}
  If no such drop occurs, set \(p=b\); the basic bound in item~1 gives
  the same displayed formula with zero correction.  This last no-drop case
  is a consequence of the basic proposition, not an invocation of the
  improved theorem at \(p=b\).
  \item If \(g\) is nonnegative, decreasing, convex, and
  \(1/2\)-Lipschitz on an integer interval \([a,b]\), if \(g(b)=0\), and if
  \(g\) is \(1/3\)-Lipschitz on \([t_*,b]\) for some
  \(t_*\in[a,b]\), then
  \begin{equation}
    \mathbf T(g+1/4;a,b)
    \le\int_a^bg(t)\,dt-\frac14\lfloor g(t_*)\rfloor.
    \label{eq:sc-improved-convex-floor-bound}
  \end{equation}
  \item If \(g\) is nonnegative, decreasing, convex, and
  \(1/2\)-Lipschitz on \([0,b]\), where \(b>0\) is arbitrary and \(g(b)=0\),
  then
  \begin{equation}
    \left\lfloor g(0)+\frac14\right\rfloor
    +2\sum_{j=1}^{\lfloor b\rfloor}
    \left\lfloor g(j)+\frac14\right\rfloor
    \le2\int_0^bg(t)\,dt.
    \label{eq:sc-convex-shifted-tail-bound}
  \end{equation}
\end{enumerate}
\end{lemma}

The first assertion is Proposition~3.1 of \cite{FLPSannuli}; the
first-shelf improvement is its Theorem~1.4; and the third assertion is its
Theorem~3.4.  The fourth is the translated convex shifted-floor theorem of
\cite{FLPSballs}.  These published one-dimensional inequalities are the only
non-special-function external inputs in what follows.

For \(r\in\mathbb N_0\), put \(x_r=r+\tfrac12\) and define the coarse shifted
tail
\begin{equation}
  \mathcal T_r=
  \left\lfloor A_{\rho,K}(x_r)+\frac14\right\rfloor
  +2\sum_{j\ge1}
  \left\lfloor A_{\rho,K}(x_r+j)+\frac14\right\rfloor.
  \label{eq:sc-shifted-tail}
\end{equation}
All but finitely many terms vanish.

\begin{lemma}[Weighted-lattice scaffold]
\label{lem:sc-weighted-scaffold}
One has
\begin{equation}
  S_{\rho,K}=\sum_{r\ge0}\mathcal T_r.
  \label{eq:sc-tail-decomposition}
\end{equation}
If, for every \(r\) with \(x_r<K\),
\begin{equation}
  \mathcal T_r\le2\int_{x_r}^{K}A_{\rho,K}(z)\,dz,
  \label{eq:sc-tail-target}
\end{equation}
then
\begin{equation}
  S_{\rho,K}\le
  \frac{2}{9\pi}(1-\rho^3)K^3.
  \label{eq:sc-scaffold-conclusion}
\end{equation}
\end{lemma}

\begin{proof}
For any finitely supported nonnegative integer sequence \(q_\ell\),
\[
  \sum_{\ell\ge0}(2\ell+1)q_\ell
  =\sum_{r\ge0}\left(q_r+2\sum_{\ell>r}q_\ell\right).
\]
Indeed, \(q_\ell\) appears once with coefficient one when \(r=\ell\) and
appears \(\ell\) times with coefficient two when \(0\le r<\ell\).  Taking
\[
  q_\ell=\left\lfloor
  A_{\rho,K}(\ell+\tfrac12)+\frac14\right\rfloor
\]
proves \eqref{eq:sc-tail-decomposition}; samples at or beyond \(K\) are
zero.

Assume \eqref{eq:sc-tail-target}.  Tonelli's theorem for the finite
nonnegative sum gives
\[
  S_{\rho,K}
  \le2\int_0^K f_3(z)A_{\rho,K}(z)\,dz,
  \qquad
  f_3(z)=\#\{r\in\mathbb N_0:r+\tfrac12\le z\}.
\]
Let \(F_3(z)=\int_0^zf_3(t)\,dt\).  If
\(z=m+\tfrac12+s\), where \(m\in\mathbb N_0\) and \(0\le s<1\), then direct
summation gives
\begin{equation}
  \frac{z^2}{2}-F_3(z)
  =\frac12\left(s-\frac12\right)^2\ge0;
  \label{eq:sc-step-primitive}
\end{equation}
for \(0\le z<1/2\) the same inequality is immediate because \(F_3(z)=0\).
The action \(A_{\rho,K}\) is absolutely continuous, decreasing, and vanishes
at \(K\).  Indeed, away from the inner interface,
\[
  A_{\rho,K}'(z)=
  \begin{cases}
  \displaystyle-\frac1\pi\left(
  \arccos\frac zK-\arccos\frac z\mu\right)<0,
  &0<z<\mu,\\[2mm]
  \displaystyle-\frac1\pi\arccos\frac zK<0,
  &\mu<z<K,
  \end{cases}
\]
and the two formulas have the same limiting value at \(z=\mu\).
Integration by parts and \eqref{eq:sc-step-primitive} therefore
give
\[
  2\int_0^Kf_3A_{\rho,K}
  =-2\int_0^KF_3A_{\rho,K}'
  \le-\int_0^Kz^2A_{\rho,K}'(z)\,dz
  =\int_0^K2zA_{\rho,K}(z)\,dz.
\]
Now apply \eqref{eq:sc-exact-action-integral}.
\end{proof}

\begin{lemma}[Tails at or above the inner interface]
\label{lem:sc-high-interface-tails}
If \(x_r\ge\mu=\rho K\) and \(x_r<K\), then
\[
  \mathcal T_r\le2\int_{x_r}^{K}A_{\rho,K}(z)\,dz.
\]
Equality \(x_r=\mu\) is included.
\end{lemma}

\begin{proof}
On \(z\ge x_r\ge\mu\), one has \(G_\mu(z)=0\), including at \(z=\mu\),
so \(A_{\rho,K}(z)=G_K(z)\).  Set \(b=K-x_r>0\) and
\(g(t)=G_K(x_r+t)\) on \([0,b]\).  Direct differentiation of
\eqref{eq:sc-model-action} gives
\[
  G_K'(z)=-\frac1\pi\arccos\frac zK\in[-1/2,0],
  \qquad
  G_K''(z)=\frac1{\pi\sqrt{K^2-z^2}}>0.
\]
Thus \(g\) is nonnegative, decreasing, convex, and \(1/2\)-Lipschitz, with
\(g(b)=G_K(K)=0\).  Terms of \eqref{eq:sc-shifted-tail} with \(j>b\) vanish;
if \(b\) is an integer, the terminal term is
\(\lfloor G_K(K)+1/4\rfloor=0\).  Therefore
\eqref{eq:sc-convex-shifted-tail-bound} is exactly the desired estimate.
\end{proof}

\subsection{The low-interface estimate in the small-hole sector}

Define
\begin{equation}
  \omega_0:=G_1(1/2)=\frac{\sqrt3}{2\pi}-\frac16,
  \qquad
  C_*:=\frac12+\frac{8\sqrt2}{15}.
  \label{eq:sc-small-hole-constants}
\end{equation}
Notice that \(0<\omega_0<1/2\).  The lower inequality is equivalent to
\(\pi<3\sqrt3\), which follows from \(\pi<4<3\sqrt3\); the upper inequality
also follows directly from \(0<G_1(1/2)<G_1(0)=1/\pi<1/2\).

\begin{lemma}[Low-interface shifted tails]
\label{lem:sc-low-interface-tails}
Assume
\begin{equation}
  0<\rho<\omega_0,
  \qquad
  K(\omega_0-\rho)\ge C_*.
  \label{eq:sc-low-interface-sector}
\end{equation}
If \(x_r=r+\tfrac12<\mu=\rho K\), then, in fact strictly,
\begin{equation}
  \mathcal T_r
  <2\int_{x_r}^{K}A_{\rho,K}(z)\,dz.
  \label{eq:sc-low-tail-conclusion}
\end{equation}
\end{lemma}

\begin{proof}
Fix a low tail and abbreviate \(x_0=x_r\), \(A=A_{\rho,K}\).  Put
\begin{equation}
  n=\lfloor\mu-x_0\rfloor,
  \qquad q=x_0+n,
  \qquad B=\lceil K-x_0\rceil.
  \label{eq:sc-interface-bookkeeping}
\end{equation}
Then
\[
  q\le\mu<q+1,
  \qquad n<B,
  \qquad G_K(x_0+B)=0.
\]
The point \(q\) is the largest half-integer in the tail grid that does not
exceed \(\mu\); it need not equal \(\lfloor\mu\rfloor\).  A low tail also
forces \(\mu>x_0\ge1/2\), hence \(\mu>1/2\).

Let
\[
  h_A(t)=A(x_0+t)+\frac14,
  \qquad h_K(t)=G_K(x_0+t)+\frac14.
\]
All samples at and beyond \(B\) have floor zero, so
\[
  \frac{\mathcal T_r}{2}=\mathbf T(h_A;0,B).
\]
If \(n\ge1\), additivity of the trapezoidal sum at the shared endpoint and
\(A\le G_K\) give
\begin{equation}
  \frac{\mathcal T_r}{2}
  \le\mathbf T(h_A;0,n)+\mathbf T(h_K;n,B).
  \label{eq:sc-tail-split-positive-n}
\end{equation}
At the split point, the two half-weights add to the original full sample;
after replacing the suffix by \(G_K\), its half-sample can only increase.
If \(n=0\), there is no concave block, and instead
\begin{equation}
  \frac{\mathcal T_r}{2}\le\mathbf T(h_K;0,B).
  \label{eq:sc-tail-split-zero-n}
\end{equation}

For \(0<z<\mu\),
\begin{equation}
  A''(z)=\frac1{\pi\sqrt{K^2-z^2}}
  -\frac1{\pi\sqrt{\mu^2-z^2}}<0.
  \label{eq:sc-action-concavity}
\end{equation}
Thus \(A\) is concave on \([x_0,q]\), also when \(q=\mu\) by continuity.
For \(n\ge1\), the concave bound
\eqref{eq:sc-concave-floor-bound} gives
\begin{equation}
  \mathbf T(h_A;0,n)
  \le\int_0^nA(x_0+t)\,dt+\frac n4.
  \label{eq:sc-concave-head}
\end{equation}

For the suffix set \(g(t)=G_K(x_0+t)\), using the zero extension after
\(K\).  It is nonnegative, decreasing, convex, globally
\(1/2\)-Lipschitz, and \(g(B)=0\).  Because
\(q\le\mu=\rho K<\omega_0K<K/2\),
\[
  t_*:=\frac K2-x_0
\]
belongs to \([n,B]\) (strictly to the right of \(n\)).  On
\([t_*,B]\),
\[
  |g'(t)|\le\frac1\pi\arccos\frac12=\frac13,
\]
and
\[
  g(t_*)=G_K(K/2)=\omega_0K.
\]
Every hypothesis of \eqref{eq:sc-improved-convex-floor-bound} is therefore
satisfied, and
\begin{equation}
  \mathbf T(h_K;n,B)
  \le\int_n^BG_K(x_0+t)\,dt
  -\frac14\lfloor\omega_0K\rfloor.
  \label{eq:sc-convex-suffix}
\end{equation}
The identical statement with \(n=0\) applies to
\eqref{eq:sc-tail-split-zero-n}.

Combining \eqref{eq:sc-concave-head} and
\eqref{eq:sc-convex-suffix}, or using only the latter when \(n=0\), leaves
one and only one integral mismatch:
\begin{equation}
  \delta:=\int_q^\mu G_\mu(z)\,dz.
  \label{eq:sc-interface-loss}
\end{equation}
Indeed,
\[
  \int_{x_0}^{q}A(z)\,dz+\int_q^KG_K(z)\,dz
  =\int_{x_0}^KA(z)\,dz+\delta,
\]
and the same identity holds for \(n=0\), where \(q=x_0\).  Hence
\begin{equation}
  \frac{\mathcal T_r}{2}
  \le\int_{x_0}^KA(z)\,dz
  +\delta-\frac{\lfloor\omega_0K\rfloor-n}{4}.
  \label{eq:sc-tail-compensation}
\end{equation}

The turning-point estimate of Lemma~6.2 in \cite{FLPSannuli} states that
\begin{equation}
  G_\mu(z)<\frac{(\mu-z)^{3/2}}{3\sqrt\mu},
  \qquad 0<z<\mu.
  \label{eq:sc-turning-point-bound}
\end{equation}
If \(q<\mu\), integration gives a strict first bound; if \(q=\mu\), both
sides below vanish.  The endpoint-safe statement is
\begin{equation}
  0\le\delta
  \le\frac{2(\mu-q)^{5/2}}{15\sqrt\mu}
  <\frac{2\sqrt2}{15},
  \label{eq:sc-interface-loss-bound}
\end{equation}
because \(0\le\mu-q<1\) and \(\mu>1/2\).  The last inequality remains
strict when \(q=\mu\), since then \(\delta=0\).

Finally, \(x_0\ge1/2\) implies
\[
  n\le\mu-x_0\le\rho K-\frac12,
\]
while \(\lfloor y\rfloor>y-1\) for every real \(y\).  Therefore
\begin{align*}
  \lfloor\omega_0K\rfloor-n
  &>\omega_0K-1-\left(\rho K-\frac12\right)\\
  &=K(\omega_0-\rho)-\frac12\\
  &\ge\frac{8\sqrt2}{15}
  >4\delta.
\end{align*}
Both strict inequalities remain strict when the threshold in
\eqref{eq:sc-low-interface-sector} is attained.  Substitution in
\eqref{eq:sc-tail-compensation} proves
\eqref{eq:sc-low-tail-conclusion}.
\end{proof}

\subsection{Uniform closure of the small-hole endpoint}

Set
\begin{equation}
  \rho_*:=\frac{\omega_0}{1+2C_*}
  =\frac{\frac{\sqrt3}{2\pi}-\frac16}
  {2+\frac{16\sqrt2}{15}}.
  \label{eq:sc-rho-star}
\end{equation}
Since \(\omega_0>0\) and \(C_*>0\),
\(0<\rho_*<\omega_0\).  Its defining identity is
\begin{equation}
  \omega_0-\rho_*=2C_*\rho_*,
  \qquad
  \frac{\omega_0-\rho_*}{2\rho_*}=C_*.
  \label{eq:sc-rho-star-identity}
\end{equation}

\begin{theorem}[Complete small-hole endpoint]
\label{thm:sc-small-hole-endpoint}
For every \(0<\rho\le\rho_*\) and every \(K\ge0\),
\begin{equation}
  \boxed{
  N_D(A_{\rho,1},K^2)
  \le\frac{2}{9\pi}(1-\rho^3)K^3.}
  \label{eq:sc-small-hole-polya}
\end{equation}
The face \(\rho=\rho_*\), the interface wall \(\rho K=1/2\), and every
strict spectral wall are included.
\end{theorem}

\begin{proof}
If \(K=0\), the strict spectrum is positive, so the left side and the right
side of \eqref{eq:sc-small-hole-polya} are both zero.  Assume \(K>0\) and
write \(\mu=\rho K\).

First suppose \(\mu\le1/2\).  Every shifted-tail start satisfies
\[
  x_r=r+\frac12\ge\frac12\ge\mu.
\]
Lemma~\ref{lem:sc-high-interface-tails} therefore proves
\eqref{eq:sc-tail-target} for every active tail.  At the joining wall
\(\mu=1/2\), the first start is exactly \(x_0=\mu\), which belongs to the
inclusive high-interface lemma.

Now suppose \(\mu>1/2\).  Then
\begin{equation}
  K>\frac1{2\rho}.
  \label{eq:sc-high-K-from-interface}
\end{equation}
For \(0<\rho\le\rho_*\), the defining identity
\eqref{eq:sc-rho-star-identity} gives
\begin{equation}
  \frac{\omega_0-\rho}{2\rho}\ge C_*;
  \label{eq:sc-uniform-small-hole-threshold}
\end{equation}
equivalently, multiply
\((1+2C_*)\rho\le(1+2C_*)\rho_*=\omega_0\)
by positive quantities.  Since
\(\omega_0-\rho>0\), \eqref{eq:sc-high-K-from-interface} and
\eqref{eq:sc-uniform-small-hole-threshold} imply
\begin{equation}
  K(\omega_0-\rho)
  >\frac{\omega_0-\rho}{2\rho}
  \ge C_*.
  \label{eq:sc-strict-small-hole-threshold}
\end{equation}
Every start \(x_r\ge\mu\) is controlled by
Lemma~\ref{lem:sc-high-interface-tails}; every start \(x_r<\mu\) is
controlled by Lemma~\ref{lem:sc-low-interface-tails}, because
\(\rho\le\rho_*<\omega_0\) and
\eqref{eq:sc-strict-small-hole-threshold} supplies its threshold.  Thus all
active tails satisfy \eqref{eq:sc-tail-target} in this branch as well.

Lemma~\ref{lem:sc-weighted-scaffold} now yields
\[
  S_{\rho,K}\le\frac{2}{9\pi}(1-\rho^3)K^3,
\]
and Proposition~\ref{prop:sc-phase-lattice} gives
\(N_D(A_{\rho,1},K^2)\le S_{\rho,K}\), proving
\eqref{eq:sc-small-hole-polya}.

At \(\rho=\rho_*\), inequality
\eqref{eq:sc-uniform-small-hole-threshold} is an equality, but the first
inequality in \eqref{eq:sc-strict-small-hole-threshold} is strict whenever
\(\mu>1/2\).  Hence the endpoint is included.  If instead
\(K(\omega_0-\rho)=C_*\), then
\[
  \mu=\frac{C_*\rho}{\omega_0-\rho}\le\frac12
\]
by \eqref{eq:sc-uniform-small-hole-threshold}, so the point already belongs
to the all-high-interface branch.  No limiting argument at \(\rho=0\), no
continuity of Bessel roots, and no finite numerical verification is used.
\end{proof}

\section{The thin-shell endpoint}
\label{thin:sec-endpoint}

We now prove the P\'olya inequality uniformly as the shell becomes thin.  In
this section the counting function is strict:
\[
  N_D(\Omega,K^2)=\#\{j:\lambda_j(\Omega)<K^2\}.
\]
We retain the global convention
\([u]_<:=\#\{n\in\mathbb N:n<u\}=\max\{0,\lceil u\rceil-1\}\).
Thus a spectral level lying exactly on the wall \(K^2\) is not counted.  Put
\begin{equation}
  \varepsilon=1-\rho,
  \qquad a=\varepsilon K,
  \qquad
  m_\varepsilon=1-\varepsilon+\frac{\varepsilon^2}{3}.
  \label{thin:eq-normalized-variables}
\end{equation}
Since \(1-\rho^3=3\varepsilon m_\varepsilon\), the desired right-hand side
has the two equivalent forms
\begin{equation}
  \frac{2}{9\pi}(1-\rho^3)K^3
  =\frac{1}{\varepsilon^2}\frac{2a^3}{3\pi}m_\varepsilon.
  \label{thin:eq-weyl-normalization}
\end{equation}

The proof uses the optimized phase estimate already established in
Proposition~\ref{prop:sc-phase-lattice}.  We record precisely the consequence
that is used here.  For
\(\nu_\ell=\ell+\tfrac12\), let
\(\gamma_{\rho,K}(\nu_\ell)\) be the normalized radial Bessel phase.  If
\(0\leq\nu_\ell\leq K\), that proposition gives
\begin{equation}
  \gamma_{\rho,K}(\nu_\ell)
  < A_{\rho,K}(\nu_\ell)+\frac14,
  \label{thin:eq-phase-input}
\end{equation}
where, after the scaling in \eqref{thin:eq-normalized-variables},
\(A_{\rho,K}(\nu)=\mathcal A(\varepsilon\nu)\) and
\(\mathcal A\) is the explicit action in
\eqref{thin:eq-action-definition} below.  The exact radial count in channel
\(\ell\) is
\begin{equation}
  \#\{n\geq1:n<\gamma_{\rho,K}(\nu_\ell)\}.
  \label{thin:eq-exact-phase-count}
\end{equation}
In particular, \eqref{thin:eq-phase-input} is an inequality for the strict
count; it is not a replacement of that count by an ordinary floor.

\subsection{The product comparison}

Under the standard unitary radial transformation, the angular channel
\(\ell\in\mathbb N_0\) is the Dirichlet operator
\[
  L_\ell=-\frac{d^2}{dr^2}+\frac{\ell(\ell+1)}{r^2}
  \quad\hbox{in }L^2((\rho,1),dr),
\]
and it occurs with multiplicity \(2\ell+1\).  The following lemma includes
the direction of the min--max comparison and every strict radial and angular
wall.

\begin{lemma}[Strict product majorant]
\label{thin:lem-product-majorant}
Let \(0<\varepsilon<1\), \(a=\varepsilon K\), and define
\begin{equation}
  N(a)=\max\left\{0,\left\lceil\frac a\pi\right\rceil-1\right\}.
  \label{thin:eq-radial-count}
\end{equation}
For \(1\leq n\leq N(a)\), put
\[
  b_n=\sqrt{a^2-n^2\pi^2},
  \qquad
  M_n=
  \left\lceil
  \sqrt{\left(\frac{b_n}{\varepsilon}\right)^2+\frac14}
  -\frac12
  \right\rceil.
\]
Then
\begin{equation}
  N_D(A_{\rho,1},K^2)
  \leq \mathcal P_\varepsilon(a)
  :=\sum_{n=1}^{N(a)}M_n^2.
  \label{thin:eq-product-majorant}
\end{equation}
In particular, the strict shell count is zero for \(0\leq a\leq\pi\).
\end{lemma}

\begin{proof}
The two quadratic forms have the common domain \(H_0^1(\rho,1)\), and
\[
  \int_\rho^1\left(
     |u'|^2+\frac{\ell(\ell+1)}{r^2}|u|^2
  \right)dr
  \geq
  \int_\rho^1\left(|u'|^2+\ell(\ell+1)|u|^2\right)dr,
\]
because \(r\leq1\).  The min--max principle therefore gives
\[
  \lambda_{\ell,n}
  \geq \left(\frac{n\pi}{\varepsilon}\right)^2
       +\ell(\ell+1),
  \qquad n\geq1.
\]
Consequently, a shell eigenvalue in this channel can be counted below
\(K^2\) only if
\begin{equation}
  n^2\pi^2+\varepsilon^2\ell(\ell+1)<a^2.
  \label{thin:eq-product-condition}
\end{equation}
The active radial integers are exactly those satisfying \(n\pi<a\), whose
number is \eqref{thin:eq-radial-count}.  For a fixed active \(n\), condition
\eqref{thin:eq-product-condition} is
\[
  \ell<
  \sqrt{\left(\frac{b_n}{\varepsilon}\right)^2+\frac14}-\frac12.
\]
Hence the allowed angular indices are
\(0,\ldots,M_n-1\), and their full spherical multiplicity is
\[
  \sum_{\ell=0}^{M_n-1}(2\ell+1)=M_n^2.
\]
Summing proves \eqref{thin:eq-product-majorant}.

If \(a=m\pi\), the radial level \(n=m\) is excluded by the strict
inequality \(n\pi<a\); thus \(N(a)=m-1\).  At an angular wall
\(b_n^2/\varepsilon^2=L(L+1)\), the displayed expression inside the ceiling
is exactly \(L\), so \(M_n=L\) and the level \(\ell=L\) is excluded.  The
jump of multiplicity \(2L+1\) occurs only above the wall.  Finally, no
positive integer satisfies \(n\pi<a\) when \(0\leq a\leq\pi\), including
both endpoints, so the product majorant and hence the shell count are zero
there.
\end{proof}

\begin{lemma}[Exact product deficit]
\label{thin:lem-product-deficit}
For \(a>\pi\), let \(N=N(a)\) and write uniquely
\begin{equation}
  \frac a\pi=N+t,
  \qquad N\geq1,
  \qquad 0<t\leq1.
  \label{thin:eq-strict-radial-parametrization}
\end{equation}
At \(a=m\pi\), this means \((N,t)=(m-1,1)\).  Define
\[
  I_0(a)=\frac{2a^3}{3\pi},
  \qquad
  S_0(a)=\sum_{n=1}^{N}(a^2-n^2\pi^2),
  \qquad
  D(a)=I_0(a)-S_0(a).
\]
Then
\begin{equation}
  \frac{D(a)}{\pi^2}
  =\frac{N^2}{2}+N\left(t^2+\frac16\right)+\frac{2t^3}{3},
  \label{thin:eq-deficit-identity}
\end{equation}
and, uniformly for \(a>\pi\),
\begin{equation}
  D(a)>\frac25a^2.
  \label{thin:eq-deficit-bound}
\end{equation}
\end{lemma}

\begin{proof}
The sum of the first \(N\) squares gives
\[
\begin{aligned}
  \frac{D(a)}{\pi^2}
  &=\frac23(N+t)^3-N(N+t)^2
    +\frac{N(N+1)(2N+1)}6 \\
  &=\frac{N^2}{2}+N\left(t^2+\frac16\right)+\frac{2t^3}{3},
\end{aligned}
\]
which proves \eqref{thin:eq-deficit-identity}.  At \(a=m\pi\), its value
with \((N,t)=(m-1,1)\) agrees with the right limit \((N,t)\to(m,0+)\);
both equal \(m^2/2+m/6\).  Thus the formula owns the wall and both
one-sided limits.

Subtracting \(\tfrac25(N+t)^2\) from
\eqref{thin:eq-deficit-identity} gives the exact identity
\begin{equation}
\begin{aligned}
  \frac{D(a)}{\pi^2}-\frac25\left(\frac a\pi\right)^2
  ={}&\frac{N^2}{10}
  +N\left[\left(t-\frac25\right)^2+\frac1{150}\right] \\
  &+\frac{2t^3}{3}-\frac{2t^2}{5}.
\end{aligned}
  \label{thin:eq-deficit-square-completion}
\end{equation}
For \(h(t)=2t^3/3-2t^2/5\),
\(h'(t)=2t(t-2/5)\), so the minimum on \(0<t\leq1\) is
\(h(2/5)=-8/375\).  Therefore the right-hand side of
\eqref{thin:eq-deficit-square-completion} is at least
\[
  \frac{N^2}{10}+\frac{N}{150}-\frac8{375}.
\]
This expression increases for integral \(N\geq1\), and at \(N=1\) it is
\[
  \frac1{10}+\frac1{150}-\frac8{375}
  =\frac{32}{375}>0.
\]
This proves \eqref{thin:eq-deficit-bound} without sampling.
\end{proof}

\begin{proposition}[The inclusive low-action piece]
\label{thin:prop-low-piece}
If
\[
  0<\varepsilon\leq\frac18,
  \qquad 0\leq a\leq\frac{\pi}{4\varepsilon},
\]
then
\begin{equation}
  N_D(A_{\rho,1},K^2)
  <\frac{1}{\varepsilon^2}\frac{2a^3}{3\pi}m_\varepsilon
  \qquad(a>0),
  \label{thin:eq-low-piece-conclusion}
\end{equation}
whereas both sides are zero at \(a=0\).
\end{proposition}

\begin{proof}
For \(0<a\leq\pi\), Lemma~\ref{thin:lem-product-majorant} gives a zero
left-hand side and the right-hand side of
\eqref{thin:eq-low-piece-conclusion} is positive.  It remains to consider
\(a>\pi\).

For \(B=b_n/\varepsilon>0\), the elementary strict ceiling inequality gives
\[
  M_n<\sqrt{B^2+\frac14}+\frac12.
\]
Both sides are nonnegative, and
\(\sqrt{B^2+1/4}\leq B+1/2\).  Squaring and restoring the scale yields
\begin{equation}
  \varepsilon^2M_n^2
  <b_n^2+\varepsilon b_n+\varepsilon^2.
  \label{thin:eq-ceiling-cost}
\end{equation}
The function \(x\mapsto\sqrt{a^2-\pi^2x^2}\) is strictly decreasing on
its positive interval.  Hence
\begin{equation}
  \sum_{n=1}^{N}b_n
  <\int_0^N\sqrt{a^2-\pi^2x^2}\,dx
  \leq\int_0^{a/\pi}\sqrt{a^2-\pi^2x^2}\,dx
  =\frac{a^2}{4}.
  \label{thin:eq-quarter-disc}
\end{equation}
Also \(N<a/\pi\), including every radial wall because the wall level is
excluded.  Summation of \eqref{thin:eq-ceiling-cost} therefore gives
\begin{equation}
  \varepsilon^2\mathcal P_\varepsilon(a)
  <S_0(a)+\frac{\varepsilon a^2}{4}
    +\frac{\varepsilon^2a}{\pi}.
  \label{thin:eq-summed-ceiling-cost}
\end{equation}

It is enough to prove
\begin{equation}
  D(a)\geq
  \varepsilon\left(I_0(a)+\frac{a^2}{4}\right)
  +\frac{\varepsilon^2a}{\pi},
  \label{thin:eq-sufficient-deficit}
\end{equation}
because then \eqref{thin:eq-summed-ceiling-cost} is at most
\(I_0(a)(1-\varepsilon)\), and hence is strictly less than
\(I_0(a)m_\varepsilon\).

After division by \(a^2\), the right-hand side of
\eqref{thin:eq-sufficient-deficit} is
\[
  \frac{2\varepsilon a}{3\pi}+\frac\varepsilon4
  +\frac{\varepsilon^2}{\pi a}.
\]
The low-piece inequalities \(a\leq\pi/(4\varepsilon)\) and \(a\geq\pi\),
together with the elementary strict bound \(\pi>3\), imply
\begin{equation}
  \frac{2\varepsilon a}{3\pi}+\frac\varepsilon4
  +\frac{\varepsilon^2}{\pi a}
  \leq \frac16+\frac\varepsilon4+\frac{\varepsilon^2}{9}.
  \label{thin:eq-low-cost-screen}
\end{equation}
The last expression increases with \(\varepsilon>0\).  On the closed face
\(\varepsilon=1/8\), its exact reserve below \(2/5\) is
\begin{equation}
  \frac25-\left(\frac16+\frac1{32}+\frac1{576}\right)
  =\frac{577}{2880}>0.
  \label{thin:eq-low-reserve}
\end{equation}
Thus Lemma~\ref{thin:lem-product-deficit} proves
\eqref{thin:eq-sufficient-deficit}, and
Lemma~\ref{thin:lem-product-majorant} together with
\eqref{thin:eq-summed-ceiling-cost} proves
\eqref{thin:eq-low-piece-conclusion}.

All inequalities allow \(a=\pi/(4\varepsilon)\).  Since
\(\varepsilon\leq1/8\), this face has \(a\geq2\pi\).  At its corner
\((\varepsilon,a)=(1/8,2\pi)\), the strict radial convention is
\((N,t)=(1,1)\), and the positive reserve
\eqref{thin:eq-low-reserve} remains unchanged.  Thus the low proof owns the
whole common face.
\end{proof}

\subsection{The complementary-action comparison}

For \(r\in\{\rho,1\}\) and \(0\leq y\leq ar\), define
\begin{equation}
  J_r(y)=\sqrt{a^2r^2-y^2}
          -y\arccos\frac{y}{ar},
  \label{thin:eq-J-action}
\end{equation}
and set
\begin{equation}
  \mathcal A(y)=
  \begin{cases}
  \dfrac{J_1(y)-J_\rho(y)}{\pi\varepsilon},
    &0\leq y\leq\rho a,\\[6pt]
  \dfrac{J_1(y)}{\pi\varepsilon},
    &\rho a\leq y\leq a.
  \end{cases}
  \label{thin:eq-action-definition}
\end{equation}
We extend \(\mathcal A(y)=0\) for \(y>a\).

\begin{lemma}[Action geometry and curvature switch]
\label{thin:lem-action-geometry}
The function \(\mathcal A\) is continuous, continuously differentiable at
\(y=\rho a\), and strictly decreasing from
\[
  T:=\mathcal A(0)=\frac a\pi
  \quad\hbox{to}\quad \mathcal A(a)=0.
\]
Let \(R:[0,T]\to[0,a]\) be its decreasing inverse, let
\[
  \tau=\mathcal A(\rho a),
  \qquad F(t)=R(t)^2,
  \qquad g(t)=-F'(t).
\]
Then
\begin{equation}
\begin{gathered}
  g\text{ decreases on }(0,\tau),
  \qquad g\text{ increases on }(\tau,T),\\
  F(0)=a^2,
  \qquad F(\tau)=\rho^2a^2,
  \qquad F(T)=0,
  \qquad g(T)=2\pi\rho a,
\end{gathered}
  \label{thin:eq-action-geometry}
\end{equation}
where \(g(T)\) denotes the one-sided limit.  Moreover \(g(t)=O(t^{-1/3})\)
as \(t\downarrow0\).
\end{lemma}

\begin{proof}
Direct differentiation on the appropriate open intervals gives
\begin{equation}
  J_r'(y)=-\arccos\frac{y}{ar},
  \qquad
  J_r''(y)=\frac1{\sqrt{a^2r^2-y^2}}.
  \label{thin:eq-J-derivatives}
\end{equation}
At \(y=\rho a\), \(J_\rho(\rho a)=0\), and the two one-sided first
derivatives of \eqref{thin:eq-action-definition} both equal
\(-\arccos\rho/(\pi\varepsilon)\).  Thus the two pieces and their first
derivatives match.  Both derivatives are negative away from \(y=a\), so the
inverse exists on exactly the stated interval.

On the outer branch \(\rho a<y<a\), put
\(\alpha=\arccos(y/a)\).  If \(t=\mathcal A(y)\), then
\begin{equation}
  g(t)=-\frac{2y}{\mathcal A'(y)}
      =\frac{2\pi\varepsilon y}{\alpha}.
  \label{thin:eq-g-outer}
\end{equation}
The function \(y/\alpha\) increases with \(y\), whereas \(y=R(t)\)
decreases with \(t\); hence \(g\) decreases on \(0<t<\tau\).

On the inner branch \(0<y<\rho a\), put
\[
  \delta(y)=\arccos\frac ya-\arccos\frac{y}{\rho a}>0.
\]
Differentiating \(\arccos(y/(ar))\) with respect to \(r\) gives the exact
identity
\begin{equation}
  \frac{\delta(y)}{y}
  =\int_\rho^1\frac{dr}{r\sqrt{a^2r^2-y^2}}.
  \label{thin:eq-delta-integral}
\end{equation}
The integrand increases strictly with \(y\), so \(\delta(y)/y\) increases,
and \(y/\delta(y)\) decreases, with \(y\).  Since
\[
  g(t)=\frac{2\pi\varepsilon y}{\delta(y)}
\]
and \(y=R(t)\) decreases, \(g\) increases on \(\tau<t<T\).  Formula
\eqref{thin:eq-g-outer} and its inner counterpart agree at the interface.

The three values of \(F\) follow from
\(R(0)=a\), \(R(\tau)=\rho a\), and \(R(T)=0\).  As \(y\downarrow0\),
\eqref{thin:eq-delta-integral} gives
\[
  \delta(y)=\frac{\varepsilon}{\rho a}y+O(y^3),
\]
and therefore \(g(T)=2\pi\rho a\).

Finally, on the outer branch write \(y=a\cos\theta\).  Then
\begin{equation}
  t=\frac{a}{\pi\varepsilon}
       (\sin\theta-\theta\cos\theta)
    \sim\frac{a\theta^3}{3\pi\varepsilon},
  \qquad
  g(t)=\frac{2\pi\varepsilon a\cos\theta}{\theta}
       =O(t^{-1/3}).
  \label{thin:eq-improper-asymptotic}
\end{equation}
This proves the asserted improper endpoint behavior.  All square roots and
arccosines in the proof are taken on their stated closed domains; every
division occurs in an open interval where its denominator is positive, and
the endpoint zeros are handled by the limits just computed.
\end{proof}

\begin{lemma}[Strict phase-to-action layer cake]
\label{thin:lem-layer-cake}
For \(\ell\in\mathbb N_0\), set
\begin{equation}
  y_\ell=\varepsilon\left(\ell+\frac12\right),
  \qquad
  q_\ell=\left[\mathcal A(y_\ell)+\frac14\right]_<,
  \qquad
  P_{\mathcal A}=\varepsilon\sum_{\ell\geq0}y_\ell q_\ell.
  \label{thin:eq-phase-proxy}
\end{equation}
Then
\begin{equation}
  N_D(A_{\rho,1},K^2)
  \leq\frac{2P_{\mathcal A}}{\varepsilon^2}.
  \label{thin:eq-phase-transfer}
\end{equation}
For \(n\geq1\), put \(x_n=n-\tfrac14\), and define
\begin{equation}
  M_\varepsilon(x)
  =\#\left\{\ell\in\mathbb N_0:
       \varepsilon\left(\ell+\frac12\right)<x\right\}
  =\max\left\{0,
       \left\lceil\frac{x}{\varepsilon}-\frac12\right\rceil
       \right\}.
  \label{thin:eq-half-integer-count}
\end{equation}
The proxy has the exact finite representation
\begin{equation}
  P_{\mathcal A}
  =\frac{\varepsilon^2}{2}
    \sum_{\substack{n\geq1\\x_n<T}}
       M_\varepsilon(R(x_n))^2.
  \label{thin:eq-discrete-layer-cake}
\end{equation}
Moreover,
\begin{equation}
  I:=\frac12\int_0^T F(t)\,dt
  =\frac{a^3}{3\pi}
     \left(1-\varepsilon+\frac{\varepsilon^2}{3}\right),
  \qquad
  \frac{2I}{\varepsilon^2}
  =\frac{2}{9\pi}(1-\rho^3)K^3.
  \label{thin:eq-continuous-normalization}
\end{equation}
\end{lemma}

\begin{proof}
For \(y_\ell<a\), equations \eqref{thin:eq-phase-input} and
\eqref{thin:eq-exact-phase-count} show that the number of radial levels in
channel \(\ell\) is at most \(q_\ell\).  If \(y_\ell\geq a\), equivalently
\(\nu_\ell\geq K\), the product comparison gives
\[
  \lambda_{\ell,1}
  \geq\frac{\pi^2}{\varepsilon^2}+\ell(\ell+1)
  =\frac{\pi^2}{\varepsilon^2}+\nu_\ell^2-\frac14
  >K^2,
\]
so there is no radial level; at \(y_\ell=a\), the definition also gives
\(q_\ell=[1/4]_< =0\).  Multiplicity \(2\ell+1=2y_\ell/\varepsilon\)
now yields
\[
  N_D(A_{\rho,1},K^2)
  \leq\sum_{\ell\geq0}\frac{2y_\ell}{\varepsilon}q_\ell
  =\frac{2P_{\mathcal A}}{\varepsilon^2},
\]
which proves \eqref{thin:eq-phase-transfer}.  If
\(\mathcal A(y_\ell)+1/4=m\in\mathbb Z\), then \(q_\ell=m-1\), so the
phase-proxy wall is excluded exactly as required.

For every \(y\geq0\), the strict bracket is
\[
  \left[\mathcal A(y)+\frac14\right]_<
  =\#\{n\geq1:x_n<\mathcal A(y)\}.
\]
The sums are finite.  Since \(\mathcal A\) and \(R\) are decreasing,
\(x_n<\mathcal A(y_\ell)\) is equivalent to \(y_\ell<R(x_n)\).  Therefore
\[
\begin{aligned}
  P_{\mathcal A}
  &=\varepsilon
    \sum_{\substack{n\geq1\\x_n<T}}
      \sum_{y_\ell<R(x_n)}y_\ell \\
  &=\varepsilon
    \sum_{\substack{n\geq1\\x_n<T}}
      \varepsilon\sum_{\ell=0}^{M_\varepsilon(R(x_n))-1}
        \left(\ell+\frac12\right) \\
  &=\frac{\varepsilon^2}{2}
    \sum_{\substack{n\geq1\\x_n<T}}
      M_\varepsilon(R(x_n))^2,
\end{aligned}
\]
because \(\sum_{\ell=0}^{M-1}(\ell+1/2)=M^2/2\).  This proves
\eqref{thin:eq-discrete-layer-cake}.  Formula
\eqref{thin:eq-half-integer-count} follows from the same strict counting;
at \(x/\varepsilon=m+1/2\), it equals \(m\), excluding \(\ell=m\).

Differentiation of \eqref{thin:eq-J-action} with respect to \(r\) gives
\[
  \frac{\partial J_r(y)}{\partial r}
  =\sqrt{a^2-\frac{y^2}{r^2}}
  \quad(0\leq y\leq ar).
\]
Consequently the two cases of \eqref{thin:eq-action-definition} combine as
\begin{equation}
  \mathcal A(y)
  =\frac1{\pi\varepsilon}
    \int_\rho^1
      \left(a^2-\frac{y^2}{r^2}\right)_+^{1/2}\,dr,
  \label{thin:eq-action-integral}
\end{equation}
where \(s_+=\max\{s,0\}\).
The area identity for a decreasing inverse and Tonelli's theorem give
\[
  \frac12\int_0^T R(t)^2\,dt
  =\int_0^a y\mathcal A(y)\,dy.
\]
Using \eqref{thin:eq-action-integral} and then \(y=rz\),
\[
\begin{aligned}
  \int_0^a y\mathcal A(y)\,dy
  &=\frac1{\pi\varepsilon}
    \int_\rho^1r^2\,dr
    \int_0^a z\sqrt{a^2-z^2}\,dz \\
  &=\frac{a^3}{3\pi\varepsilon}\int_\rho^1r^2\,dr
   =\frac{a^3}{3\pi}
      \left(1-\varepsilon+\frac{\varepsilon^2}{3}\right).
\end{aligned}
\]
This is \eqref{thin:eq-continuous-normalization}; its final equality follows
from \(1-\rho^3=3\varepsilon m_\varepsilon\) and \(K=a/\varepsilon\).
\end{proof}

\begin{lemma}[Shifted sawtooth and radial quadrature deficit]
\label{thin:lem-radial-deficit}
Let
\[
  C(t)=\#\{n\geq1:n-\tfrac14<t\},
  \qquad w(t)=t-C(t),
  \qquad \mathfrak W(t)=\int_0^t w(s)\,ds,
\]
and put \(\Psi(t)=\mathfrak W(t)-t/4\).  Then, for all \(t\geq0\),
\begin{equation}
  \mathfrak W(t)\geq0,
  \qquad
  -\frac1{32}\leq\Psi(t)\leq\frac3{32}.
  \label{thin:eq-sawtooth-bounds}
\end{equation}
Furthermore, with
\begin{equation}
  D_{\mathrm{rad}}
  =\int_0^T F(t)\,dt
   -\sum_{\substack{n\geq1\\x_n<T}}F(x_n),
  \label{thin:eq-radial-deficit-definition}
\end{equation}
one has
\begin{equation}
  D_{\mathrm{rad}}
  \geq\frac{\rho^2a^2}{4}-\frac{\pi\rho a}{4}.
  \label{thin:eq-radial-deficit-bound}
\end{equation}
\end{lemma}

\begin{proof}
On \(0\leq t\leq3/4\), \(C(t)=0\), and hence
\begin{equation}
  \Psi(t)=\frac12\left(t-\frac14\right)^2-\frac1{32}.
  \label{thin:eq-first-sawtooth-cell}
\end{equation}
For \(x_n=n-1/4\), \(n\geq1\), and \(t=x_n+u\) with
\(0\leq u\leq1\), direct integration gives
\begin{equation}
  \Psi(t)=\frac12\left(u-\frac12\right)^2-\frac1{32}.
  \label{thin:eq-periodic-sawtooth-cell}
\end{equation}
These formulas agree at cell endpoints and prove the two-sided bound for
\(\Psi\).  On the first cell \(\mathfrak W=t^2/2\geq0\).  Thereafter
\(\mathfrak W=t/4+\Psi\geq t/4-1/32>0\), proving
\eqref{thin:eq-sawtooth-bounds}.  At a jump \(x_n\), strict counting gives
the one-sided values \(w(x_n^-)=3/4\) and \(w(x_n^+)=-1/4\), while
\(\mathfrak W\)
and \(\Psi\) are continuous.

Distributionally, \(dw=dt-dC\).  Since \(F(T)=0\), an atom at \(x_n=T\)
has zero weight and is consistent with its exclusion from
\eqref{thin:eq-radial-deficit-definition}.  Stieltjes integration by parts,
first on \([\eta,T]\) and then with \(\eta\downarrow0\), gives
\begin{equation}
  D_{\mathrm{rad}}=\int_0^T w(t)g(t)\,dt.
  \label{thin:eq-stieltjes-start}
\end{equation}
Indeed, \eqref{thin:eq-improper-asymptotic}, together with
\(w(t)=t\) and \(\mathfrak W(t)=t^2/2\) near zero, gives
\(w(t)g(t)=O(t^{2/3})\) and
\(\mathfrak W(t)g(t)=O(t^{5/3})\to0\), so the improper
boundary term vanishes.

Split \eqref{thin:eq-stieltjes-start} at the actual value \(\tau\), with
no assumption that \(\tau\) belongs to any particular sawtooth cell.  On
\((0,\tau)\), \(g\) decreases and \(\mathfrak W\geq0\); hence
\begin{equation}
  \int_0^\tau wg
  =\mathfrak W(\tau)g(\tau)-\int_0^\tau \mathfrak W\,dg
  \geq \mathfrak W(\tau)g(\tau).
  \label{thin:eq-decreasing-stieltjes}
\end{equation}
On \((\tau,T)\), \(g\) increases and \(w=1/4+\Psi'\) almost everywhere.
Adding its integration-by-parts identity to
\eqref{thin:eq-decreasing-stieltjes}, and using
\(\mathfrak W(\tau)=\tau/4+\Psi(\tau)\), cancels the interface value and
yields
\[
  D_{\mathrm{rad}}
  \geq \frac{F(\tau)}4+\frac{\tau g(\tau)}4
     +\Psi(T)g(T)-\int_\tau^T\Psi\,dg.
\]
Because \(dg\) is a positive measure on \((\tau,T)\), the bounds
\eqref{thin:eq-sawtooth-bounds} imply
\[
\begin{aligned}
  D_{\mathrm{rad}}
  &\geq \frac{F(\tau)}4-\frac{g(T)}8
    +g(\tau)\left(\frac\tau4+\frac3{32}\right) \\
  &\geq \frac{F(\tau)}4-\frac{g(T)}8.
\end{aligned}
\]
The two discarded quantities,
\(-\int_0^\tau \mathfrak W\,dg\) and
\(g(\tau)(\tau/4+3/32)\), are explicitly nonnegative.  Substitution of
\(F(\tau)=\rho^2a^2\) and \(g(T)=2\pi\rho a\) from
Lemma~\ref{thin:lem-action-geometry} proves
\eqref{thin:eq-radial-deficit-bound}.  Continuity of
\(\mathfrak W,\Psi,g\) at the
split shows that the same proof covers \(\tau\) below, on, or above every
sawtooth grid point.
\end{proof}

\begin{proposition}[The inclusive high-action piece]
\label{thin:prop-high-piece}
If
\[
  0<\varepsilon\leq\frac18,
  \qquad a\geq\frac{\pi}{4\varepsilon},
\]
then
\begin{equation}
  N_D(A_{\rho,1},K^2)
  <\frac{2}{9\pi}(1-\rho^3)K^3.
  \label{thin:eq-high-piece-conclusion}
\end{equation}
\end{proposition}

\begin{proof}
The number of active radial action layers is
\begin{equation}
\begin{aligned}
  J_{\mathrm{rad}}
  &:=\#\{n\geq1:x_n<T\}
    =\left\lceil T+\frac14\right\rceil-1 \\
  &<T+\frac14=\frac a\pi+\frac14.
\end{aligned}
  \label{thin:eq-active-action-layers}
\end{equation}
At a wall \(x_n=T\), this gives \(J_{\mathrm{rad}}=n-1\), so the equality
layer is excluded.

For every included \(x_n<T\), let \(x=R(x_n)>0\).  The exact count
\eqref{thin:eq-half-integer-count} satisfies
\[
  M_\varepsilon(x)<\frac{x}{\varepsilon}+\frac12.
\]
The two sides are nonnegative, so after squaring and using \(x\leq a\),
\begin{equation}
  \varepsilon^2M_\varepsilon(x)^2
  <x^2+\varepsilon x+\frac{\varepsilon^2}{4}
  \leq x^2+\varepsilon a+\frac{\varepsilon^2}{4}.
  \label{thin:eq-angular-rounding}
\end{equation}
At a half-integer wall \(x/\varepsilon=m+1/2\), the strict count is \(m\),
so \eqref{thin:eq-angular-rounding} remains strict.  Summing and using
\eqref{thin:eq-active-action-layers} gives
\begin{equation}
  \varepsilon^2
  \sum_{\substack{n\geq1\\x_n<T}}
    M_\varepsilon(R(x_n))^2
  <\sum_{\substack{n\geq1\\x_n<T}}F(x_n)+E,
  \label{thin:eq-complete-angular-error}
\end{equation}
where
\begin{equation}
  E=\left(\frac a\pi+\frac14\right)
     \left(\varepsilon a+\frac{\varepsilon^2}{4}\right).
  \label{thin:eq-angular-error}
\end{equation}

By Lemma~\ref{thin:lem-radial-deficit} and
\(a\geq\pi/(4\varepsilon)\),
\begin{equation}
  \frac{D_{\mathrm{rad}}}{a^2}
  \geq\frac{\rho^2}{4}-\frac{\pi\rho}{4a}
  \geq\frac{(1-\varepsilon)(1-5\varepsilon)}4.
  \label{thin:eq-high-lower-screen}
\end{equation}
The last expression has derivative
\((-6+10\varepsilon)/4<0\) on \(0<\varepsilon\leq1/8\), and therefore
\begin{equation}
  \frac{D_{\mathrm{rad}}}{a^2}\geq\frac{21}{256}.
  \label{thin:eq-high-lower-endpoint}
\end{equation}
On the other hand, expansion of \eqref{thin:eq-angular-error} and
\(1/a\leq4\varepsilon/\pi\) give
\begin{equation}
  \frac{E}{a^2}
  \leq\frac\varepsilon\pi+\frac{\varepsilon^2}\pi
     +\frac{\varepsilon^3}{\pi^2}
     +\frac{\varepsilon^4}{\pi^2}.
  \label{thin:eq-high-upper-screen}
\end{equation}
This scaling is deliberately non-strict: equality occurs at the common
optical face \(a=\pi/(4\varepsilon)\).  The right-hand side is strictly
increasing in \(\varepsilon>0\).  At \(\varepsilon=1/8\), the elementary
strict inequality \(\pi>3\) gives
\begin{equation}
  \frac{E}{a^2}
  \leq\frac1{8\pi}+\frac1{64\pi}
      +\frac1{512\pi^2}+\frac1{4096\pi^2}
  <\frac{193}{4096}.
  \label{thin:eq-high-upper-endpoint}
\end{equation}
Combining \eqref{thin:eq-high-lower-endpoint} and
\eqref{thin:eq-high-upper-endpoint} gives the exact positive reserve
\begin{equation}
  D_{\mathrm{rad}}-E
  >a^2\left(\frac{21}{256}-\frac{193}{4096}\right)
  =\frac{143}{4096}a^2>0.
  \label{thin:eq-high-reserve}
\end{equation}

Equations \eqref{thin:eq-radial-deficit-definition},
\eqref{thin:eq-complete-angular-error}, and
\eqref{thin:eq-high-reserve} now give the complete strict chain
\begin{equation}
  \varepsilon^2
  \sum_{\substack{n\geq1\\x_n<T}}
    M_\varepsilon(R(x_n))^2
  <\sum_{\substack{n\geq1\\x_n<T}}F(x_n)+E
  <\int_0^T F(t)\,dt.
  \label{thin:eq-high-strict-chain}
\end{equation}
By Lemma~\ref{thin:lem-layer-cake}, this is \(P_{\mathcal A}<I\), and hence
\[
  N_D(A_{\rho,1},K^2)
  \leq\frac{2P_{\mathcal A}}{\varepsilon^2}
  <\frac{2I}{\varepsilon^2}
  =\frac{2}{9\pi}(1-\rho^3)K^3.
\]

Every inequality used above includes \(a=\pi/(4\varepsilon)\).  At that
face the non-strict scalings in
\eqref{thin:eq-high-lower-screen}--\eqref{thin:eq-high-upper-screen} are
equalities, but the strict estimate \(\pi>3\) retains the reserve
\eqref{thin:eq-high-reserve}.  Thus the high proof independently owns the
whole common face, including \((\varepsilon,a)=(1/8,2\pi)\).
\end{proof}

\begin{lemma}[Thin-shell endpoint]
\label{lem:thin-shell}
For \(7/8\leq\rho<1\) and \(K\geq0\),
\begin{equation}
  N_D(A_{\rho,1},K^2)
  \leq\frac{2}{9\pi}(1-\rho^3)K^3.
  \label{eq:thin-shell-theorem}
\end{equation}
Equality holds at \(K=0\), and the displayed inequality is strict when
\(K>0\).
\end{lemma}

\begin{proof}
At \(K=0\), positivity of the Dirichlet operator gives a zero strict count,
and the right-hand side is also zero.  Suppose \(K>0\).  Then
\(0<\varepsilon\leq1/8\) and \(a>0\).  The two inclusive intervals
\[
  0\leq a\leq\frac{\pi}{4\varepsilon},
  \qquad
  a\geq\frac{\pi}{4\varepsilon}
\]
cover every \(a\geq0\), with no gap and no third range.  The first is proved
by Proposition~\ref{thin:prop-low-piece}; the second is proved by
Proposition~\ref{thin:prop-high-piece}.  Both propositions include their
common face.  Formula \eqref{thin:eq-weyl-normalization} identifies the
low-piece target with the right-hand side of
\eqref{eq:thin-shell-theorem}.  This completes the proof on the closed face
\(\rho=7/8\) and for every \(7/8<\rho<1\).  The limit
\(\rho\uparrow1\) means \(\varepsilon\downarrow0\) through positive values;
the nonexistent shell \(\varepsilon=0\) is never inserted into a
denominator or treated as part of the domain.
\end{proof}

\begin{remark}[Dependency boundary]
\label{thin:rem-no-lorch}
No finite list of Bessel zeros, no numerical root certificate, and no lower
bound for a first Bessel zero is used in the proof of
Lemma~\ref{lem:thin-shell}.  In particular, the inequalities of Lorch for
\(j_{\nu,1}\) are dependencies of the compact-middle finite-channel
staircase, not of the endpoint \(7/8\leq\rho<1\).  The only non-elementary
input specific to the high piece is the all-domain optimized phase estimate
\eqref{thin:eq-phase-input}, whose proof appears earlier in this manuscript;
all product, action, inverse, curvature, Stieltjes, rounding, seam, and
constant estimates used after that input have been proved above.
\end{remark}

% Self-contained compact-middle proof fragment.
% It assumes only the notation and phase-to-lattice reduction established
% earlier in the manuscript.

\section{The compact-middle argument in full detail}
\label{cm:sec-full}

We retain the strict counting convention
\([x]_<:=\#\{n\in\mathbb N:n<x\}\), put
\[
 W(\rho,K):=\frac{2}{9\pi}(1-\rho^3)K^3,
 \qquad z_\rho:=\frac{\pi}{1-\rho},
 \qquad k_m(\rho):=\sqrt{z_\rho^2+m(m+1)},
\]
and denote by \(q_{\ell,n}(\rho)\) the \(n\)-th positive frequency in
angular channel \(\ell\).  Its multiplicity is \(2\ell+1\).  The phase
reduction proved earlier gives
\begin{equation}
 N_D(A_{\rho,1},K^2)
 \le P_{\rm coarse}(\rho,K)
 :=\sum_{\ell+1/2<K}(2\ell+1)
 \left[A_{\rho,K}(\ell+1/2)+\frac14\right]_<,
 \label{cm:eq-coarse}
\end{equation}
where \(A_{\rho,K}=G_K-G_{\rho K}\) and
\[
 G_a(\nu)=
 \begin{cases}
 \displaystyle\frac1\pi\left(\sqrt{a^2-\nu^2}
 -\nu\arccos\frac\nu a\right),&0\leq\nu<a,\\[4pt]
 0,&\nu\geq a.
 \end{cases}
\]
The value at both interfaces is therefore fixed by zero extension.  This
will matter at \(\nu=\rho K\), at \(\nu=K\), and at every integer proxy
wall.

\subsection{Constants and the primitive analytic envelope}

For \(0\leq s\leq1\), set
\[
 G_1(s)=\frac1\pi\left(\sqrt{1-s^2}-s\arccos s\right),
 \quad
 \omega_0=G_1(1/2)=\frac{\sqrt3}{2\pi}-\frac16,
\]
\[
 C_*=\frac12+\frac{8\sqrt2}{15},\qquad
 C_0=1+\frac{8\sqrt2}{15},\qquad
 \rho_*:=\frac{\omega_0}{1+2C_*}=\frac{\omega_0}{2C_0}.
\]
For \(0<\rho<1\), define
\[
 a_\rho=\frac{2\pi\rho}{1-\rho},\qquad
 \eta_\rho=G_1\!\left(\max\{\rho,1/2\}\right),
\]
\begin{equation}
 K_0(\rho)=
 \left(
 \frac{\sqrt{a_\rho}+\sqrt{a_\rho+4\eta_\rho C_0}}
 {2\eta_\rho}
 \right)^2,
 \qquad
 H_0(\rho)=\frac{C_*}{\omega_0-\rho}\quad(\rho<\omega_0).
 \label{cm:eq-upper-functions}
\end{equation}
We first re-establish every primitive owner that is needed to form the
compact residual.  This prevents the residual description from hiding an
unproved coverage assumption.

\begin{proposition}[Primitive analytic owners]
\label{cm:prop-primitive-owners}
The P\'olya bound holds on each of the following inclusive domains:
\begin{enumerate}
\item \(2\rho K\leq1\);
\item \((1-\rho)K\leq\pi\);
\item \(0<\rho<\omega_0\) and
      \(K(\omega_0-\rho)\geq C_*\), equivalently \(K\geq H_0(\rho)\);
\item \(0<\rho\leq\rho_*\), for every \(K\geq0\);
\item \(K\geq K_0(\rho)\);
\item \(0<1-\rho\leq1/6\) and
      \(K(1-\rho)^2\geq54\);
\item \(7/8\leq\rho<1\), for every \(K\geq0\).
\end{enumerate}
In particular, on the full ratio interval \(0<\rho<1\), the bound holds
whenever \(K\geq295^2\).
\end{proposition}

\begin{proof}
For item 1, \(\mu=\rho K\leq1/2\); every shifted half-integer tail begins
at or above the inner interface and is controlled by the convex high-angular
tail inequality.  Summing the tail integrals with the weighted identity
gives \(N_D\leq W\).  For item 2,
\(K\leq z_\rho=q_{0,1}\), and
\eqref{cm:eq-product-bound} (whose elementary proof is repeated below)
shows that no radial mode is strictly below \(K\).

We record the tail bookkeeping used in items 3--5.  Put
\[
 x_r=r+\frac12,\qquad
 q_\ell=\left\lfloor A_{\rho,K}\!\left(\ell+\frac12\right)
                  +\frac14\right\rfloor
\]
and
\[
 \mathcal T_r=
 \left\lfloor A_{\rho,K}(x_r)+\frac14\right\rfloor
 +2\sum_{j\geq1}
 \left\lfloor A_{\rho,K}(x_r+j)+\frac14\right\rfloor .
\]
All sums are finite because \(A_{\rho,K}=0\) at and beyond \(K\).
For integers \(a<b\), write
\[
 \mathbf T(h,a,b)=\frac12\lfloor h(a)\rfloor
 +\sum_{j=a+1}^{b-1}\lfloor h(j)\rfloor
 +\frac12\lfloor h(b)\rfloor .
\]
The elementary multiplicity identity
\[
 \sum_{\ell\geq0}(2\ell+1)q_\ell
 =\sum_{r\geq0}\left(q_r+2\sum_{\ell>r}q_\ell\right)
 =\sum_{r\geq0}\mathcal T_r
\]
shows that \(P_{\rm coarse}\leq\sum_r\mathcal T_r\).  If every active
tail satisfies
\[
 \mathcal T_r\leq2\int_{x_r}^{K}A_{\rho,K}(z)\,dz,
\]
then, with
\(f_3(z)=\#\{r\geq0:x_r\leq z\}\) and
\(F_3(z)=\int_0^zf_3(t)\,dt\),
\[
 P_{\rm coarse}\leq2\int_0^K f_3(z)A_{\rho,K}(z)\,dz.
\]
Writing \(z=m+1/2+s\), \(m\in\mathbb N_0\), \(0\leq s<1\), gives
\[
 \frac{z^2}{2}-F_3(z)=\frac12\left(s-\frac12\right)^2\geq0;
\]
for \(0\leq z<1/2\), the same inequality is immediate.  Since
\(A_{\rho,K}\) is decreasing, absolutely continuous, and vanishes at
\(K\), integration by parts yields
\[
 P_{\rm coarse}
 \leq-\int_0^Kz^2A_{\rho,K}'(z)\,dz
 =\int_0^K2zA_{\rho,K}(z)\,dz
 =\frac{2}{9\pi}(1-\rho^3)K^3=W(\rho,K).
\]
For the final equality, scaling reduces each \(G_a\)-integral to
\[
 \int_0^1 2xG_1(x)\,dx
 =\frac2\pi\left(\frac13-\frac29\right)=\frac{2}{9\pi}.
\]

We shall use the exact trapezoidal-floor estimates proved in the
one-dimensional reduction.  For a nonnegative concave \(h\),
\(\mathbf T(h,a,b)\leq\int_a^bh(t)\,dt\).  If \(g\) is nonnegative,
decreasing, convex, and \(1/2\)-Lipschitz, vanishes at \(b\), and is
\(1/3\)-Lipschitz after \(t_*\), then
\[
 \mathbf T(g+1/4,a,b)
 \leq\int_a^bg(t)\,dt-\frac14\lfloor g(t_*)\rfloor.
\]
The corresponding shifted convex estimate gives
\(\mathcal T_r\leq2\int_{x_r}^KG_K(z)\,dz\) whenever \(x_r\geq\mu\).
Indeed, on that interval \(A=G_K\), and
\[
 G_K'(z)=-\frac1\pi\arccos\frac zK\in[-1/2,0],
 \qquad
 G_K''(z)=\frac1{\pi\sqrt{K^2-z^2}}>0.
\]

We now prove item 3.  Write \(A=A_{\rho,K}\).  Only a start
\(x_0<\mu=\rho K\) remains.  Put
\[
 n=\lfloor\mu-x_0\rfloor,\qquad q=x_0+n,\qquad
 B=\lceil K-x_0\rceil .
\]
Thus \(q\leq\mu<q+1\), \(n<B\), and zero extension gives
\(G_K(x_0+B)=0\).  The action is concave on \([x_0,q]\), because
\[
 A''(z)=\frac1{\pi\sqrt{K^2-z^2}}
 -\frac1{\pi\sqrt{\mu^2-z^2}}<0\qquad(0<z<\mu).
\]
Moreover \(q\leq\mu=\rho K<\omega_0K<K/2\).  Splitting at \(n\), using
the concave estimate on the head and the improved convex estimate on the
\(G_K\)-suffix with \(t_*=K/2-x_0\), gives, also when \(n=0\),
\[
 \frac{\mathcal T_r}{2}
 \leq\int_{x_0}^{q}A(z)\,dz+\frac n4
 +\int_q^KG_K(z)\,dz-\frac14\lfloor\omega_0K\rfloor.
\]
The only integral mismatch is
\[
 \delta:=\int_q^\mu G_\mu(z)\,dz.
\]
To bound it, write \(t=\cos\theta\).  Concavity of \(\sin\) on
\([0,\pi/4]\) gives
\(\sin(\theta/2)\geq\sqrt2\,\theta/\pi\), hence
\(\arccos t\leq(\pi/2)\sqrt{1-t}\) for \(0\leq t\leq1\).  Since
\[
 G_\mu(z)=\frac1\pi\int_z^\mu\arccos\frac t\mu\,dt,
\]
we obtain
\[
 0\leq\delta
 \leq\frac{2(\mu-q)^{5/2}}{15\sqrt\mu}
 <\frac{2\sqrt2}{15},
\]
where a low tail has \(\mu>x_0\geq1/2\) and \(0\leq\mu-q<1\).
Consequently
\[
 \frac{\mathcal T_r}{2}
 \leq\int_{x_0}^{K}A(z)\,dz
 +\delta-\frac{\lfloor\omega_0K\rfloor-n}{4}.
\]
Finally \(n\leq\rho K-1/2\) and \(\lfloor y\rfloor>y-1\), so
\[
 \lfloor\omega_0K\rfloor-n
 >K(\omega_0-\rho)-\frac12
 \geq C_*-\frac12=\frac{8\sqrt2}{15}>4\delta.
\]
Thus every low-interface tail is strict, every high-interface tail is
non-strict, and the weighted scaffold proves item 3, including the face
\(K(\omega_0-\rho)=C_*\).

For item 4, if \(\mu\leq1/2\) use item 1.  Otherwise \(K>1/(2\rho)\).
Because \(\rho_*=\omega_0/(1+2C_*)\), for
\(0<\rho\leq\rho_*\),
\[
 K(\omega_0-\rho)>
 \frac{\omega_0-\rho}{2\rho}
 \geq\frac{\omega_0-\rho_*}{2\rho_*}=C_*,
\]
and item 3 applies.  All faces are included; at \(K=0\) both sides vanish.

For item 5, fix a low-interface tail \(x_0=r+1/2<\mu\), retain the
preceding definition of \(\mathcal T_r\), and write \(A=A_{\rho,K}\).
Put \(n=\lfloor\mu-x_0\rfloor\), \(q=x_0+n\), and
\(B=\lceil K-x_0\rceil\).  On \([0,n]\),
\(h(t)=A(x_0+t)+1/4\) is decreasing, concave, and Lipschitz with
constant \(c_\rho=\arccos\rho/\pi\).  If \(p\) is the last index of its
first constant ordinary-floor shelf (put \(p=n\) when the shelf never
drops), the concave trapezoidal-floor inequality gives
\begin{equation}
 \mathbf T(h,0,n)
 \leq\int_0^nA(x_0+t)\,dt+\frac n4
 -\frac{1-c_\rho}{2}(n-p).
 \label{cm:eq-fixed-head}
\end{equation}
For \(n=0\), the head is absent and \(p=0\).

Let \(\vartheta=-A'\).  Direct differentiation gives
\[
 \vartheta'(z)=\frac1{\pi\sqrt{\mu^2-z^2}}
 -\frac1{\pi\sqrt{K^2-z^2}}
 \geq\frac{1-\rho}{\pi\rho K}=:\kappa_\rho.
\]
Equal floors on the first shelf imply
\(0\leq A(x_0)-A(x_0+p)<1\), including at an integer endpoint.  Hence
\[
 1>\int_{x_0}^{x_0+p}\vartheta(z)\,dz
 \geq\frac{\kappa_\rho p^2}{2},
 \qquad p<\sqrt{a_\rho K}.
\]

For the convex tail set \(s=\max\{q,K/2\}\).  The function
\(G_K(x_0+t)\) is decreasing and convex, is Lipschitz \(1/2\) on the
whole tail and \(1/3\) after \(s\), and
\(G_K(s)\geq K\eta_\rho\).  The convex trapezoidal-floor inequality
therefore gives
\begin{equation}
 \mathbf T(G_K(x_0+\cdot)+1/4,n,B)
 \leq\int_n^B G_K(x_0+t)\,dt
 -\frac14\lfloor K\eta_\rho\rfloor.
 \label{cm:eq-fixed-tail}
\end{equation}
At \(j=n\), the two half endpoint weights in
\eqref{cm:eq-fixed-head}--\eqref{cm:eq-fixed-tail} majorize the original
full \(A\)-sample.  Their only integral mismatch is
\[
 \delta=\int_q^\mu G_\mu(z)\,dz,
 \qquad 0\leq\delta\leq
 \frac{2(\mu-q)^{5/2}}{15\sqrt\mu}<\frac{2\sqrt2}{15}.
\]
Writing \(d_\rho=1-2c_\rho=2\arcsin\rho/\pi\), combination of the
head and tail yields
\[
 \frac{\mathcal T_r}{2}
 \leq\int_{x_0}^KA(z)\,dz+\delta-\frac M4,
 \quad
 M=\lfloor K\eta_\rho\rfloor+d_\rho(n-p)-p.
\]
Since \(d_\rho>0\) and \(p<\sqrt{a_\rho K}\), the strict floor
inequality, valid even when \(K\eta_\rho\) is an integer, gives
\[
 M>K\eta_\rho-1-\sqrt{a_\rho K}.
\]
Thus the exact sufficient condition is
\begin{equation}
 K\eta_\rho-\sqrt{a_\rho K}\geq C_0.
 \label{cm:eq-fixed-ratio-condition}
\end{equation}
Indeed it implies \(M>8\sqrt2/15>4\delta\), so every low-interface tail
is strictly below twice its action integral.  Tails beginning at or above
\(\mu\) satisfy the non-strict convex high-interface bound; the weighted
identity completes the proof.  The cases \(n=0\), \(p=0\), \(p=n\),
\(q=\mu\), \(q\) on either side of \(K/2\), and all strict-floor walls
are included in the displayed inequalities.

Writing \(Y=\sqrt K\), the left side minus \(C_0\) is
\(\eta_\rho Y^2-\sqrt{a_\rho}Y-C_0\).  It has one positive root, and
the square of that root is precisely \(K_0(\rho)\) in
\eqref{cm:eq-upper-functions}.  Hence \eqref{cm:eq-fixed-ratio-condition}
holds, including equality, exactly for \(K\geq K_0(\rho)\).

We give the seam proof for item 6 because it is the nontrivial owner in the
primitive mask.  Put
\[
 \varepsilon=1-\rho,\quad y=\sqrt\varepsilon,\quad
 \kappa=K\varepsilon^2,\quad \mu=\rho K,\quad
 c=\frac{\arccos\rho}{\pi},\quad d=1-2c,\quad
 \eta=G_1(\rho).
\]
For a shifted low-interface tail beginning at
\(x_0=r_0+1/2<\mu\), write
\[
 n=\lfloor\mu-x_0\rfloor,\quad q=x_0+n,\quad
 \beta=\mu-q,\quad
 h_j=\left\lfloor A(x_0+j)+\frac14\right\rfloor.
\]
Let \(p\) be the last index of the first constant plateau, set
\(m=n-p\), \(R=p-dm\), and use \(p=m=R=0\) if \(n=0\).  The exact
one-tail decomposition is
\begin{equation}
 \frac{\mathcal T_{r_0}}2
 \leq\int_{x_0}^K A(z)\,dz+\delta-\frac M4,
 \quad M=\lfloor K\eta\rfloor-R,
 \quad 0\leq\delta<\frac{2\sqrt2}{15}.
 \label{cm:eq-seam-tail}
\end{equation}
The curvature shelf estimate gives
\begin{equation}
 p<\sqrt{\frac{2\pi\rho K}{\varepsilon}}.
 \label{cm:eq-seam-shelf}
\end{equation}
It remains to prove \(M>4\delta\) on
\(0<y\leq1/\sqrt6\), \(\kappa\geq54\).

Set \(P=py\), \(r=Ry\), and \(S=(p+m)y\).  The elementary half-angle
estimate \(\cos(3\pi/16)<5/6\leq\rho\) gives
\begin{equation}
 d>5/8,\qquad R>0\Longrightarrow
 m<\frac85p,\quad S<\frac{13}{5}P.
 \label{cm:eq-seam-angular}
\end{equation}
With \(t=x_0/(\rho K)\), \(w=1-t\), equations
\eqref{cm:eq-seam-shelf}--\eqref{cm:eq-seam-angular} imply
\[
 w<\widehat q
 :=\frac{y^4+y^3S}{\kappa\rho}
 <\frac1{1620}+\frac{13}{5}\frac{763}{5000}
 =\frac{804689}{2025000}<\frac{159}{400}.
\]
The estimates use only
\(\pi<1571/500\),
\(140/99<\sqrt2<99/70\), and
\(y<49/120\), each proved by positive rational squaring.  In particular,
\(x_0/K>241/480>1/2\).

For \(0<z<\mu\), let \(\sigma(z)=-A'(z)\).  Direct differentiation gives
\[
 \sigma'(z)>0,\qquad
 \sigma(x_0)\geq
 \frac{\varepsilon t}{\pi\sqrt{1-\rho^2t^2}}.
\]
Equal ordinary floors along the plateau imply the strict inequality
\(A(x_0)-A(x_0+p)<1\), even at an integer wall.  Put
\[
 Q=1+\frac{y^2}{\kappa}+\frac{yS}{\kappa}.
\]
Since \(1-\rho^2t^2<2y^2Q\), integration of \(\sigma\) across the
plateau yields
\begin{equation}
 P^2<\frac{2\pi^2Q}{(1-\widehat q)^2}.
 \label{cm:eq-seam-selfconsistent}
\end{equation}
Using \(d>5/8\), replace
\(S\) by \(S_*=(13P-8r)/5\), and define
\[
 Q_*=1+\frac{y^2}{\kappa}+\frac{yS_*}{\kappa},
 \quad q_*=\frac{y^2}{\rho}(Q_*-1),
 \quad H(P,r)=\frac{2\pi^2Q_*}{(1-q_*)^2}.
\]
The right side increases with \(Q_*\), so
\(P^2<H(P,r)\).  Suppose \(r\geq B:=14/3\).  Since
\(R=p-dm\leq p\), one has \(0<r\leq P\).  At fixed \(P\), the quantity
\(S_*(P,r)=(13P-8r)/5\) decreases with \(r\); hence \(Q_*\) and \(q_*\)
also decrease.  Because \(q_*<159/400<1\), the expression
\(2\pi^2Q_*/(1-q_*)^2\) increases with \(Q_*\).  Therefore
\[
 H(P,r)\leq H(P,B).
\]
Now freeze \(r=B\) and follow the entire segment \(B\leq P'\leq P\).
The original shelf ceiling remains valid because \(P'\leq P\), while
\[
 0<S_*(P',B)\leq S_*(P',0)=\frac{13}{5}P'.
\]
Thus the bounds \(q_*<159/400\) and all positive denominators used above
remain valid along the path.  On it,
\[
 \partial_{P'}H(P',B)<\frac{16}{5},\qquad
 \frac{d}{dP'}\bigl(P'^2-H(P',B)\bigr)>\frac{92}{15},
\]
whereas the initial exact reserve is
\[
 B^2-H(B,B)>
 \frac{2505132463469}{2616573970125}>0.
\]
Integration of the positive derivative yields
\[
 P^2-H(P,B)>B^2-H(B,B)>0.
\]
Consequently \(P^2>H(P,B)\geq H(P,r)\), contradicting
\(P^2<H(P,r)\) from \eqref{cm:eq-seam-selfconsistent}.  Hence
\begin{equation}
 R<\frac{14}{3\sqrt\varepsilon}.
 \label{cm:eq-seam-R}
\end{equation}

Finally
\[
 \eta=\frac1\pi\int_0^\varepsilon\arccos(1-v)\,dv
 \geq\frac{2\sqrt2}{3\pi}\varepsilon^{3/2},
\]
so on \(\kappa\geq54\),
\[
 K\eta>\frac{280000}{17281}\frac1y.
\]
If \(R>0\), the strict inequality \(\lfloor x\rfloor>x-1\),
\eqref{cm:eq-seam-R}, and \(1/y>120/49\) give
\[
 M-4\delta>
 \left(\frac{598066}{51843}\right)\frac{120}{49}
 -1-\frac{132}{175}
 =\frac{80132733}{3024175}>0.
\]
If \(R\leq0\), the stronger reserve is
\(114694733/3024175>0\).  Substitution in
\eqref{cm:eq-seam-tail} makes every low-interface tail strictly smaller
than its action integral; high-interface tails are controlled by convexity.
The weighted identity then proves item 6.  This argument includes
\(\kappa=54\), every plateau wall, \(R=0\), every integer
\(K\eta\) wall, and the interface \(x_0=\mu\).
The derivative cap, initial reserve, and terminal rational payments in this
synthetic comparison are regenerated line by line by the exact ledger in
Section~\ref{cm:sec-embedded-analytic-ledgers}.

Item 7 is the two-piece thin-shell theorem proved by the exact product
deficit for low optical frequency and the complementary-action Stieltjes
deficit for high optical frequency.  For completeness, its two closing
reserves are
\[
 \frac25-\left(\frac16+\frac1{32}+\frac1{576}\right)
 =\frac{577}{2880}>0,
 \qquad
 D_{\rm rad}-E>\frac{143}{4096}a^2>0,
\]
with \(a=(1-\rho)K\); the common face is included.  Thus it supplies the
entire closed ratio face \(\rho=7/8\) needed here.

It remains to prove the global frequency stated in the proposition.  On
\([\rho_*,1/16]\), item 3 and the increase of \(H_0\) leave only
\(K<64\).  On
\([1/16,5/6]\), monotonicity of \(K_0\), proved below, and the exact
estimate \(K_0(5/6)<295^2\) leave only \(K<295^2\).  On
\([5/6,7/8]\), item 6 leaves only
\(K<54/(1-\rho)^2\leq3456\).  Item 7 owns every frequency on
\([7/8,1)\).  All threshold faces are included, so \(K=295^2\) is
covered at every ratio.
\end{proof}

Proposition~\ref{cm:prop-primitive-owners} covers the following inclusive
sets in \([\rho_*,7/8]\times[0,\infty)\):
\begin{align*}
 &\rho=\rho_*,\quad \rho=7/8,\quad 2\rho K\leq1,
 \quad (1-\rho)K\leq\pi,\\
 &\rho<\omega_0,\quad K(\omega_0-\rho)\geq C_*,
 \qquad K\geq K_0(\rho),\\
 &0<1-\rho\leq1/6,\quad K(1-\rho)^2\geq54,
 \qquad K\geq295^2.
\end{align*}

Put
\[
 L(\rho)=\max\left\{\frac1{2\rho},\frac\pi{1-\rho}\right\},
\]
and let \(U(\rho)\) be the minimum of all eligible upper owners in
\eqref{cm:eq-upper-functions} and the seam owner \(54/(1-\rho)^2\).
Since every primitive frequency wall is included, exact complementation
gives
\begin{equation}
 \mathcal D_{16}=
 \left\{(\rho,K):\rho_*<\rho<\frac78,\quad
 L(\rho)<K<U(\rho)\right\}.
 \label{cm:eq-D16}
\end{equation}
Both frequency inequalities are strict.

We record the switches, since they determine every later face owner.  The
lower walls meet at
\[
 \rho_c:=\frac1{1+2\pi},\qquad
 L(\rho)=\begin{cases}(2\rho)^{-1},&\rho\leq\rho_c,\\
 z_\rho,&\rho\geq\rho_c.
 \end{cases}
\]
On \((\rho_*,\omega_0)\), substituting \(K=H_0(\rho)\) into the
positive-root equation
\(\eta_\rho K-\sqrt{a_\rho K}-C_0=0\) gives, after a reversible
squaring,
\begin{equation}
 P(\rho):=(1-\rho)\left(C_0\rho-\frac{\omega_0}{2}\right)^2
 -2\pi C_*\rho(\omega_0-\rho)=0.
 \label{cm:eq-Pswitch}
\end{equation}
Here \(C_0\rho-\omega_0/2>0\), and
\[
 P''(\rho)=2C_0^2(1-3\rho)+2C_0\omega_0+4\pi C_*>0.
\]
At \(\rho_*\) the squared term vanishes and the other term is negative,
whereas
\(P(\omega_0)=(1-\omega_0)\omega_0^2C_*^2>0\).  Strict convexity
therefore gives a unique switch \(\rho_{HK}\).  Here is a fully rational
certificate for its locator.  Put
\[
 S_n(x)=\sum_{j=0}^{n-1}\frac{(-1)^jx^{2j+1}}{2j+1}.
\]
The alternating series in Machin's identity gives
\[
\begin{aligned}
 \frac{15707963}{5000000}
 &<16S_6(1/5)-4S_3(1/239)<\pi\\
 &<16S_5(1/5)-4S_2(1/239)
 <\frac{31415927}{10000000}.
\end{aligned}
\]
The two outer gaps are respectively
\[
 \frac{88855616195735287}{1688778771196584375000000},
 \qquad
 \frac{3783145391}{215017724250000000}.
\]
Set these outer bounds equal to \(\pi^-\) and \(\pi^+\), and set
\[
\begin{array}{ll}
 s_2^-=\dfrac{2828427}{2000000},&
 s_2^+=\dfrac{1767767}{1250000},\\[3pt]
 s_3^-=\dfrac{4330127}{2500000},&
 s_3^+=\dfrac{17320509}{10000000}.
\end{array}
\]
Their square-test residuals are
\[
\begin{array}{ll}
2(2000000)^2-2828427^2=705671,&
1767767^2-2(1250000)^2=166289,\\
3(2500000)^2-4330127^2=163871,&
17320509^2-3(10000000)^2=32019081,
\end{array}
\]
so \(s_j^-<\sqrt j<s_j^+\).  Define
\[
 \omega^-=\frac{s_3^-}{2\pi^+}-\frac16,\quad
 \omega^+=\frac{s_3^+}{2\pi^-}-\frac16,\quad
 C_*^\pm=\frac12+\frac8{15}s_2^\pm,\quad
 C_0^\pm=1+\frac8{15}s_2^\pm .
\]
For \(r_-=9407/100000\), monotonic substitution gives
\[
 P(r_-)\leq\mathcal P_-:=
 (1-r_-)(C_0^+r_--\omega^-/2)^2
 -2\pi^-C_*^-r_-(\omega^--r_-),
\]
and exact reduction gives
\[
 \mathcal P_-+\frac1{5000000}
 =-\frac{14699034939621959968377942867507773}
 {2409571458177072753906250000000000000000000}<0.
\]
For \(r_+=94071/1000000\), one first checks
\[
 C_0^-r_+-\frac{\omega^+}{2}-\frac1{10}
 =\frac{619967074526802271}
 {58904861250000000000}>0.
\]
Thus the square has the same monotonic direction, and
\[
 P(r_+)\geq\mathcal P_+:=
 (1-r_+)(C_0^-r_+-\omega^+/2)^2
 -2\pi^+C_*^+r_+(\omega^+-r_+),
\]
where
\[
 \mathcal P_+-\frac7{10000000}
 =\frac{118239888922618787414317706992300967689}
 {3469782678881751562500000000000000000000000000}>0.
\]
Consequently
\[
 \frac{9407}{100000}<\rho_{HK}<\frac{94071}{1000000},
\]
such that \(H_0\) is active below it and \(K_0\) above it.  The locator
is not used as a replacement for the implicit root.

The function \(K_0\) is increasing: \(a_\rho\) increases,
\(\eta_\rho\) is constant up to \(1/2\) and then decreases because
\(G_1'(s)=-\arccos(s)/\pi\), and the positive root of
\(\eta y^2-\sqrt a\,y-C_0=0\) increases with \(a\) and decreases with
\(\eta\).  At \(\rho=5/6\),
\[
 \cos\frac9{10}
 <1-\frac{(9/10)^2}{2}+\frac{(9/10)^4}{24}
 =\frac{49787}{80000}<\frac56,
\]
so \(\arccos(5/6)<9/10\).  Since
\[
 \eta_{5/6}=\frac1\pi\int_{5/6}^1\arccos t\,dt
 <\frac1{6\pi}\arccos\frac56<\frac1{20},
\]
where \(\pi>3\), the positive-root equation implies
\[
 K_0(5/6)>\frac{a_{5/6}}{\eta_{5/6}^2}
 >10\cdot3\cdot20^2=12000,
 \qquad
 \frac{54}{(1-\rho)^2}\leq3456
 \quad(5/6\leq\rho<7/8).
\]
Consequently
\begin{equation}
 U(\rho)=
 \begin{cases}
 H_0(\rho),&\rho_*<\rho<\rho_{HK},\\
 K_0(\rho),&\rho_{HK}\leq\rho<5/6,\\
 54/(1-\rho)^2,&5/6\leq\rho<7/8.
 \end{cases}
 \label{cm:eq-U-piecewise}
\end{equation}
The values agree at \(\rho_{HK}\); the seam face \(\rho=5/6\) is
owned by the third branch.  For the opposite estimate, the inequality
\(\arccos t\geq\sqrt{2(1-t)}\), obtained from
\(\cos u\geq1-u^2/2\), gives
\[
 \eta_{5/6}\geq\frac1\pi\int_{5/6}^1\sqrt{2(1-t)}\,dt
 =\frac1{9\pi\sqrt3}>\frac1{49}.
\]
Indeed, \(\pi<22/7\), while
\(343^2-3\cdot198^2=37>0\), so
\(9\pi\sqrt3<9(22/7)(343/198)=49\).
Also
\[
 a_{5/6}=10\pi<\frac{220}{7}<36,\qquad
 C_0<1+\frac8{15}\frac{99}{70}=\frac{307}{175},
\]
where \(99^2-2\cdot70^2=1>0\).  Therefore, at \(Y=295\),
\[
 \eta_{5/6}Y^2-\sqrt{a_{5/6}}Y-C_0
 >\frac{295^2}{49}-6\cdot295-\frac{307}{175}
 =\frac{5226}{1225}>0,
\]
so \(K_0(5/6)<295^2\).

For the remaining \(H_0\) check, \(\sqrt3>12/7\) and \(\pi<22/7\)
give \(15\sqrt3>8\pi\), hence \(\omega_0>1/10\).  Also
\(\sqrt2<3/2\) gives \(C_*<13/10\).  Consequently
\[
 \omega_0-\frac1{16}>\frac3{80}>\frac{19}{528},
 \qquad
 H_0(1/16)<\frac{13/10}{19/528}
 =\frac{3432}{95}<64.
\]
Together with the seam ceiling \(3456\), this proves that
\(K=295^2\) is covered at every ratio, including equality.

\subsection{Variational comparisons and the complete zero registry}

The transformed channel form is
\[
 \mathfrak a_\ell[u]=\int_\rho^1
 \left(|u'|^2+\frac{\ell(\ell+1)}{r^2}|u|^2\right)dr,
 \qquad D(\mathfrak a_\ell)=H_0^1(\rho,1).
\]
Since \(r^{-2}\geq1\), the min--max principle gives, at every radial
index,
\begin{equation}
 q_{\ell,n}^2\geq n^2z_\rho^2+\ell(\ell+1),
 \qquad q_{0,n}=nz_\rho.
 \label{cm:eq-product-bound}
\end{equation}
Extension by zero from \((\rho,1)\) to \((0,1)\) embeds the shell
fixed-channel form domain isometrically into the ball fixed-channel form
domain.  The zero trace at \(r=\rho\) preserves membership in
\(H_0^1(0,1)\), and Hardy's inequality controls the centrifugal term.
Thus, preserving both \(\ell\) and \(n\),
\begin{equation}
 q_{\ell,n}^2\geq j_{\ell+1/2,n}^2.
 \label{cm:eq-shell-ball}
\end{equation}
The ball forms have the same domain for every angular order; hence, for
\(p\geq\ell\),
\begin{equation}
 j_{p+1/2,n}^2\geq j_{\ell+1/2,n}^2
 +p(p+1)-\ell(\ell+1).
 \label{cm:eq-angular-propagation}
\end{equation}
These are fixed-channel comparisons, not an invocation of unlabelled
global domain monotonicity.

We use the exact elementary enclosure
\begin{equation}
 \frac{333}{106}<\pi<\frac{22}{7}.
 \label{cm:eq-pi}
\end{equation}
For the lower bound, Machin's identity
\(\pi=16\arctan(1/5)-4\arctan(1/239)\) and alternating sums give a
strictly stronger rational bound; for the upper bound,
\[
 0<\int_0^1\frac{x^4(1-x)^4}{1+x^2}\,dx=\frac{22}{7}-\pi.
\]

For clarity we now derive every specialized Bessel-zero inequality used
below, apart from the one published first-zero estimate that is stated
explicitly before specialization.  The spherical Bessel identity and
recurrences are standard \cite{DLMF}.  Set
\[
 \mathsf j_\ell(x)=\sqrt{\frac{\pi}{2x}}J_{\ell+1/2}(x),
 \qquad
 P_\ell(x)=x^{\ell+1}\mathsf j_\ell(x).
\]
Then
\begin{equation}
 P_{\ell+1}=(2\ell+1)P_\ell-x^2P_{\ell-1},
 \qquad P_\ell'=xP_{\ell-1},
 \label{cm:eq-P-recurrence}
\end{equation}
with \(P_0=\sin x\) and \(P_1=\sin x-x\cos x\).  In particular,
\[
\begin{aligned}
P_2={}&(3-x^2)\sin x-3x\cos x,\\
P_3={}&(15-6x^2)\sin x+(x^3-15x)\cos x,\\
P_5={}&(945-420x^2+15x^4)\sin x
       +(-945x+105x^3-x^5)\cos x,\\
P_6={}&(10395-4725x^2+210x^4-x^6)\sin x\\
 &+(-10395x+1260x^3-21x^5)\cos x,\\
P_7={}&(135135-62370x^2+3150x^4-28x^6)\sin x\\
 &+(-135135x+17325x^3-378x^5+x^7)\cos x.
\end{aligned}
\]
Positive zeros are simple by ODE uniqueness.  At a zero of
\(\mathsf j_\ell\), the derivative recurrence gives
\(\mathsf j_{\ell+1}=-\mathsf j_\ell'\).  Combined with
\eqref{cm:eq-angular-propagation}, this gives strict interlacing and makes
the following sign/count ledger a complete enumeration, rather than a
sampled sign test:
\begin{center}
\small
\begin{tabular}{c|c|c|c}
endpoint & half-period & signs \(\mathsf j_0,\ldots,\mathsf j_\ell\)
& zero counts \(N_0,\ldots,N_\ell\)\\ \hline
\(77/10\)&\((2\pi,5\pi/2)\)&\(+,-\)&\(2,1\)\\
\(9\)&\((5\pi/2,3\pi)\)&\(+,+,-\)&\(2,2,1\)\\
\(10\)&\((3\pi,7\pi/2)\)&\(-,+,+,-,-,-,+\)&\(3,2,2,1,1,1,0\)\\
\(103/10\)&\((3\pi,7\pi/2)\)&\(-,+,+,-\)&\(3,2,2,1\)\\
\(21/2\)&\((3\pi,7\pi/2)\)&\(-,+\)&\(3,2\)\\
\(23/2\)&\((7\pi/2,4\pi)\)&\(-,-,+,+,-,-,-,+\)&\(3,3,2,2,1,1,1,0\)\\
\(61/5\)&\((7\pi/2,4\pi)\)&\(-,-,+\)&\(3,3,2\)\\
\(129/10\)&\((4\pi,9\pi/2)\)&\(+,-,-,+,+,-\)&\(4,3,3,2,2,1\)
\end{tabular}
\end{center}
For example, the endpoint signs follow from \eqref{cm:eq-pi}, the displayed
polynomials, and
\(\tan s>s\), \(\tan s>s+s^3/3\),
\(\tan s<s/(1-s^2/2)\) for \(0<s<1\).  The nonautomatic strict
comparisons can be taken as
\[
\begin{array}{c|c}
77/10&5\pi/2-x>3/20>10/77\\
21/2&7\pi/2-x>49/100>2/21\\
9&3\pi-x>21/50>9/26\\
61/5&4\pi-x>9/25>915/3646\\
103/10&7\pi/2-x>69/100>621540/938227\\
129/10&0<x-4\pi<17/50,\quad\tan(x-4\pi)<1700/4711\\
10&4/7<x-3\pi<29/50,\quad\tan(x-3\pi)<2900/4159\\
23/2&53/50<4\pi-x<\pi/2,\quad
\tan(4\pi-x)>546377/375000.
\end{array}
\]
All comparisons are between positive rationals and are checked by cross
multiplication.  The ledger proves
\begin{equation}
\begin{gathered}
 j_{3/2,2}>77/10,\quad j_{5/2,2}>9,\quad
 j_{7/2,2}>103/10,\quad j_{11/2,2}>129/10,\\
 j_{3/2,3}>21/2,\quad j_{5/2,3}>61/5,\\
 j_{13/2,1}>10,\quad j_{15/2,1}>23/2.
\end{gathered}
 \label{cm:eq-internal-zero-registry}
\end{equation}
This includes the requested higher-radial derivations.  For additional
detail, the second root of \(P_3\) is the unique root in
\((3\pi,7\pi/2)\): the derivative chain
\(R'=x\sin x\), \(P_2'=xR\), \(P_3'=xP_2\) first excludes every
earlier cell, and at \(x=103/10\), writing \(y=x-3\pi\), alternating
Taylor bounds give \(\tan y<5/4\), while
\[
 \frac{x(x^2-15)}{6x^2-15}-\frac32=\frac{5917}{621540}>0,
\]
so \(P_3(x)<0\).  Likewise, the third root of \(P_2\) is unique in
\((7\pi/2,4\pi)\); at \(x=61/5\),
\[
 4\pi-x>\frac{97}{265}>
 \frac{3x}{x^2-3},
\]
so \(P_2(x)>0\) before its decreasing zero.  At \(x=129/10\), the
explicit \(P_5\) coefficients and
\(\tan(x-4\pi)<3/8<|B|/A\) give \(P_5(x)<0\); angular propagation of
\(j_{5/2,3}>61/5\) puts the third \(P_5\)-zero above this point, hence
its second zero is also above it.  These arguments use no root table.

For the remaining first zeros we use Lorch's strict first-zero inequality
\cite{Lorch1993}
\[
 j_{\nu,1}^2>
 \frac{24(\nu+1)^2}
 {1-2\nu+\sqrt{(2\nu+3)(2\nu+11)}}-2(\nu^2-1),
 \qquad \nu>-1.
\]
At \(\nu=\ell+1/2\), its right side is
\[
 R_\ell=\frac{3(2\ell+3)\sqrt{(\ell+2)(\ell+6)}
 -2\ell^2+\ell+6}{4}.
\]
Exact positive-side squaring gives
\begin{center}
\small
\begin{tabular}{c|c|c}
\(\ell\)&first-zero wall&integer residual proving \(R_\ell>c^2\)\\ \hline
2&\(51/10\)&\(105/4-(51/10)^2=6/25\)\\
3&\(13/2\)&\(81^2\cdot5-178^2=1121\)\\
4&\(15/2\)&\(66^2\cdot15-247^2=4331\)\\
5&\(87/10\)&\(198189\)\\
8&\(71/6\)&\(1026^2\cdot35-6067^2=35171\)\\
9&\(64/5\)&\(1575^2\cdot165-20059^2=6939644\)\\
10&\(69/5\)&\(3450^2\cdot3-5911^2=767579\).
\end{tabular}
\end{center}
Together with \eqref{cm:eq-internal-zero-registry}, this yields the complete
first-mode walls
\begin{equation}
\begin{array}{c|cccccccccc}
\ell&1&2&3&4&5&6&7&8&9&10\\ \hline
\beta_{\ell,1}&4&51/10&13/2&15/2&87/10&10&23/2&71/6&64/5&69/5.
\end{array}
 \label{cm:eq-first-zero-table}
\end{equation}
The \(\ell=1\) wall follows internally from \(\tan x=x\): the first
positive root lies in \((\pi,3\pi/2)\), and \(\tan4<2<4\).
Applying \eqref{cm:eq-angular-propagation} to the higher-radial seeds gives,
for later use,
\begin{align}
 j_{p+1/2,2}^2&>9409/100+p(p+1) &&(p\geq3),\label{cm:eq-prop-second-a}\\
 j_{p+1/2,3}^2&>3571/25+p(p+1) &&(p\geq2),\label{cm:eq-prop-third}\\
 j_{p+1/2,2}^2&>13641/100+p(p+1) &&(p\geq5).
 \label{cm:eq-prop-second-b}
\end{align}
Equations \eqref{cm:eq-shell-ball}--\eqref{cm:eq-prop-second-b} transfer
every displayed wall to the shell at the same radial index.

\subsection{The first and next angular staircases}

Throughout the staircase and optical calculations below we use the
abbreviation
\[
 z:=z_\rho=\frac{\pi}{1-\rho}.
\]

\begin{lemma}[First two angular bands]
\label{cm:lem-first-bands}
For \(\rho_c\leq\rho\leq7/8\) and
\(z_\rho\leq K\leq k_2(\rho)\), one has
\(N_D(A_{\rho,1},K^2)<W(\rho,K)\).
\end{lemma}

\begin{proof}
Since \(z_\rho>3\), \eqref{cm:eq-product-bound} excludes all \(n\geq2\)
and all \(\ell\geq2\) through \(k_2\).  Thus the strict caps are
\[
 N_D=0\quad(K=z_\rho),\qquad
 N_D\leq1\quad(z_\rho<K\leq k_1),
 \qquad N_D\leq4\quad(k_1<K\leq k_2).
\]
At \(K=k_m\), the newly possible channel \(m\) is excluded because the
count is strict.  At the first wall,
\[
 W(\rho,z_\rho)=\frac{2\pi^2}{9}
 \frac{1+\rho+\rho^2}{(1-\rho)^2}>\frac{2\pi^2}{9}>2>1.
\]
For \(F(\rho)=W(\rho,k_1(\rho))\), direct logarithmic differentiation gives
\[
 \frac{F'}F=\frac{1+2\rho}{1+\rho+\rho^2}
 +\frac{2(\pi^2-(1-\rho)^2)}{(1-\rho)(\pi^2+2(1-\rho)^2)}>0.
\]
At \(\rho_c\), exact substitution of
\(157/50<\pi<22/7\) gives
\[
 F(\rho_c)>
 \frac{388430104857}{92514296875}
 =4+\frac{18372917357}{92514296875}>4.
\]
Strict increase in \(K\) pays both caps and proves the lemma.
\end{proof}

The closed band of Lemma~\ref{cm:lem-first-bands} meets
\(\mathcal D_{16}\) exactly in
\(\rho_c\leq\rho<7/8\), \(z_\rho<K\leq k_2\).  Indeed
\(k_2<K_0\) follows from \(K_0>64\) and \(k_2<27\), and on the seam
\(k_2<27<1944\).  Thus exact subtraction gives
\begin{equation}
\begin{aligned}
 \mathcal D_{17}={}&
 \{\rho_*<\rho<\rho_c:(2\rho)^{-1}<K<U(\rho)\}\\
 &\cup\{\rho_c\leq\rho<7/8:k_2(\rho)<K<U(\rho)\}.
\end{aligned}
 \label{cm:eq-D17}
\end{equation}
The two former pilot rectangles
\[
\begin{aligned}
 B_0&=[999/2000,1001/2000]\times[67/10,168/25],\\
 B_1&=[999/2000,1001/2000]\times[168/25,673/100]
\end{aligned}
\]
are analytically subsumed.  Monotonicity of \(z_\rho,k_2\) and
\eqref{cm:eq-pi} give
\[
 \max z_\rho<\frac{44000}{6993}<\frac{67}{10},
\]
\[
 \min k_2^2-(168/25)^2>\frac{126027526}{626250625}>0,
 \quad
 \min k_2^2-(673/100)^2>\frac{668749071}{10020010000}>0.
\]
Hence no pilot box is subtracted a second time.

\begin{lemma}[Staircase through \(k_5\)]
\label{cm:lem-k5}
For \(\rho_c\leq\rho\leq7/8\) and
\(k_2(\rho)<K\leq k_5(\rho)\), one has \(N_D<W\).
\end{lemma}

\begin{proof}
Put
\[
 c_2=51/10,\qquad c_3=13/2,\qquad c_4=15/2,
 \qquad q_m(\rho)=\max\{k_m(\rho),c_m\}.
\]
The first-zero walls in \eqref{cm:eq-first-zero-table} and
\eqref{cm:eq-product-bound} give the successive caps
\[
 4,\quad 9,\quad 16,\quad 25
\]
on \(K\leq q_2\), \(q_2<K\leq q_3\),
\(q_3<K\leq q_4\), and \(q_4<K\leq k_5\).  Since
\(z\geq\pi+1/2>7/2\), \(4z^2>z^2+30\), so no second radial mode is
present.  The cumulative multiplicities are
\(1,1+3,1+3+5,1+3+5+7,1+3+5+7+9\).

For \(F_a(\rho)=(1-\rho^3)(z_\rho^2+a)^{3/2}\), the sign of
\(F_a'\) is the sign of
\[
 z_\rho^2(1+\rho)-a\rho^2.
\]
It is positive for \(a=6,12,20\) on \([\rho_c,7/8]\).  Thus moving
payments increase with \(\rho\), while fixed-frequency payments decrease.
The following exact split payments cover both one-sided traces:
\begin{center}
\small
\begin{tabular}{c|c|c|c}
cap&split&fixed wall on the left&moving wall on the right\\ \hline
9&\(3/10\)&\(W(3/10,51/10)>9\)&\(W(3/10,k_2)>9\)\\
16&\(1/2\)&\(W(1/2,13/2)=107653/6336>16\)&\(W(1/2,k_3)>196/11>16\)\\
25&\(1/2\)&\(W(1/2,15/2)=165375/6336>25\)&\(W(1/2,k_4)>101528/3960>25\).
\end{tabular}
\end{center}
For cap \(9\), the exact fixed and moving cross-product reserves are
\(12485961\) and \(592618642\), respectively.  Cap \(4\) is paid by
\[
 W(\rho_c,k_2)>\frac7{99}\frac{342}{343}\,73>4.
\]
All inequalities are strict after a channel enters; equality at a zero wall
retains the lower cap.

It remains to compare with the upper owner.  If \(\rho\leq1/2\), then
\(\eta_\rho=\omega_0<1/9\): indeed \(9\sqrt3<5\pi\) follows after
positive squaring from \(\pi>333/106\) and
\(25\cdot333^2-243\cdot106^2=41877>0\).  Since \(k_5\) increases with
\(\rho\),
\[
 k_5(\rho)^2\leq k_5(1/2)^2=4\pi^2+30
 <4\left(\frac{22}{7}\right)^2+30
 =\frac{3406}{49}<81,
\]
and therefore \(\eta_\rho k_5(\rho)<1\).

If \(\rho\geq1/2\), write \(\rho=\cos\theta\).  Then
\(\pi\eta_\rho=\sin\theta-\theta\cos\theta
\leq\theta(1-\rho)\), while \(\theta\leq\pi/3\) and
\(\sqrt{z^2+30}<z+15/z\).  Hence
\[
 \eta_\rho k_5(\rho)
 <\frac\pi3+\frac{5(1-\rho)^2}{\pi}
 \leq\frac\pi3+\frac5{4\pi}
 <\frac{41}{28}<\frac{131}{75}<C_0.
\]
The last chain uses \(3<\pi<22/7\) and
\(\sqrt2>7/5\), the latter because \(2>49/25\).  Thus in both ratio cases
\(\eta_\rho k_5<C_0\).
But \(\eta_\rho K_0=C_0+\sqrt{a_\rho K_0}>C_0\), hence
\(k_5<K_0\).  On the seam, with \(t=1-\rho\leq1/6\),
\[
 t^4k_5^2=t^2\pi^2+30t^4<65/216<2916=t^4U^2.
\]
This proves the lemma on all faces.
\end{proof}

Consequently
\begin{equation}
\begin{aligned}
 \mathcal D_{18}={}&
 \{\rho_*<\rho<\rho_c:(2\rho)^{-1}<K<U(\rho)\}\\
 &\cup\{\rho_c\leq\rho<7/8:k_5(\rho)<K<U(\rho)\}.
\end{aligned}
 \label{cm:eq-D18}
\end{equation}

\subsection{The two-sided staircase}

Put
\[
 \rho_0=\frac1{\sqrt{337}},\qquad d=\frac{\sqrt{337}}2,
 \qquad p_1(\rho)=\sqrt{4z_\rho^2+2}.
\]

\begin{lemma}[High side through \(k_6\)]
\label{cm:lem-k6}
For \(\rho_c\leq\rho\leq7/8\) and
\(z_\rho\leq K\leq k_6(\rho)\), one has \(N_D<W\).
\end{lemma}

\begin{proof}
For \(\rho\leq1/4\), the only possible new modes beyond the first modes
\(\ell=0,\ldots,4\) are \((0,2),(1,2)\); the first \(\ell=5\) mode is
delayed by \(j_{11/2,1}>17/2\).  For \(\rho\geq1/4\),
\(z>4\) makes every second mode absent through \(k_6\), and first modes
\(\ell=0,\ldots,5\) are the complete inventory.  The cumulative first-mode
caps are \(1,4,9,16,25,36\); the two possible second modes give caps
\(26,29\).  Their entry walls are
\[
\begin{array}{c|c}
(1,1)&k_1\\
(2,1)&\max\{k_2,51/10\}\\
(3,1)&\max\{k_3,13/2\}\\
(4,1)&\max\{k_4,15/2\}\\
(5,1)&\max\{k_5,17/2\}\\
(0,2)&2z\\
(1,2)&\max\{p_1,77/10\}.
\end{array}
\]
For a moving wall \(T^2=az^2+b\), \(W(\rho,T)\) increases whenever
\(a\pi^2(1+\rho)>b\rho^2(1-\rho)^2\), which holds here because
\(b/a\leq42\).  Fixed walls decrease with \(\rho\).  Exact payments are
obtained by the splits
\[
 (k_1,1/8,4),\ (k_2,3/10,9),\ (k_3,1/2,16),\
 (k_4,1/2,25),\ (k_5,13/25,36),\ (p_1,1/5,29).
\]
Writing
\(A=a(333/106)^2/(1-r)^2+b\) and
\(B=7(1-r^3)/99\), each moving payment is the positive rational check
\(B^2A^3-C^2>0\).  In the displayed order the numerators are
\[
\begin{gathered}
153864824754340538785,
1399810848073457853053,
137027505353736631,\\
2507119282010251109,
92672404686738742434741,
373255772037478993002833,
\end{gathered}
\]
over positive denominators.  The corresponding fixed-side margins are
positive as well; for example they are
\(1387329/11000000,6277/6336,775/704,452843/343750\), and
\(849901/281250\) at the nontrivial splits.  Finally
\(W(\rho_c,2z)>26\).  Every possible mode is therefore paid, including
coincident entries, and every equality remains assigned to the lower cap.
The exact-ledger supplement in
Section~\ref{cm:sec-embedded-analytic-ledgers} maps every printed moving
numerator and fixed margin to its wall and cap.
\end{proof}

\begin{lemma}[Lower side through \(d\)]
\label{cm:lem-lower-d}
For \(\rho_0<\rho<\rho_c\) and
\((2\rho)^{-1}<K\leq d\), one has \(N_D<W\).
\end{lemma}

\begin{proof}
Because \(3z>d\), every \(n\geq3\) mode is absent.  The zero registry and
angular propagation exclude first modes \(\ell\geq6\) and second modes
\(\ell\geq3\).  The complete cap table is
\[
\begin{array}{c|c}
\text{open-lower, closed-upper range}&N_D\text{ cap}\\ \hline
L<K\leq4&1\\
4<K\leq51/10&4\\
51/10<K\leq13/2,\ K\leq2z&9\\
51/10<K\leq13/2,\ K>2z&10\\
13/2<K\leq15/2,\ K\leq2z&16\\
13/2<K\leq15/2,\ K>2z&17\\
15/2<K\leq77/10&26\\
77/10<K\leq17/2&29\\
17/2<K\leq9&40\\
9<K\leq d&45.
\end{array}
\]
In fact \(13/2<2z<15/2\), so the cap-10 row is empty.  The fixed-wall
lower bounds, using \(\rho<\rho_c<7/50\), exceed their caps by
\[
 \frac{793292}{1546875},\frac{486236661}{1375000000},
 \frac{333100003}{99000000},\frac{329797}{88000},
 \frac{3590476297}{1125000000},\frac{327078887}{99000000},
 \frac{8805519}{1375000},
\]
respectively.  The initial cap is paid by
\(W(\rho_c,L(\rho_c))>19/6>1\), and the moving branch by
\(W(1/19,2z)>508/27>17\).  This proves every row, including \(K=d\).
The same exact-ledger supplement records each margin with its corresponding
row and verifies the moving \(2z\) payment.
\end{proof}

The upper-floor comparisons are strict.  On the lower side,
\(H_0(\rho_*)=(2\rho_*)^{-1}>d\), while
\(K_0>C_0/\omega_0>12>d\).  On the high side, \(K_0>12>k_6\) for
\(\rho\leq1/2\), \(K_0>384>k_6\) for \(1/2<\rho<5/6\), and the seam
owner exceeds \(54>k_6\).  Thus exact subtraction gives
\begin{equation}
\boxed{\begin{aligned}
\mathcal D_{19}={}&
\{\rho_*<\rho\leq\rho_0:(2\rho)^{-1}<K<U(\rho)\}\\
&\cup\{\rho_0<\rho<\rho_c:d<K<U(\rho)\}\\
&\cup\{\rho_c\leq\rho<7/8:k_6(\rho)<K<U(\rho)\}.
\end{aligned}}
\label{cm:eq-D19}
\end{equation}
At \(\rho=\rho_0\), \((2\rho_0)^{-1}=d\), so the would-be new lower
fiber is empty and the first component owns the equality slice.

\subsection{Combined closure of the lower components and the high staircase}

Set
\[
 \sigma:=\frac{3\omega_0}{4}.
\]
We make every comparison in the required ordering explicit.  The
alternating Machin sums give
\[
\begin{aligned}
 \pi
 &<16\left(\frac15-\frac1{3\cdot5^3}
 +\frac1{5\cdot5^5}-\frac1{7\cdot5^7}
 +\frac1{9\cdot5^9}\right)\\
 &\quad-4\left(\frac1{239}-\frac1{3\cdot239^3}\right)
 <\frac{355}{113},
\end{aligned}
\]
and the last gap is exactly
\[
 \frac{45167474711}{189820334689453125}>0.
\]
Since
\[
 3\cdot1101^2\cdot113^2-607^2\cdot355^2=1998482>0,
\]
we have
\[
 \sqrt3>\frac{607\cdot355}{1101\cdot113}
 >\frac{607\pi}{1101},
\]
and therefore
\begin{equation}
 \omega_0=\frac{\sqrt3}{2\pi}-\frac16>\frac{40}{367}.
 \label{cm:eq-omega-lower}
\end{equation}
On the other side,
\[
 25\cdot333^2-243\cdot106^2=41877>0
\]
and \(\pi>333/106\) imply \(9\sqrt3<5\pi\), hence
\(\omega_0<1/9\).  Moreover
\(2\cdot32^2-45^2=23>0\), so
\(\sqrt2>45/32\), \(C_0>7/4\), and
\[
 \rho_*=\frac{\omega_0}{2C_0}<\frac2{63}.
\]
Now all remaining comparisons are witnessed by
\[
\begin{gathered}
 4\cdot337<63^2,\qquad 18^2<337,\qquad
 \frac1{18}<\frac3{40}<\frac{3\omega_0}{4}
 <\frac1{12}<\frac7{51},\\
 \frac7{51}<\frac1{1+2\pi}<\frac17,\qquad
 \frac17<\frac{39}{50}<\frac78.
\end{gathered}
\]
Here the first inequality on the second line uses \(\pi<22/7\), and the
second uses \(\pi>3\).  Thus, without decimal comparison,
\[
 \rho_*<\rho_0<\sigma<\rho_c<\frac{39}{50}<\frac78.
\]

\begin{lemma}[Closure of both lower components of \(\mathcal D_{19}\)]
\label{cm:lem-lower-closure}
The strict inequality \(N_D<W\) holds on the first two components of
\eqref{cm:eq-D19}.
\end{lemma}

\begin{proof}
We divide the proof into a wedge, a finite staircase, and one remaining
floor cell.

For a low-interface tail beginning at \(x_r=r+1/2<\mu=\rho K\), put
\[
 n_r=\lfloor\mu-x_r\rfloor,\qquad
 q_r=x_r+n_r,\qquad p=\lfloor\omega_0K\rfloor.
\]
The concave-head/convex-tail split used in
\eqref{cm:eq-seam-tail}, now with its coarse first-shelf payment, gives
\begin{equation}
 \frac{\mathcal T_r}{2}
 <\int_{x_r}^K A_{\rho,K}(z)\,dz
 +\delta_r-\frac{p-n_r}{4},
 \qquad
 0\leq\delta_r<
 \frac{2(\mu-q_r)^{5/2}}{15\sqrt\mu}.
 \label{cm:eq-lower-wedge-tail}
\end{equation}
When \(n_r=0\), the concave head is absent and the formula follows from
the convex tail alone.  From \eqref{cm:eq-omega-lower} and
\(400\cdot337-367^2=111>0\),
\[
 \omega_0d>
 \frac{40}{367}\frac{\sqrt{337}}2
 =\frac{20\sqrt{337}}{367}>1.
\]
If
\(0<\rho\leq\sigma\), \(K>d\), and \(\rho K>1/2\), then with
\(x=\omega_0K>1\) and \(m=\lfloor x\rfloor\),
\[
 n_r\leq\left\lfloor\frac{3x}{4}-\frac12\right\rfloor<m=p.
\]
Since \(\delta_r<2\sqrt2/15<1/4\), every tail in
\eqref{cm:eq-lower-wedge-tail} is strict.  The hypotheses hold throughout
the first component of \(\mathcal D_{19}\) and on
\(\rho_0\leq\rho\leq\sigma\), \(K>d\).  This includes the complete
\(\rho=\rho_0\) fiber.

For \(\rho_0<\rho<\rho_c\) and \(K\leq\sqrt{114}\), the complete zero
registry and \eqref{cm:eq-angular-propagation} give the following exhaustive
inventory:
\begin{center}
\small
\begin{tabular}{c|l|c}
range (lower face open, upper face closed)&newly possible modes&cap\\ \hline
\(d<K\leq10,\ K\leq3z\)&first \(0{:}5\), second \(0{:}2\)&45\\
\(d<K\leq10,\ K>3z\)&preceding plus \((0,3)\)&46\\
\(10<K\leq81/8\)&plus \((6,1)\), possibly \((0,3)\)&59\\
\(81/8<K\leq21/2\)&plus \((3,2)\)&66\\
\(21/2<K\leq\sqrt{7073}/8\)&plus \((1,3)\)&69\\
\(\sqrt{7073}/8<K\leq\sqrt{114}\)&plus \((4,2)\)&78.
\end{tabular}
\end{center}
First modes \(\ell\geq7\), second modes \(\ell\geq5\), third modes
\(\ell\geq2\), and all \(n\geq4\) are absent.  In particular,
\[
 (81/8)^2+8=7073/64
\]
is the propagated \((4,2)\) wall.  Since \(\rho<\rho_c<1/7\), the
uniform estimate
\[
 W(\rho,K)>
 \frac{2}{9(22/7)}\left(1-\frac1{7^3}\right)K^3
\]
pays the successive caps with exact positive reserves
\[
 \frac{2908}{539},\quad\frac{6199}{539},\quad
 \frac{990435}{137984},\quad\frac{555}{44},\quad\frac{159}{44}.
\]
The first number pays even cap \(46\) from \(K>9\); the last pays cap
\(78\) from \(K>21/2\).  Hence \(K=\sqrt{114}\) is included.

It remains to consider \(\sigma<\rho<\rho_c\) and
\(K>\sqrt{114}\).  Put
\[
 p=\lfloor\omega_0K\rfloor,\qquad
 m=\lfloor\rho K-1/2\rfloor.
\]
Then \(p\geq1\).  Except on
\begin{equation}
 \mathcal B=\left\{\sigma<\rho<\rho_c,\quad K>\sqrt{114},\quad
 \rho K\geq5/2,\quad K<2/\omega_0\right\},
 \label{cm:eq-exceptional-B}
\end{equation}
one has \(m\leq2p-1\).  Indeed this is immediate when \(\rho K<5/2\);
when \(K\geq2/\omega_0\), one has \(p\geq2\).  Moreover,
\[
 \rho_c<\frac17<\frac{60}{367}<\frac{3\omega_0}{2},
\]
where the first and last comparisons were proved above and
\(367<420\).  Hence \(\rho K-1/2<2p\).

Away from a half-integer \(\mu\), all interface remainders in
\eqref{cm:eq-lower-wedge-tail} are equal.  Summing over
\(r=0,\ldots,m\) gives the average floor reserve
\[
 \frac14\left(p-\frac m2\right)\geq\frac18.
\]
For \(m=0\), use \(\delta<1/4\); for \(m\geq1\), \(\mu>3/2\) and
\(\delta<2/(15\sqrt{3/2})<1/8\).  At
\(\mu\in\mathbb Z+1/2\), assign the interface to the high side; then the
remainder is zero and strictness remains in the nonzero convex tail.

On \(\mathcal B\), \(\omega_0>40/367\), so \(K<367/20=:R\).  The
turning estimate
\[
 A_{\rho,K}(z)\leq G_K(z)<\frac{(K-z)^{3/2}}{3\sqrt K}
\]
and monotonicity in \(K\) reduce the proxy count at
\(z_\ell=\ell+1/2\) to
\[
 \frac{(357-20\ell)^3}{1321200}
 <\left(c_\ell+\frac34\right)^2.
\]
The integer numerators of these strict comparisons are
\begin{center}
\small
\begin{tabular}{c|rrrrrrrrrrrrrrr}
\(\ell\)&0&1&2&3&4&5&6&7&8&9&10&11&12&13&14\\ \hline
\(c_\ell\)&6&5&5&4&4&3&3&3&2&2&1&1&1&1&0
\end{tabular}
\end{center}
and, in the same order,
\[
\begin{gathered}
14697882,5409422,11827162,3611502,8555642,
1604782,5267322,8361062,\\
2346202,4446342,176282,1474822,2444562,3133502,286642.
\end{gathered}
\]
The \(\ell=14\) row and monotonicity remove the entire angular tail.
Therefore the full multiplicity cap is
\[
 \sum_{\ell=0}^{13}(2\ell+1)c_\ell=395.
\]
But \(\rho K\geq5/2\), \(\rho<\rho_c<11/80\), and
\(1/\pi>113/355\) give
\[
 W(\rho,K)>
 \frac{160293325}{378004}
 =395+\frac{10981745}{378004}>395.
\]
Thus \(\mathcal B\) is closed as well.  The face \(\rho K=5/2\) is
\(\mathcal B\)-owned and \(K=2/\omega_0\) is aggregate-owned.  All lower
components of \(\mathcal D_{19}\) are proved.
\end{proof}

We now turn to the high component.  Define the strict channel proxy
\begin{equation}
 b_{\ell,n}(z)^2=
 \max\{n^2z^2+\ell(\ell+1),\,\beta_{\ell,n}^2\},
 \label{cm:eq-channel-proxy}
\end{equation}
For the radial channel we set, for every \(n\geq1\),
\[
 \beta_{0,n}:=j_{1/2,n}=n\pi,
\]
the last identity following from
\(J_{1/2}(x)=\sqrt{2/(\pi x)}\sin x\).  For \(\ell\geq1\), the
first-mode \(\beta\)'s are in
\eqref{cm:eq-first-zero-table} and
\[
\begin{aligned}
 \beta_{1,2}&=77/10,&
 \beta_{2,2}&=9,&
 \beta_{3,2}&=103/10,&
 \beta_{4,2}&=\sqrt{11409}/10,\\
 \beta_{5,2}&=129/10,&
 \beta_{1,3}&=21/2,&
 \beta_{2,3}&=61/5.
\end{aligned}
\]
By \eqref{cm:eq-product-bound} and \eqref{cm:eq-shell-ball}, a mode can
be counted only if \(b_{\ell,n}(z)<K\).

\begin{lemma}[Closed high staircase through \(k_{11}\)]
\label{cm:lem-k11}
For \(\rho_c\leq\rho\leq7/8\) and
\(z_\rho\leq K\leq k_{11}(\rho)\), one has \(N_D<W\).
\end{lemma}

\begin{proof}
The exhaustive checkpoint inventories are
\begin{center}
\small
\begin{tabular}{c|l}
checkpoint&possible modes\\ \hline
\(k_7\)&first \(0{:}6\), second \(0{:}1\), no \(n\geq3\)\\
\(k_8\)&first \(0{:}7\), second \(0{:}3\), no \(n\geq3\)\\
\(k_9\)&first \(0{:}8\), second \(0{:}4\), no \(n\geq3\)\\
\(k_{10}\)&first \(0{:}9\), second \(0{:}5\), third \(0{:}1\), no \(n\geq4\)\\
\(k_{11}\)&first \(0{:}10\), second \(0{:}4\), third \(0{:}1\), no \(n\geq4\).
\end{tabular}
\end{center}
For example, at \(k_{11}\) the mode \((5,2)\) would require both
\(z^2<34\) from the product wall and
\(z^2>(129/10)^2-132=3441/100\) from the ball wall, a contradiction.
Also \(4z>k_{11}\) at \(z\geq\pi+1/2\).  Thus radial indices
\(1,2,3,4\) and angular indices through \(11\) are proved above to be
exhaustive for the stated checkpoints.

Writing \(H\) for the highest first channel and \(h\) for the highest
second channel, the block cap is \((H+1)^2+(h+1)^2\), with an additional
\(1\) or \(4\) for third modes.  The complete cap tables at \(k_8\) and
\(k_9\) are
\[
\begin{array}{c|ccccc}
k_8:H\backslash h&\varnothing&0&1&2&3\\ \hline
7&64&65&68&73&80\\
6&49&50&53&-&-\\
5&36&37&40&45&52\\
\leq4&25&26&29&34&41
\end{array}
\qquad
\begin{array}{c|cccccc}
k_9:H\backslash h&\varnothing&0&1&2&3&4\\ \hline
8&81&-&-&-&-&-\\
7&64&65&68&73&-&-\\
6&49&50&53&58&65&74\\
5&36&37&40&45&52&61\\
\leq4&25&26&29&34&41&50.
\end{array}
\]
The dashes follow from incompatible necessary inequalities, not from a
numerical sample.  At \(k_{10}\) the cap lists are
\[
 100;\quad81,97;\quad64,80,89,100;\quad74,69,78,85,89,
\]
and at \(k_{11}\) they are
\[
 121;\quad100,125;\quad106,110;\quad93.
\]

Define the exact finite proxy
\[
 C_z(K)=\sum_{(\ell,n)}(2\ell+1)
 \mathbf1_{\{b_{\ell,n}(z)<K\}},
\]
where the sum runs over the finite inventory above.  Between proxy events
it is constant and \(W\) increases in \(K\).  Every squared event is either
constant or affine in \(z^2\).  At a moving event \(K^2=sz^2+d_0\), the
derivative of its Weyl payment has the sign of
\begin{equation}
 s\pi^2\frac{1+\rho}{(1-\rho)^2}-\rho^2d_0.
 \label{cm:eq-moving-payment-sign}
\end{equation}
Thus the finite split registry
\[
\frac15,\frac3{10},\frac13,\frac38,\frac25,\frac5{12},\frac37,
\frac12,\frac{107}{200},\frac8{15},\frac35,\frac{16}{25},
\frac{13}{20},\frac23,\frac4{25},\frac14,\frac7{20},
\]
together with \(z^2=16,68/3,34\), reduces every cell to exact rational
endpoint arithmetic.  The smallest representative reserves in the six
successive bands are
\[
 \frac{1387329}{11000000},\quad
 \frac{849901}{281250},\quad
 \frac{835355}{577368},\quad
 \frac{835355}{577368},\quad
 \frac{943655}{171072},\quad
 \frac{507845}{261954}.
\]
Every realizable event is strictly paid, with coincident events charged at
their combined multiplicity.

There is one conservative row requiring explicit treatment.  Angular
propagation gives
\[
 j_{9/2,2}^2>\left(\frac{103}{10}\right)^2+8
 =\frac{11409}{100}.
\]
If \((4,2)\) were counted at \(k_9\), this ball wall would force
\(z^2>2409/100\), whereas the product wall forces \(z^2<70/3\); since
\(2409/100-70/3=227/300>0\), the printed cap-74 cell is actually empty.
If one deliberately retains the weaker conservative cell, counting the
mode forces \(K>207/20\) and \(\rho<7/20\).  Therefore
\begin{equation}
 W(\rho,K)>
 \frac{52823261673}{704000000}
 =74+\frac{727261673}{704000000}>74.
 \label{cm:eq-cap74}
\end{equation}
This is the corrected cap-74 payment; it is smaller than the generic
\(k_9\) summary reserve and must not be hidden by a claim that all omitted
cells have larger reserves.

At every \(K=k_m\), the \((m,1)\) mode is on its product equality wall
and is excluded.  At every fixed Bessel wall the zero inequality is strict.
The event calculation therefore covers all equality and coincidence faces,
and proves the lemma.
\end{proof}

The combined finite analytic ledger---covering the zero/sign registry, the
two-sided and lower staircases, the lower closure, the high staircase,
optical constants, and exact subtraction---can be replayed without floating
point.  Its core contains \(488\) substantive rational/radical checks and
\(65\) bookkeeping identities; these are whole-ledger counts, not a count of
\(k_{11}\)-only cells.  It also checks the sign of
\eqref{cm:eq-moving-payment-sign} on the named faces.  Every proof decision
is a cross multiplication or positive-side squaring; decimal displays play
no role.  The complete deterministic registry and executable source are
printed in Section~\ref{cm:sec-embedded-analytic-ledgers}.

\subsection{The optical closure and the exact residual
\texorpdfstring{\(\mathcal D_{20}\)}{D20}}

\begin{lemma}[All-frequency optical theorem]
\label{cm:lem-optical}
For \(39/50\leq\rho<1\) and \(K\geq0\),
\(N_D(A_{\rho,1},K^2)\leq W(\rho,K)\), with strict inequality for
\(K>0\).
\end{lemma}

\begin{proof}
Put \(\varepsilon=1-\rho\leq11/50\),
\(a=\varepsilon K\), and \(c=1126/625\).  We use two inclusive screens
meeting at \(a=c/\varepsilon\).

For the product screen, \eqref{cm:eq-product-bound} implies that a counted
mode satisfies
\[
 n^2\pi^2+\varepsilon^2\ell(\ell+1)<a^2.
\]
There is no mode for \(a\leq\pi\).  For \(a>\pi\), write
\(a/\pi=N+t\), with \(N\geq1\), \(0<t\leq1\), assigning
\((N,t)=(m-1,1)\) at \(a=m\pi\).  If
\[
 M_n=\left\lceil\sqrt{(b_n/\varepsilon)^2+1/4}-1/2\right\rceil,
\]
the exact angular multiplicity is bounded by
\[
 \mathcal P_\varepsilon(a)=\sum_{n=1}^N M_n^2.
\]
Direct summation of the continuous-minus-discrete product deficit gives
\begin{equation}
 \frac{D(a)}{\pi^2}=\frac{N^2}{2}
 +N\left(t^2+\frac16\right)+\frac{2t^3}{3}.
 \label{cm:eq-optical-product-deficit}
\end{equation}
For \(C_D=1382/3125\), the difference
\(D/\pi^2-C_D(N+t)^2\) increases in \(N\), and at \(N=1\) is minimized
at \(t=C_D\), where it equals
\(1822532/91552734375>0\).  Thus \(D>C_Da^2\).

The elementary ceiling bound and quarter-circle integral give
\[
 \varepsilon^2\mathcal P_\varepsilon
 <S_0+\varepsilon a^2/4+\varepsilon^2a/\pi.
\]
On \(a\leq c/\varepsilon\), using \(q=106/333>1/\pi\) and
\(\varepsilon\leq11/50\), the exact reserve is
\begin{equation}
 C_D-\left(\frac{2cq}{3}+\frac{11}{200}
 +(11/50)^2q^2\right)
 =\frac{39569}{2772225000}>0.
 \label{cm:eq-optical-low-reserve}
\end{equation}
This proves the low screen, including all radial and angular equality walls.

For the complementary-action screen, use the inverse-action construction
proved in Lemma~\ref{thin:lem-action-geometry}: let the decreasing shell
action have inverse \(R_{\mathcal A}\), put \(F=R_{\mathcal A}^2\), and
\(g=-F'\).  If \(\tau\) is the actual curvature interface and
\(T=a/\pi\), that lemma gives
\[
 g\text{ decreasing on }(0,\tau),\quad
 g\text{ increasing on }(\tau,T),
\]
\[
 F(0)=a^2,\quad F(\tau)=\rho^2a^2,\quad F(T)=0,\quad
 g(T)=2\pi\rho a.
\]
For \(C(t)=\#\{n:n-1/4<t\}\), set \(w=t-C(t)\) and
\(\Psi(t)=\int_0^tw(s)\,ds-t/4\).  The complete sawtooth and Stieltjes
calculation in Lemma~\ref{thin:lem-radial-deficit}, including the ungridded
curvature interface \(\tau\), gives
\begin{equation}
 D_{\rm rad}:=\int_0^TF(t)\,dt
 -\sum_{n-1/4<T}F(n-1/4)
 \geq\frac{\rho^2a^2}{4}-\frac{\pi\rho a}{4}.
 \label{cm:eq-optical-radial-deficit}
\end{equation}
The exact half-integer angular count from
Lemma~\ref{thin:lem-layer-cake} satisfies
\(\varepsilon^2M_\varepsilon(x)^2<(x+\varepsilon/2)^2\), even on an
angular wall.  Since fewer than \(a/\pi+1/4\) radial layers occur, the
angular error is strictly below
\begin{equation}
 E=\left(\frac a\pi+\frac14\right)
 \left(\varepsilon a+\frac{\varepsilon^2}{4}\right).
 \label{cm:eq-optical-angular-error}
\end{equation}
On \(a\geq c/\varepsilon\), the lower screen from
\eqref{cm:eq-optical-radial-deficit} decreases and the upper screen from
\eqref{cm:eq-optical-angular-error} increases with \(\varepsilon\).  At
\(\varepsilon=11/50\), their exact difference is
\begin{equation}
 \frac{14817541}{472867032960000}>0.
 \label{cm:eq-optical-high-reserve}
\end{equation}
Thus the strict layer-cake sum is below the action integral, and the phase
bridge proves the high screen.  Both screens include
\(a=c/\varepsilon\); at \(K=0\) both sides vanish.
\end{proof}

Combining Lemmas~\ref{cm:lem-lower-closure}, \ref{cm:lem-k11}, and
\ref{cm:lem-optical} with \eqref{cm:eq-D19} leaves exactly
\begin{equation}
 \boxed{
 \mathcal D_{20}=
 \left\{(\rho,K):\rho_c\leq\rho<\frac{39}{50},\quad
 k_{11}(\rho)<K<U(\rho)=K_0(\rho)\right\}.}
 \label{cm:eq-D20}
\end{equation}
Indeed \(k_{11}<U\): on \(\rho\geq\rho_c\),
\(a_\rho\geq1\) and \(\eta_\rho<1/8\), so \(K_0>64\), whereas
\(k_{11}<64\) for \(\rho<7/8\); the seam owner is greater than \(1944\).
On the surviving ratio range neither \(H_0\) nor the seam branch is
eligible, so \(U=K_0\).  The face \(K=k_{11}\) belongs to the closed
staircase, \(\rho=39/50\) belongs to the optical theorem, and \(K=U\)
belongs to the fixed-ratio high-frequency owner.

\subsection{Certified closure of the exact residual
\texorpdfstring{\(\mathcal D_{20}\)}{D20}}

The last step has two parts: a finite compact rectangle and an analytic
tail in \(K\), whose three base signs are certified at \(K=200\).  We state
the certificate predicates explicitly so that the machine's role is
separated from the analytic proof.

\begin{lemma}[Compact rectangle]
\label{cm:lem-compact-certificate}
On the complete closed rectangle
\[
 \frac7{51}\leq\rho\leq\frac{39}{50},\qquad
 12\leq K\leq200,
\]
one has \(N_D(A_{\rho,1},K^2)<W(\rho,K)\).
\end{lemma}

\begin{proof}
For fixed \(\nu\), direct differentiation, with the zero extension at
\(a=\nu\), gives
\[
 \partial_aG_a(\nu)=\frac1\pi\sqrt{1-\frac{\nu^2}{a^2}}
 \quad(a>\nu).
\]
Thus \(A_{\rho,K}(\nu)\) decreases weakly with \(\rho\).  For fixed
\(\rho\),
\[
 \partial_KA_{\rho,K}(\nu)=
 \begin{cases}
 \sqrt{K^2-\nu^2}/(\pi K),&\rho K\leq\nu<K,\\[3pt]
 \bigl(\sqrt{K^2-\nu^2}-\sqrt{\rho^2K^2-\nu^2}\bigr)/(\pi K),
 &\nu<\rho K,
 \end{cases}
\]
and both branches are positive and meet continuously.  The newly active
term at a half-integer \(K=\nu_\ell\) has strict count
\([1/4]_< =0\).  Consequently \(P_{\rm coarse}\) decreases weakly with
\(\rho\) and increases weakly with \(K\), across both interfaces.  Since
\[
 W_\rho=-\frac{2\rho^2K^3}{3\pi}<0,\qquad
 W_K=\frac{2(1-\rho^3)K^2}{3\pi}>0,
\]
every closed rational box
\(B=[\rho_-,\rho_+]\times[K_-,K_+]\) satisfies
\begin{equation}
 P_{\rm coarse}(\rho,K)\leq
 P_{\rm coarse}(\rho_-,K_+),\qquad
 W(\rho,K)\geq W(\rho_+,K_-).
 \label{cm:eq-compact-corners}
\end{equation}

At the proxy corner, for each exact active half-integer
\(\nu_\ell<K_+\), outward ball arithmetic encloses
\[
 X_\ell=A_{\rho_-,K_+}(\nu_\ell)+1/4.
\]
It proposes an integer \(M_\ell\) from the outward upper endpoint but
accepts it only after the certain comparison \(X_\ell\leq M_\ell\).  Then
\begin{equation}
 [X_\ell]_<\leq M_\ell-1,\qquad
 \widehat P_B:=\sum_{\nu_\ell<K_+}(2\ell+1)(M_\ell-1).
 \label{cm:eq-compact-strict-wall}
\end{equation}
This is correct even at \(X_\ell=M_\ell\); an ordinary floor would be
wrong there.  At the opposite corner, an outward lower ball
\(W_{B,-}\leq W(\rho_+,K_-)\) is computed.  A leaf is accepted only if
\begin{equation}
 W_{B,-}-\widehat P_B>0
 \label{cm:eq-compact-leaf-sign}
\end{equation}
is a certain ball comparison.  Equations
\eqref{cm:eq-coarse}, \eqref{cm:eq-compact-corners},
\eqref{cm:eq-compact-strict-wall}, and
\eqref{cm:eq-compact-leaf-sign} then prove the strict theorem on the
entire closed leaf.

Here is the complete deterministic partition algorithm.
\begin{enumerate}
\item Start with the exact rational root
\([7/51,39/50]\times[12,200]\), a stack containing that root at depth
zero, and empty caches for the two monotone corners.
\item Evaluate \eqref{cm:eq-compact-leaf-sign} at 256-bit Arb precision.
If it passes, store the four rational endpoints, depth, and integer
\(\widehat P_B\).
\item If it fails, bisect either \(\rho\) or \(K\) at the exact rational
midpoint.  Both possible bisections are evaluated; a display-only score
chooses the direction, but this score never accepts a box.  Push the two
chosen children, lower child first.  Stop with failure if depth would exceed
30 or the box count would exceed \(100000\).
\item For \(G_a\), decide \(\nu<a\), \(\nu=a\), or \(\nu>a\) by exact
rational comparison before calling square root or arccos.  Enumerate the
active set as
\(\max\{0,\lceil K-1/2\rceil\}\), so \(\nu=K\) is excluded.
\item After termination, sort leaves canonically.  Check positive rational
width, exact total area, every elementary open \(\rho\)-slab, and every
vertical rational face.  Point ownership is lower-closed and upper-open in
each coordinate, except that the two outer upper faces are closed.  The
analytic inequality itself was proved on every closed leaf.
\end{enumerate}
The run terminates with \(10580\) leaves, maximum depth \(15\),
\(16020\) distinct proxy corners, and \(2153076\) certified
Arb-versus-integer comparisons.  There are zero unresolved integer-wall
straddles.  Exact slab, face, and area sweeps certify full coverage and
unique half-open ownership.  At 256 bits the canonical digest of the schema,
precision, root, and every sorted leaf record is
\[
 \mathtt{c0f92eeda050934a147ab6e774c3968c49c38517fc63e46d50d3b4c617fb1a72}.
\]
A separate 384-bit regeneration produces the same leaf count and all strict
signs; its precision-dependent digest is
\[
 \mathtt{4ee16f3bd7e7659fb38b4f63fd51ce0d36740581f7786eb502469da5323fb7aa}.
\]
The complete executable that regenerates both values is printed in
Section~\ref{sec:embedded-certifiers}.  Thus the finite predicates just
described prove the lemma.
\end{proof}

We next reconstruct the aggregate theorem, including the discrete floor
arithmetic that links its continuous reserve to the spectrum.  Put
\[
 d_\rho=\frac{2\arcsin\rho}{\pi},\qquad
 \mu=\rho K,\qquad C=\frac{2\pi\rho K}{1-\rho}.
\]
When \(\mu>1/2\), write uniquely
\[
 \mu-\frac12=J+\tau,\qquad J\in\mathbb N_0,\quad 0\leq\tau<1,
\]
and define
\[
 R=\begin{cases}J,&\tau=0,\\J+1,&\tau>0,
 \end{cases}\qquad x_r=r+\frac12\quad(0\leq r<R).
\]
Then
\begin{equation}
 n_r=\lfloor\mu-x_r\rfloor=J-r,\quad
 q_r=x_r+n_r=J+\frac12,\quad
 \sum_{r=0}^{R-1}n_r=\frac{J(J+1)}2,\quad
 \mu-q_r=\tau.
 \label{cm:eq-aggregate-arithmetic}
\end{equation}
For \(C>0\), set
\begin{equation}
 \mathcal I(C,R)=\frac12\left[
 R\sqrt{R^2+C}+C\operatorname{arsinh}\frac R{\sqrt C}-R^2
 \right].
 \label{cm:eq-I-def}
\end{equation}

\begin{lemma}[Discrete aggregate implication]
\label{cm:lem-Q-implication}
Define
\begin{align}
 \mathcal Q(\rho,K)={}&R\lfloor K\eta_\rho\rfloor
 +d_\rho\frac{J(J+1)}2-(1+d_\rho)\mathcal I(C,R)
 -\frac{8R\tau^{5/2}}{15\sqrt\mu}.
 \label{cm:eq-Q-def}
\end{align}
If \(\mathcal Q(\rho,K)\geq0\), then
\(N_D(A_{\rho,1},K^2)<W(\rho,K)\).
\end{lemma}

\begin{proof}
For the accepted first-shelf length \(p_r\), the curvature bound gives
\[
 p_r<\sqrt{x_r^2+C}-x_r=:f_C(x_r).
\]
The function \(f_C\) is positive and strictly convex.  The midpoint
inequality therefore yields the strict sum
\begin{equation}
 \sum_{r=0}^{R-1}p_r
 <\sum_{r=0}^{R-1}f_C(r+1/2)
 \leq\int_0^Rf_C(x)\,dx=\mathcal I(C,R).
 \label{cm:eq-shelf-integral}
\end{equation}
The interface remainder common to all low tails is zero at \(\tau=0\) and
otherwise satisfies
\[
 0\leq\delta_\tau\leq\frac{2\tau^{5/2}}{15\sqrt\mu}.
\]
The exact concave-head/convex-tail estimate is
\[
 \frac{\mathcal T_r}{2}
 \leq\int_{x_r}^KA(z)\,dz+\delta_\tau
 -\frac14\left(\lfloor K\eta_\rho\rfloor+d_\rho n_r
 -(1+d_\rho)p_r\right).
\]
This formula also holds when \(n_r=0\), with absent head and \(p_r=0\).
Summing and applying \eqref{cm:eq-aggregate-arithmetic} and
\eqref{cm:eq-shelf-integral} gives
\begin{equation}
 \sum_{r<R}\frac{\mathcal T_r}{2}
 -\sum_{r<R}\int_{x_r}^KA(z)\,dz
 <-\frac14\mathcal Q(\rho,K).
 \label{cm:eq-low-tail-Q}
\end{equation}
For \(r\geq R\), \(x_r\geq\mu\), including equality at a half-integer
interface; zero extension and the convex tail inequality give
\(\mathcal T_r\leq2\int_{x_r}^KA\).  Tails beginning at or above \(K\)
vanish.

If \(h_\ell=[A(\ell+1/2)+1/4]_<\), the exact multiplicity identity is
\[
 \sum_{\ell\geq0}(2\ell+1)h_\ell
 =\sum_{r\geq0}\left(h_r+2\sum_{\ell>r}h_\ell\right).
\]
Each parenthesis is bounded by \(\mathcal T_r\); at an integer proxy wall
the strict count is one smaller than the ordinary floor.  Hence
\(\mathcal Q\geq0\) and \eqref{cm:eq-low-tail-Q} imply
\[
 P_{\rm coarse}<2\sum_{r\geq0}\int_{x_r}^KA(z)\,dz
 =2\int_0^Kf_3(z)A(z)\,dz.
\]
The weighted scaffold satisfies
\(\int_0^zf_3(t)\,dt\leq z^2/2\).  Integration by parts, using that
\(A\) decreases and \(A(K)=0\), gives
\[
 2\int_0^Kf_3A\leq\int_0^K2zA(z)\,dz=W(\rho,K).
\]
The first inequality is strict, including \(\tau=0\), every half-integer
\(\mu\), and every integer \(K\eta_\rho\).  Together with
\eqref{cm:eq-coarse}, this proves the lemma.
\end{proof}

For \(K\eta_\rho>1\), define
\[
 b=\frac{2\pi\rho}{1-\rho},\quad
 \overline R=\mu+\frac12,\quad
 S=\sqrt{\overline R^2+bK},
\]
\[
 \overline{\mathcal I}=\frac12\left[
 \overline RS+bK\operatorname{arsinh}\frac{\overline R}{\sqrt{bK}}
 -\overline R^2\right]
\]
and the continuous reserve
\begin{equation}
\begin{aligned}
 \mathcal B(\rho,K)={}&
 (\mu-1/2)(K\eta_\rho-1)
 +\frac{d_\rho}{2}(\mu-3/2)(\mu-1/2)\\
 &-(1+d_\rho)\overline{\mathcal I}
 -\frac{8(\mu+1/2)}{15\sqrt\mu}.
\end{aligned}
 \label{cm:eq-B-def}
\end{equation}
If \(y=K\eta_\rho>1\) and \(\mu>3/2\), then
\[
 R\lfloor y\rfloor>R(y-1)\geq(\mu-1/2)(y-1),
\]
\[
 \frac{d_\rho J(J+1)}2>
 \frac{d_\rho}{2}(\mu-3/2)(\mu-1/2),\quad
 \mathcal I(C,R)<\overline{\mathcal I},\quad
 R\tau^{5/2}<\overline R.
\]
Therefore
\begin{equation}
 \mathcal Q(\rho,K)>\mathcal B(\rho,K),\qquad
 \mathcal B\geq0\Longrightarrow\mathcal Q>0\Longrightarrow N_D<W.
 \label{cm:eq-B-Q-chain}
\end{equation}

\begin{lemma}[Aggregate tail for \(K\geq200\)]
\label{cm:lem-aggregate-tail}
For \(\rho_c\leq\rho\leq39/50\) and \(K\geq200\), one has
\(N_D(A_{\rho,1},K^2)<W(\rho,K)\).
\end{lemma}

\begin{proof}
It suffices to work on the rational superset
\(7/51\leq\rho\leq39/50\).  On it,
\[
 1-\rho\geq11/50,\qquad
 \mu\geq1400/51>3/2.
\]
Moreover
\(G_1(z)=\pi^{-1}\int_z^1\arccos t\,dt\), and
\(\arccos t\geq\sqrt{2(1-t)}\), so
\[
 200\eta_\rho\geq200G_1(39/50)
 >\frac{1400\sqrt2}{33}(11/50)^{3/2}>1;
\]
the square of the last left side is
\(1043504/27225>1\).  Thus all definitions above are valid and
\(S>\overline R>\rho K\).  At \(\rho=1/2\), the constant and variable
definitions of \(\eta_\rho\) agree exactly.

For fixed \(\rho\), write \(I(K)=\overline{\mathcal I}\) and
\(P=S-\overline R\).  Differentiation of
\[
 I(K)=\int_0^{\overline R}(\sqrt{x^2+bK}-x)\,dx
\]
gives
\begin{align}
 I_K&=\rho P+\frac b2
 \operatorname{arsinh}\frac{\overline R}{\sqrt{bK}},
 \label{cm:eq-IK}\\
 I_{KK}&=\rho^2\left(\frac{\overline R}{S}-1\right)
 +\frac{\rho b}{2S}+
 \frac{b(2\rho K-1)}{8KS}.
 \label{cm:eq-IKK}
\end{align}
Consequently
\begin{align}
 \mathcal B_K={}&\rho(K\eta_\rho-1)+(\mu-1/2)\eta_\rho
 +d_\rho\rho(\mu-1)\notag\\
 &-(1+d_\rho)I_K-
 \frac{2\rho(2\mu-1)}{15\mu^{3/2}},
 \label{cm:eq-BK}\\
 E_{KK}&=\frac{\rho^2(2\mu-3)}{15\mu^{5/2}},
 \label{cm:eq-EKK}\\
 \mathcal B_{KK}&=2\rho\eta_\rho+d_\rho\rho^2
 -(1+d_\rho)I_{KK}+E_{KK}.
 \label{cm:eq-BKK}
\end{align}
Since \(S>\overline R>\rho K\), the first term in
\eqref{cm:eq-IKK} is negative and
\begin{equation}
 I_{KK}<\frac{3\rho b}{4S}<\frac{3b}{4K}
 \leq\frac{3b}{800},\qquad E_{KK}>0.
 \label{cm:eq-curvature-chain}
\end{equation}
Define
\[
 F(\rho)=2\rho\eta_\rho+d_\rho\rho^2
 -\frac{3(1+d_\rho)b}{800}.
\]
Equations \eqref{cm:eq-BKK}--\eqref{cm:eq-curvature-chain} prove, for
every \(K\geq200\),
\begin{equation}
 \mathcal B_{KK}(\rho,K)>F(\rho).
 \label{cm:eq-BKK-F}
\end{equation}

The finite certificate at the single base frequency \(K=200\) establishes
on \([7/51,39/50]\) the three strict predicates
\begin{equation}
 \mathcal B(\rho,200)>0,\qquad
 \mathcal B_K(\rho,200)>0,\qquad F(\rho)>0.
 \label{cm:eq-base-predicates}
\end{equation}
We describe its exact validation below.  Assuming only those certified base
signs, \eqref{cm:eq-BKK-F} gives \(\mathcal B_{KK}>0\) at every frequency,
and the two exact integrations
\[
 \mathcal B_K(\rho,K)=\mathcal B_K(\rho,200)
 +\int_{200}^K\mathcal B_{KK}(\rho,s)\,ds>0,
\]
\[
 \mathcal B(\rho,K)=\mathcal B(\rho,200)
 +\int_{200}^K\mathcal B_K(\rho,s)\,ds>0
\]
prove the conclusion for \(K>200\); the base predicates own \(K=200\).
Finally apply \eqref{cm:eq-B-Q-chain}.

For completeness, the base certificate partitions at the formula interface
\(\rho=1/2\).  Starting from \(7/51\), it creates consecutive exact
rational intervals of width \(1/2000\), shortening only the last interval
of each segment.  There are \(726\) intervals on \([7/51,1/2]\) and
\(560\) on \([1/2,39/50]\), hence \(1286\) boxes.  Each is converted
to an outward Arb ball by its exact rational midpoint and radius; the
verifier first proves that both exact endpoints are contained.  At 192-bit
precision it then requires certain signs for
\eqref{cm:eq-base-predicates} and, as consistency checks only,
\[
 1-\rho>0,\quad\mu>3/2,\quad200\eta_\rho>1,\quad
 S>\overline R>200\rho,
\]
\[
 I_{KK}<3b/800,\quad E_{KK}>0,\quad\mathcal B_{KK}>F.
\]
No base consistency check is extrapolated to \(K>200\); that is the role
of \eqref{cm:eq-curvature-chain} and the two integrations.  Exact endpoint
adjacency proves that the boxes tile both segments with no gap or overlap.
A 384-bit replay gives the same strict signs.  The run performs
\(14146\) certain sign comparisons and \(2572\) exact-endpoint containment
checks at each precision.  The canonical certificate digests at 192 and
384 bits are, respectively,
\[
 \mathtt{54e115a05a9257b5b9279c7f79bfe4b866388d2dd2868101181da17ab4bdfc50},
\]
\[
 \mathtt{6f0bc0fcb26cfa78b12d95fa51b20bf3238d801e61d4b11248253f3a2075df92}.
\]
The complete executable is printed in
Section~\ref{sec:embedded-certifiers}.
\end{proof}

\begin{proposition}[Exact closure of \(\mathcal D_{20}\)]
\label{cm:prop-exact-closure}
The compact-middle residual is empty after the preceding two lemmas.
\end{proposition}

\begin{proof}
First, \(\pi<22/7\) gives
\[
 14\pi<44\Longrightarrow7(1+2\pi)<51
 \Longrightarrow \frac7{51}<\rho_c.
\]
Second, on the correctly scoped domain \(\rho_c\leq\rho<1\),
\[
 z_\rho\geq z_{\rho_c}=\pi+\frac12>\frac72,
\]
so
\[
 k_{11}(\rho)^2=z_\rho^2+132>\frac{577}{4}>144,\qquad
 k_{11}(\rho)>12.
\]
The upper wall \(\rho<1\) is essential: \(z_\rho\) is undefined at
\(\rho=1\), and the unqualified assertion for all \(\rho\geq\rho_c\)
would be false, for example at \(\rho=2\).

Define the unique subtraction owners
\[
 \mathcal C_{21}=\mathcal D_{20}\cap\{K\leq200\},\qquad
 \mathcal T_{21}=\mathcal D_{20}\cap\{K>200\}.
\]
Every point of \(\mathcal C_{21}\) lies in the compact rectangle, and
every point of \(\mathcal T_{21}\) lies in the aggregate theorem.  They
are disjoint and exhaust \(\mathcal D_{20}\), with \(K=200\) assigned
only to \(\mathcal C_{21}\).  This remains true whether
\(U(\rho)<200\), \(U(\rho)=200\), or \(U(\rho)>200\).  Therefore
\begin{equation}
 \boxed{\mathcal D_{21}:=\mathcal D_{20}\setminus
 (\mathcal C_{21}\cup\mathcal T_{21})=\varnothing.}
 \label{cm:eq-D21-empty}
\end{equation}
The four inherited faces retain their owners:
\(\rho=\rho_c\) is included subject to the two strict frequency
inequalities, while \(\rho=39/50\), \(K=k_{11}\), and \(K=U\) are
outside \(\mathcal D_{20}\).  The exact classifier printed in
Section~\ref{cm:sec-embedded-analytic-ledgers} enumerates all
\(9\cdot7=63\) listed ratio/frequency state pairs and five separate
interface assertions, and verifies the same disjoint-union truth table.
\end{proof}

\begin{proposition}[Compact-middle P\'olya theorem]
\label{prop:compact-middle}
For every
\[
 \rho_*<\rho<\frac78,\qquad K\geq0,
\]
the Dirichlet counting function of the concentric spherical shell satisfies
\[
 N_D(A_{\rho,1},K^2)\leq W(\rho,K).
\]
\end{proposition}

\begin{proof}
Proposition~\ref{cm:prop-primitive-owners} proves the inequality outside
the exact residual \(\mathcal D_{16}\) in \eqref{cm:eq-D16}.  Within that
residual, Lemmas~\ref{cm:lem-first-bands}, \ref{cm:lem-k5},
\ref{cm:lem-k6}, \ref{cm:lem-lower-d}, \ref{cm:lem-lower-closure},
\ref{cm:lem-k11}, and \ref{cm:lem-optical} remove precisely the regions
subtracted in the definition of \(\mathcal D_{20}\).  Hence any point not
yet owned belongs to
\(\mathcal D_{20}\) in \eqref{cm:eq-D20}.  The compact certificate proves
the inequality on \(\mathcal C_{21}\), and the aggregate certificate proves
it on \(\mathcal T_{21}\).  These two sets are disjoint and exhaust
\(\mathcal D_{20}\), as the exact identity \eqref{cm:eq-D21-empty} shows.
Thus no residual point remains.  The cases on every threshold face have
the explicit owners specified above; in particular, equality at a
frequency wall is not lost in taking complements.  Finally, \(K=0\) is
immediate from \(N_D(A_{\rho,1},0)=W(\rho,0)=0\).  This proves the assertion for
the whole stated parameter range.
\end{proof}

\subsection{Certificate protocol, reproducibility data, and coverage
checklist}
\label{cm:sec-certificate-protocol}

The finite computations above are interval proofs, not floating-point
experiments.  The proof-decision rules are:
\begin{enumerate}
\item all parameter endpoints, subdivisions, active-channel cutoffs, and set
relations use exact integers or rationals;
\item all transcendental values use outward Arb balls at not less than
192-bit midpoint precision;
\item a sign is accepted only by a certain comparison of the complete ball
with zero; a displayed midpoint or decimal is never a predicate;
\item strict integer walls use \([x]_<\leq M-1\) after the certified
comparison \(x\leq M\), never \(\lfloor x\rfloor\) at equality;
\item exact interfaces \(\nu=\rho K\), \(\nu=K\),
\(\rho=1/2\), half-integer \(\mu\), and \(K=200\) have explicit owners;
\item every accepted run is repeated at higher precision, and each complete
deterministic certificate is hashed canonically;
\item the complete replay sources are printed verbatim in
Section~\ref{sec:embedded-certifiers}.  They read no input files, use only
exact rational data and outward Arb balls, and exit nonzero on the first
failed proof predicate.
\end{enumerate}

The final exact replay reports are:
\begin{center}
\small
\begin{tabular}{l|l}
compact, 256 bits&\(10580\) leaves; \(2153076\) floor comparisons; PASS\\
compact, 384 bits&\(10580\) leaves; \(2153076\) floor comparisons; PASS\\
aggregate base, 192 bits&\(1286\) boxes; \(14146\) signs; PASS\\
aggregate base, 384 bits&\(1286\) boxes; \(14146\) signs; PASS\\
exact set logic&\(68\) state/interface checks; disjoint union; PASS.
\end{tabular}
\end{center}
The SHA--256 digests of the two source listings are
\[
\begin{array}{c|c}
\text{compact source}&
\begin{gathered}
\mathtt{bc8c6771a03bde0d0560c41bb254a9db}\\[-2pt]
\mathtt{c128edb53a00555303132a3c1a25a9e5}
\end{gathered}\\
\text{aggregate source}&
\begin{gathered}
\mathtt{e71dde74a259f6c55068c3a77e129898}\\[-2pt]
\mathtt{c22441fe708e3a20f21a65f66821c46e}
\end{gathered}.
\end{array}
\]

\paragraph{Coverage checklist.}
The fragment contains: the exact primitive mask and both active upper
switches; the global \(295^2\) owner; the fixed-channel shell-to-ball and
angular comparisons; all first-, second-, and third-zero bounds used; the
first, next, and two-sided staircases; every printed multiplicity inventory;
the lower shifted-tail wedge and exceptional cap-395 cell; the high
staircase through \(k_{11}\), including the corrected cap-74 cell; both
optical screens; the compact proxy implication; the aggregate discrete
reserve, continuous reserve, derivatives, curvature propagation, and two
integrations; the corrected \(\rho<1\) scope of \(k_{11}>12\); and exact
ownership of \(\rho_c,39/50,k_{11},U,12,200\).

\paragraph{Deterministically regenerated certificate data.}
The \(10580\) individual compact leaf records (four rational endpoints,
depth, and integer proxy cap), the \(1286\) individual aggregate outward
balls and their per-predicate enclosures, and the \(2153076\) individual
Arb-versus-integer channel comparisons are too large to print as raw arrays.
They are deterministic outputs regenerated by the complete sources printed
in Section~\ref{sec:embedded-certifiers}; they are not additional
mathematical assumptions.  The recorded counts, source digests, certificate
digests, and replay results make the regeneration byte-identifiable.
Independent verification should preferably use a separately written
implementation or a second interval library.  The digests identify runs;
they are run metadata, not logical premises.

\section{Proof of the spectral theorem}

We now assemble the regional results without importing any new estimate.
First, elementary bounds give
\[
  3\sqrt3>5>\pi,
\]
and hence \(\omega_0>0\).  Also \(\sqrt3<2\) and \(\pi>3\) give
\(\omega_0<1/6\).  Since \(C_*>0\),
\begin{equation}
  0<\rho_*<\omega_0<\frac16<\frac78.
  \label{eq:ratio-ordering}
\end{equation}
Therefore
\begin{equation}
  (0,1)
  =(0,\rho_*]\mathbin{\dot\cup}
  (\rho_*,7/8)\mathbin{\dot\cup}
  [7/8,1).
  \label{eq:ratio-partition}
\end{equation}

Fix \(0<\rho<1\).  At \(K=0\), positivity in
Proposition~\ref{prop:sc-separated-spectrum} gives
\begin{equation}
  N_D(A_{\rho,1},0)=0=W(\rho,0).
  \label{eq:k-zero}
\end{equation}
Let \(K>0\).  If \(0<\rho\le\rho_*\), apply
Theorem~\ref{thm:sc-small-hole-endpoint}.  If \(\rho_*<\rho<7/8\), apply
Proposition~\ref{prop:compact-middle}.  If \(7/8\le\rho<1\), apply
Lemma~\ref{lem:thin-shell}.  The three cases in
\eqref{eq:ratio-partition} are disjoint and exhaustive, so
\begin{equation}
  N_D(A_{\rho,1},K^2)
  \le\frac{2}{9\pi}(1-\rho^3)K^3
  \qquad(K\ge0).
  \label{eq:unit-shell-theorem}
\end{equation}

Now
\[
  \omega_3=\frac{4\pi}{3},
  \qquad
  L_3=\frac{\omega_3}{(2\pi)^3}=\frac1{6\pi^2},
  \qquad
  |A_{\rho,1}|=\frac{4\pi}{3}(1-\rho^3),
\]
so
\begin{equation}
  L_3|A_{\rho,1}|=\frac{2}{9\pi}(1-\rho^3).
  \label{eq:weyl-normalization}
\end{equation}
Taking \(K=\sqrt\Lambda\) in \eqref{eq:unit-shell-theorem} proves the
unit-shell form of Theorem~\ref{thm:spectral} for every \(\Lambda\ge0\).

For arbitrary \(0<r<R\), put \(\rho=r/R\).  The unitary dilation
\[
  (D_Ru)(x)=R^{-3/2}u(x/R)
\]
maps \(L^2(A_{\rho,1})\) onto \(L^2(A_{r,R})\), and its Dirichlet form
scales by \(R^{-2}\).  Hence
\[
  \lambda_j^D(A_{r,R})=R^{-2}\lambda_j^D(A_{\rho,1}),
\]
and the strict threshold transforms as
\begin{equation}
  N_D(A_{r,R},\Lambda)
  =N_D(A_{\rho,1},R^2\Lambda).
  \label{eq:dilation-count}
\end{equation}
Applying the unit-shell result at \(R^2\Lambda\),
\[
\begin{aligned}
  N_D(A_{r,R},\Lambda)
  &\le\frac{2}{9\pi}(1-\rho^3)(R^2\Lambda)^{3/2}\\
  &=\frac{2}{9\pi}(R^3-r^3)\Lambda^{3/2}\\
  &=L_3|A_{r,R}|\Lambda^{3/2}.
\end{aligned}
\]
This proves Theorem~\ref{thm:spectral} for every \(R>0\), including
\(R<1\).

\section{Proof that spherical shells do not tile}

We prove Theorem~\ref{thm:nontiling} independently of the spectral argument.
Set \(\alpha=r/R\in(0,1)\) and scale by \(1/R\).  It suffices to consider
\[
  T=A_{\alpha,1}=\{x:\alpha<|x|<1\}.
\]
Every rigid motion has the form \(x\mapsto Qx+a\), with \(Q\) orthogonal.
Because \(T\) is radial, \(Q(T)=T\), so every congruent copy is a translate
\[
  T_a=a+T=\{x:\alpha<|x-a|<1\}.
\]

Assume for contradiction that \(\{T_a:a\in\mathfrak C\}\) has
pairwise-disjoint interiors and covers almost everywhere.  Duplicate centers
are impossible because they give the same nonempty open tile.

Fix a unit vector \(e\) and put
\[
  c=\frac{1+\alpha}{2}e,
  \qquad
  \delta=\frac{1-\alpha}{2}.
\]
Write \(B(x,s)=\{y\in\R^3:|y-x|<s\}\) for the open Euclidean ball.
Then \(B(c,\delta)\subset T\).  Therefore \(T_a\) contains
\(B(a+c,\delta)\), and disjointness implies
\begin{equation}
  |a-b|\ge1-\alpha
  \qquad(a\ne b).
  \label{eq:center-separation}
\end{equation}
Thus the centers are locally finite: a bounded set cannot contain infinitely
many points with fixed positive separation.  They are also countable, since
\[
  \mathfrak C
  =\bigcup_{m\ge1}(\mathfrak C\cap\overline B(0,m))
\]
is a countable union of finite sets.

Each tile boundary is a union of two spheres and is three-dimensional null.
The countable union
\[
  Z=\bigcup_{a\in\mathfrak C}\partial T_a
\]
is therefore null.  Exact open-shell coverage is already a special case of
almost-everywhere coverage.  If closed shells cover exactly or almost
everywhere, removing \(Z\) shows that their open interiors still cover almost
everywhere.  Hence it is enough to assume
\begin{equation}
  \left|\R^3\setminus\bigcup_{a\in\mathfrak C}T_a\right|=0.
  \label{eq:ae-coverage}
\end{equation}

Choose one tile \(T_{a_0}\) and its outer sphere
\[
  \Sigma=\{x:|x-a_0|=1\}.
\]
Fix \(p\in\Sigma\) and put \(u=p-a_0\).  For \(n\ge1\), let
\[
  U_n=B\left(p+\frac2n u,\frac1n\right).
\]
Every \(U_n\) lies outside \(T_{a_0}\), is open, and has positive volume.
By \eqref{eq:ae-coverage}, choose \(x_n\in U_n\cap T_{a_n}\) with
\(a_n\ne a_0\).  Since \(x_n\to p\) and \(|x_n-a_n|<1\), the centers
\(a_n\) eventually lie in a fixed bounded set.  Local finiteness lets us
pass to a subsequence with one fixed center \(a\ne a_0\).  Thus
\(p\in\overline{T_a}\).

The point \(p\) is not in \(T_a\).  Otherwise some
\(B(p,\varepsilon)\) lies in \(T_a\).  Choose
\[
  0<t<\min\{\varepsilon,1-\alpha\}.
\]
Then \(p-tu\in T_{a_0}\cap T_a\), contradicting disjoint interiors.
Therefore every \(p\in\Sigma\) belongs to the boundary of a neighboring
tile.

If \(p\in\Sigma\cap\partial T_a\), then
\(|p-a|\in\{\alpha,1\}\), hence \(|a-a_0|\le2\).  Only finitely many
centers satisfy this bound.  Consequently \(\Sigma\) is covered by finitely
many neighboring inner or outer boundary spheres.

Translate so that \(a_0=0\).  The intersection of \(\Sigma\) with a
neighboring sphere \(\{x:|x-a|=s\}\), \(s\in\{\alpha,1\}\), satisfies
\[
  |x|^2=1,
  \qquad |x-a|^2=s^2,
\]
and hence
\begin{equation}
  2a\cdot x=|a|^2+1-s^2.
  \label{eq:sphere-plane}
\end{equation}
Because \(a\ne0\), \eqref{eq:sphere-plane} is a genuine plane.  Its
intersection with \(\Sigma\) is empty, a tangent point, or a circle, and
therefore has zero surface measure on \(\Sigma\).  A finite union of such
sets cannot cover \(\Sigma\), whose area is \(4\pi\).

There is no coincident-sphere exception.  A neighboring outer sphere equals
\(\Sigma\) only when it has the same center, which is the original tile or a
forbidden duplicate.  A neighboring inner sphere cannot equal \(\Sigma\)
because \(\alpha<1\).  We have reached a contradiction.  Scaling back proves
Theorem~\ref{thm:nontiling}.

\appendix

\section{Standalone exact-rational analytic ledgers}
\label{cm:sec-embedded-analytic-ledgers}

The following program is the complete executable source for the finite
arithmetic ledgers used in the seam, two-sided staircase, lower closure, and
high staircase arguments.  It uses only the Python standard library, reads no
file, imports no project module, and has no hidden data input.  Every accepted
predicate is an integer or rational comparison, an integer-square-root
enclosure, or an alternating-series enclosure.  Failure of any predicate
raises an exception and produces a nonzero exit status.

The ordered registry has two named parts.  The core contains \(553\) checks:
\(488\) substantive inequalities or sign implications and \(65\) bookkeeping
identities.  The supplement contains \(58\) checks that attach the printed
seam and two-sided-staircase reserves to their exact wall/cap pairs and record
the \(227/300\) cap--\(74\) incompatibility gap.  Thus the canonical registry
has \(611\) rows.  Importantly, the number \(488\) is the count of the combined
core ledger; it is not a count of \(k_{11}\)-only geometric cells.

The canonicalization is the newline-terminated sequence
\[
 \mathtt{namespace\string\tindex\string\tkind\string\tlabel}.
\]
Its digest identifies the ordered predicates and is not an assumption about
an external artifact.  A successful replay gives
\begin{center}
\small
\begin{tabular}{@{}
>{\raggedright\arraybackslash}p{0.34\linewidth}
>{\raggedright\arraybackslash}p{0.61\linewidth}@{}}
verdict & PASS; first issue: none\\
core checks & \(553=488+65\)\\
supplemental checks & \(58\)\\
combined registry & \(611\) rows\\
canonical registry SHA--256 &
\(
\mathtt{afd7e054f52aa9a3992fc8ef16d3e755}\)
\(\mathtt{1586c76bfb589053714f5f55a36792f1}
\)\\
embedded source SHA--256 &
\(
\mathtt{41691116e0e3e5453b9b209acb93ff78}\)
\(\mathtt{4724c3a95b83c94bbdf7f6760616e716}
\)\\
seam derivative cap &
\(2260740364246/708624500625<16/5\)\\
seam derivative margin & \(6858037754/708624500625\)\\
seam initial reserve & \(2505132463469/2616573970125\)\\
lower-\(d\) moving-\(2z\) lower bound & \(173863/8427>508/27\)\\
cap--\(74\) incompatibility gap & \(227/300\)
\end{tabular}
\end{center}

The replay command is simply
\begin{lstlisting}[language={},caption={Replay command for the exact-rational ledger}]
python verify_analytic_ledgers.py
\end{lstlisting}
No floating-point display is consulted by a proof predicate.  The program
checks the finite arithmetic reductions only; the analytic implications that
reduce the spectral inequalities to these predicates are proved in the main
text.

\begin{lstlisting}[language=Python,caption={Complete standalone exact-rational verifier},label={lst:analytic-ledgers},basicstyle=\ttfamily\tiny]
"""Standalone exact-rational verifier for the finite analytic ledgers.

The program reads no files and has no package dependencies.  Every accepted
predicate is an integer comparison, a ``fractions.Fraction`` comparison, an
integer-square-root enclosure, or an alternating-series enclosure.  It
regenerates the seam constants, the two-sided staircase payment tables, the
high-staircase event registry, and the exact ownership truth table.  A
canonical SHA-256 of the ordered check registry makes independent replays
directly comparable.

This executable verifies the finite arithmetic reductions.  The analytic
steps reducing the spectral problem to these predicates are proved in the
surrounding manuscript and are not silently replaced by computation here.
"""

from __future__ import annotations

from dataclasses import dataclass
from fractions import Fraction as Q
import hashlib
from math import factorial, isqrt
from typing import Callable, Mapping


class VerificationError(AssertionError):
    """First failed exact implication."""


class Ledger:
    def __init__(self) -> None:
        self.labels: list[str] = []
        self.kinds: list[str] = []

    def require(
        self,
        condition: bool,
        label: str,
        detail: str = "",
        *,
        kind: str = "substantive",
    ) -> None:
        if kind not in {"substantive", "bookkeeping", "authentication"}:
            raise ValueError(f"unknown check kind: {kind}")
        if not condition:
            suffix = f": {detail}" if detail else ""
            raise VerificationError(f"{label}{suffix}")
        self.labels.append(label)
        self.kinds.append(kind)

    def counts(self) -> dict[str, int]:
        return {
            kind: sum(observed == kind for observed in self.kinds)
            for kind in ("substantive", "bookkeeping", "authentication")
        }

    def canonical_rows(self, namespace: str) -> tuple[str, ...]:
        """Serialize the ordered registry without platform-dependent data."""

        if len(set(self.labels)) != len(self.labels):
            raise VerificationError(f"duplicate labels in {namespace} registry")
        return tuple(
            f"{namespace}\t{index:04d}\t{kind}\t{label}"
            for index, (kind, label) in enumerate(zip(self.kinds, self.labels), 1)
        )


@dataclass(frozen=True)
class Interval:
    """Closed exact rational interval."""

    lo: Q
    hi: Q

    def __post_init__(self) -> None:
        if self.lo > self.hi:
            raise ValueError("reversed interval")

    @staticmethod
    def point(value: int | Q) -> "Interval":
        value = Q(value)
        return Interval(value, value)

    def __add__(self, other: int | Q | "Interval") -> "Interval":
        other = as_interval(other)
        return Interval(self.lo + other.lo, self.hi + other.hi)

    __radd__ = __add__

    def __neg__(self) -> "Interval":
        return Interval(-self.hi, -self.lo)

    def __sub__(self, other: int | Q | "Interval") -> "Interval":
        return self + (-as_interval(other))

    def __rsub__(self, other: int | Q | "Interval") -> "Interval":
        return as_interval(other) - self

    def __mul__(self, other: int | Q | "Interval") -> "Interval":
        other = as_interval(other)
        products = (
            self.lo * other.lo,
            self.lo * other.hi,
            self.hi * other.lo,
            self.hi * other.hi,
        )
        return Interval(min(products), max(products))

    __rmul__ = __mul__

    def reciprocal(self) -> "Interval":
        if self.lo <= 0 <= self.hi:
            raise ZeroDivisionError("interval contains zero")
        return Interval(Q(1, 1) / self.hi, Q(1, 1) / self.lo)

    def __truediv__(self, other: int | Q | "Interval") -> "Interval":
        return self * as_interval(other).reciprocal()

    def __rtruediv__(self, other: int | Q | "Interval") -> "Interval":
        return as_interval(other) / self

    def __pow__(self, exponent: int) -> "Interval":
        if exponent < 0:
            return (self.reciprocal()) ** (-exponent)
        result = Interval.point(1)
        base = self
        n = exponent
        while n:
            if n & 1:
                result = result * base
            base = base * base
            n //= 2
        return result


def as_interval(value: int | Q | Interval) -> Interval:
    return value if isinstance(value, Interval) else Interval.point(value)


def sqrt_fraction_bounds(value: Q, decimal_digits: int = 50) -> Interval:
    """Certified decimal-grid enclosure of sqrt(value), using integer square roots."""

    if value < 0:
        raise ValueError("negative radicand")
    if value == 0:
        return Interval.point(0)
    scale = 10**decimal_digits
    floor_scaled_square = value.numerator * scale * scale // value.denominator
    root = isqrt(floor_scaled_square)
    lo = Q(root, scale)
    hi = Q(root + 1, scale)
    if not (lo * lo <= value < hi * hi):
        raise VerificationError("integer-square-root enclosure failed")
    return Interval(lo, hi)


def sqrt_interval(value: Interval, decimal_digits: int = 50) -> Interval:
    if value.lo < 0:
        raise ValueError("negative interval radicand")
    return Interval(
        sqrt_fraction_bounds(value.lo, decimal_digits).lo,
        sqrt_fraction_bounds(value.hi, decimal_digits).hi,
    )


def atan_reciprocal_bounds(q: int, terms: int) -> Interval:
    """Alternating-series enclosure for atan(1/q)."""

    x = Q(1, q)
    total = Q(0)
    for k in range(terms):
        term = x ** (2 * k + 1) / (2 * k + 1)
        total += term if k % 2 == 0 else -term
    next_term = x ** (2 * terms + 1) / (2 * terms + 1)
    if terms % 2 == 0:  # next sign is positive
        return Interval(total, total + next_term)
    return Interval(total - next_term, total)


def pi_bounds() -> Interval:
    """Machin: pi = 16 atan(1/5) - 4 atan(1/239)."""

    a = atan_reciprocal_bounds(5, 36)
    b = atan_reciprocal_bounds(239, 12)
    return 16 * a - 4 * b


PI = pi_bounds()


def verify_pi(ledger: Ledger) -> None:
    ledger.require(PI.lo < PI.hi, "Machin interval is nonempty")
    ledger.require(PI.lo > Q(333, 106), "pi > 333/106")
    ledger.require(PI.hi < Q(22, 7), "pi < 22/7")
    ledger.require(Q(106, 333) * PI.lo > 1, "1/pi < 106/333")


def exact_constants() -> dict[str, Interval]:
    sqrt2 = sqrt_fraction_bounds(Q(2))
    sqrt3 = sqrt_fraction_bounds(Q(3))
    sqrt337 = sqrt_fraction_bounds(Q(337))
    omega = sqrt3 / (2 * PI) - Q(1, 6)
    c_star = Q(1, 2) + Q(8, 15) * sqrt2
    c0 = 1 + Q(8, 15) * sqrt2
    rho_star = omega / (1 + 2 * c_star)
    rho0 = 1 / sqrt337
    sigma = Q(3, 4) * omega
    rho_c = 1 / (1 + 2 * PI)
    d = sqrt337 / 2
    return {
        "sqrt2": sqrt2,
        "sqrt3": sqrt3,
        "sqrt337": sqrt337,
        "omega": omega,
        "Cstar": c_star,
        "C0": c0,
        "rho_star": rho_star,
        "rho0": rho0,
        "sigma": sigma,
        "rho_c": rho_c,
        "d": d,
    }


def separated(left: Interval, right: Interval) -> bool:
    return left.hi < right.lo


def verify_thresholds(ledger: Ledger) -> dict[str, Interval]:
    c = exact_constants()
    chain: list[tuple[str, Interval]] = [
        ("rho_*", c["rho_star"]),
        ("rho_0", c["rho0"]),
        ("sigma", c["sigma"]),
        ("rho_c", c["rho_c"]),
        ("39/50", Interval.point(Q(39, 50))),
        ("7/8", Interval.point(Q(7, 8))),
    ]
    for (lname, left), (rname, right) in zip(chain, chain[1:]):
        ledger.require(separated(left, right), f"threshold order {lname} < {rname}")

    ledger.require(separated(c["omega"], c["rho_c"]), "omega_0 < rho_c (H0 ineligible)")
    ledger.require(
        (c["omega"] * c["d"]).lo > 1,
        "omega_0 d > 1",
    )

    sqrt114 = sqrt_fraction_bounds(Q(114))
    c42 = sqrt_fraction_bounds(Q(7073, 64))
    fixed = [
        ("d", c["d"]),
        ("10", Interval.point(10)),
        ("81/8", Interval.point(Q(81, 8))),
        ("21/2", Interval.point(Q(21, 2))),
        ("sqrt(7073)/8", c42),
        ("sqrt(114)", sqrt114),
    ]
    for (lname, left), (rname, right) in zip(fixed, fixed[1:]):
        ledger.require(separated(left, right), f"lower-frequency order {lname} < {rname}")
    ledger.require(Q(7073, 64) == Q(81, 8) ** 2 + 8, "c42 propagation identity")

    z_at_rho0 = PI / (1 - c["rho0"])
    z_at_rhoc = PI + Q(1, 2)  # exact simplification at rho_c
    ledger.require(separated(c["d"], 3 * z_at_rho0), "d < 3 z(rho0)")
    ledger.require((3 * z_at_rho0).hi < 10, "3 z(rho0) < 10")
    ledger.require(separated(sqrt114, 3 * z_at_rhoc), "sqrt(114) < 3 z(rho_c)")

    moving_walls = [
        ("10", Interval.point(10)),
        ("81/8", Interval.point(Q(81, 8))),
        ("21/2", Interval.point(Q(21, 2))),
        ("c42", c42),
        ("sqrt114", sqrt114),
    ]
    crossings: list[tuple[str, Interval]] = []
    for name, wall in moving_walls:
        crossing = 1 - 3 * PI / wall
        ledger.require(separated(c["rho0"], crossing), f"3z={name} crossing above rho0")
        ledger.require(separated(crossing, c["rho_c"]), f"3z={name} crossing below rho_c")
        crossings.append((name, crossing))
    for (lname, left), (rname, right) in zip(crossings, crossings[1:]):
        ledger.require(separated(left, right), f"moving-wall order {lname} before {rname}")

    r_proxy = Interval.point(Q(367, 20))
    ledger.require(separated(sqrt114, 2 / c["omega"]), "sqrt(114) < 2/omega_0")
    ledger.require(separated(2 / c["omega"], r_proxy), "2/omega_0 < 367/20")
    ledger.require(
        separated(c["rho_c"], Q(3, 2) * c["omega"]),
        "rho_c < 3 omega_0/2",
    )
    ledger.require((c["omega"] * sqrt114).lo > 1, "omega_0 sqrt(114) > 1")
    return {**c, "sqrt114": sqrt114, "c42": c42, "R": r_proxy}


def ceil_q(value: Q) -> int:
    return -((-value.numerator) // value.denominator)


def floor_q(value: Q) -> int:
    return value.numerator // value.denominator


def strict_positive_integer_count(value: Q) -> int:
    return max(0, ceil_q(value) - 1)


def verify_strict_face_conventions(ledger: Ledger) -> None:
    for m in range(1, 9):
        ledger.require(
            strict_positive_integer_count(Q(m)) == m - 1,
            f"strict integer bracket at {m}",
        )
        ledger.require(
            strict_positive_integer_count(Q(2 * m + 1, 2)) == m,
            f"strict integer bracket between walls {m}",
        )
    # If x^2=ell(ell+1), y=sqrt(x^2+1/4)-1/2=ell exactly;
    # M=ceil(y)=ell counts ell=0,...,ell-1 and excludes the equality channel.
    for ell in range(0, 12):
        ledger.require(
            sum(2 * j + 1 for j in range(ell)) == ell * ell,
            f"product angular equality excludes ell={ell}",
        )
    # At A+1/4=n, [A+1/4]_< = n-1 and the layer x_n=n-1/4 is excluded.
    for n in range(1, 8):
        ledger.require(
            strict_positive_integer_count(Q(n)) == n - 1,
            f"phase-proxy integer wall n={n}",
        )


def taylor_sin_cos(value: Q, terms: int = 70) -> tuple[Interval, Interval]:
    """Global Taylor enclosures; derivative remainders are bounded by one."""

    sin_sum = Q(0)
    cos_sum = Q(0)
    for k in range(terms):
        sin_term = value ** (2 * k + 1) / factorial(2 * k + 1)
        cos_term = value ** (2 * k) / factorial(2 * k)
        sin_sum += sin_term if k % 2 == 0 else -sin_term
        cos_sum += cos_term if k % 2 == 0 else -cos_term
    sin_err = abs(value) ** (2 * terms) / factorial(2 * terms)
    cos_err = abs(value) ** (2 * terms - 1) / factorial(2 * terms - 1)
    return (
        Interval(sin_sum - sin_err, sin_sum + sin_err),
        Interval(cos_sum - cos_err, cos_sum + cos_err),
    )


def spherical_coefficients(ell: int, x: Q) -> tuple[Q, Q]:
    """Return A,B with spherical_j_ell(x)=A sin(x)+B cos(x)."""

    if x <= 0:
        raise ValueError("x must be positive")
    a0, b0 = Q(1, 1) / x, Q(0)
    if ell == 0:
        return a0, b0
    a1, b1 = Q(1, 1) / (x * x), -Q(1, 1) / x
    if ell == 1:
        return a1, b1
    prev = (a0, b0)
    cur = (a1, b1)
    for l in range(1, ell):
        nxt = (
            Q(2 * l + 1, 1) * cur[0] / x - prev[0],
            Q(2 * l + 1, 1) * cur[1] / x - prev[1],
        )
        prev, cur = cur, nxt
    return cur


def linear_interval(a: Q, x: Interval, b: Q, y: Interval) -> Interval:
    return a * x + b * y


def spherical_sign_at_rational(ell: int, x: Q) -> int:
    a, b = spherical_coefficients(ell, x)
    sin_x, cos_x = taylor_sin_cos(x)
    value = linear_interval(a, sin_x, b, cos_x)
    if value.lo > 0:
        return 1
    if value.hi < 0:
        return -1
    raise VerificationError(f"unresolved exact spherical-Bessel sign ell={ell}, x={x}")


def interval_spherical_coefficients(ell: int, x: Interval) -> tuple[Interval, Interval]:
    a0, b0 = 1 / x, Interval.point(0)
    if ell == 0:
        return a0, b0
    a1, b1 = 1 / (x * x), -(1 / x)
    if ell == 1:
        return a1, b1
    prev = (a0, b0)
    cur = (a1, b1)
    for l in range(1, ell):
        nxt = (
            (2 * l + 1) * cur[0] / x - prev[0],
            (2 * l + 1) * cur[1] / x - prev[1],
        )
        prev, cur = cur, nxt
    return cur


def spherical_sign_at_half_period(ell: int, half_index: int) -> int:
    x = Q(half_index, 2) * PI
    a, b = interval_spherical_coefficients(ell, x)
    phase = half_index % 4
    sin_value = (0, 1, 0, -1)[phase]
    cos_value = (1, 0, -1, 0)[phase]
    value = sin_value * a + cos_value * b
    if value.lo > 0:
        return 1
    if value.hi < 0:
        return -1
    raise VerificationError(
        f"unresolved half-period sign ell={ell}, half_index={half_index}"
    )


@dataclass(frozen=True)
class InternalZeroFace:
    ell: int
    radial: int
    wall: Q
    expected_sign: int
    left_half: int
    right_half: int
    left_sign: int
    right_sign: int


INTERNAL_ZERO_FACES = (
    InternalZeroFace(1, 2, Q(77, 10), -1, 4, 5, -1, 1),
    InternalZeroFace(2, 2, Q(9), -1, 5, 6, -1, 1),
    InternalZeroFace(3, 2, Q(103, 10), -1, 6, 7, -1, 1),
    InternalZeroFace(5, 2, Q(129, 10), -1, 8, 9, -1, 1),
    InternalZeroFace(1, 3, Q(21, 2), 1, 6, 7, 1, -1),
    InternalZeroFace(2, 3, Q(61, 5), 1, 7, 8, 1, -1),
    InternalZeroFace(6, 1, Q(10), 1, 6, 7, 1, -1),
    InternalZeroFace(7, 1, Q(23, 2), 1, 7, 8, 1, -1),
)


LORCH_ZERO_FACES = (
    (8, Q(71, 6)),
    (9, Q(64, 5)),
    (10, Q(69, 5)),
)


def lorch_l2_rhs(ell: int) -> Interval:
    nu = Q(2 * ell + 1, 2)
    radical = sqrt_fraction_bounds((2 * nu + 3) * (2 * nu + 11))
    denominator = 1 - 2 * nu + radical
    if denominator.lo <= 0:
        raise VerificationError(f"Lorch L2 denominator not positive for ell={ell}")
    return 24 * (nu + 1) ** 2 / denominator - 2 * (nu * nu - 1)


def verify_zero_specializations(ledger: Ledger) -> dict[tuple[int, int], Q]:
    registry: dict[tuple[int, int], Q] = {}
    for face in INTERNAL_ZERO_FACES:
        ledger.require(
            (Q(face.left_half, 2) * PI).hi < face.wall,
            f"zero wall ell={face.ell},n={face.radial} right of left half-period",
        )
        ledger.require(
            face.wall < (Q(face.right_half, 2) * PI).lo,
            f"zero wall ell={face.ell},n={face.radial} left of right half-period",
        )
        ledger.require(
            spherical_sign_at_half_period(face.ell, face.left_half) == face.left_sign,
            f"left tangent-cell sign ell={face.ell},n={face.radial}",
        )
        ledger.require(
            spherical_sign_at_half_period(face.ell, face.right_half) == face.right_sign,
            f"right tangent-cell sign ell={face.ell},n={face.radial}",
        )
        ledger.require(
            spherical_sign_at_rational(face.ell, face.wall) == face.expected_sign,
            f"rational zero-wall sign ell={face.ell},n={face.radial}",
        )
        registry[(face.ell, face.radial)] = face.wall * face.wall

    for ell, wall in LORCH_ZERO_FACES:
        rhs = lorch_l2_rhs(ell)
        ledger.require(
            rhs.lo > wall * wall,
            f"Lorch L2 exact specialization ell={ell}",
        )
        ledger.require(
            spherical_sign_at_rational(ell, wall) == 1,
            f"first-zero rational-wall sign ell={ell}",
        )
        registry[(ell, 1)] = wall * wall

    ledger.require(Q(103, 10) > Q(81, 8), "strong j_7/2,2 wall implies 81/8 wall")
    ledger.require(Q(61, 5) > Q(21, 2), "third-mode wall order 21/2 < 61/5")
    return registry


def angular_sum(max_ell: int) -> int:
    return sum(2 * ell + 1 for ell in range(max_ell + 1))


def weyl_interval(rho: Interval, k: Interval) -> Interval:
    return Q(2, 9) * (1 / PI) * (1 - rho**3) * k**3


def verify_lower_inventories_and_payments(
    ledger: Ledger, constants: Mapping[str, Interval]
) -> None:
    # Exclusion/activation arithmetic.  Strict zero walls are analytic inputs;
    # all consequences at included K faces are checked here.
    ledger.require(Q(23, 2) ** 2 > 114, "first ell>=7 absent through sqrt114")
    ledger.require(Q(10) ** 2 == 100, "first ell=6 activation wall 10")
    ledger.require(Q(129, 10) ** 2 > 114, "second ell>=5 absent through sqrt114")
    ledger.require(Q(103, 10) > Q(81, 8), "second ell=3 absent through 81/8")
    ledger.require(
        Q(81, 8) ** 2 + 8 == Q(7073, 64),
        "second ell=4 propagated c42 wall",
    )
    ledger.require(
        Q(81, 8) ** 2 + 18 > 114,
        "second ell>=5 propagated absence",
    )
    ledger.require(Q(21, 2) ** 2 + 4 > 114, "third ell>=2 propagated absence")
    ledger.require((16 * PI**2).lo > 114, "all n>=4 absent through sqrt114")

    expected_caps = (45, 46, 59, 66, 69, 78)
    derived_caps = (
        angular_sum(5) + angular_sum(2),
        angular_sum(5) + angular_sum(2) + 1,
        angular_sum(6) + angular_sum(2) + 1,
        angular_sum(6) + angular_sum(3) + 1,
        angular_sum(6) + angular_sum(3) + 1 + 3,
        angular_sum(6) + angular_sum(4) + 1 + 3,
    )
    ledger.require(
        derived_caps == expected_caps,
        "all six lower inventory caps",
        kind="bookkeeping",
    )

    rho_c = constants["rho_c"]
    payments = (
        (constants["d"], 46, "d"),
        (Interval.point(10), 59, "10"),
        (Interval.point(Q(81, 8)), 66, "81/8"),
        (Interval.point(Q(21, 2)), 69, "21/2"),
        (constants["c42"], 78, "c42"),
    )
    for k, cap, name in payments:
        reserve = weyl_interval(rho_c, k)
        ledger.require(reserve.lo > cap, f"lower Weyl payment above {name} pays cap {cap}")

    proxy_caps = (6, 5, 5, 4, 4, 3, 3, 3, 2, 2, 1, 1, 1, 1)
    ledger.require(
        sum((2 * ell + 1) * cap for ell, cap in enumerate(proxy_caps)) == 395,
        "exceptional-cell proxy cap is exactly 395",
    )
    r = Q(367, 20)
    for ell, cap in enumerate(proxy_caps + (0,)):
        nu = Q(2 * ell + 1, 2)
        radical_1 = sqrt_fraction_bounds(r * r - nu * nu)
        radical_2 = sqrt_fraction_bounds(2 * (1 - nu / r))
        # arccos(x) >= sqrt(2(1-x)); hence this is an exact upper bound for G_R.
        numerator_upper = radical_1.hi - nu * radical_2.lo
        proxy_upper = Interval.point(numerator_upper) / PI + Q(1, 4)
        ledger.require(
            proxy_upper.hi < cap + 1,
            f"strict phase proxy ell={ell} has cap {cap}",
        )
    # G_R is decreasing in nu; ell=14 therefore kills every omitted angular tail.
    tail_caps = proxy_caps + (0,)
    ledger.require(
        tail_caps[-1] == 0 and all(a >= b for a, b in zip(tail_caps, tail_caps[1:])),
        "ell>=14 omitted by monotonicity after exact ell=14 check",
    )

    rho_c_k = Q(5, 2) / rho_c
    exceptional_payment = weyl_interval(rho_c, rho_c_k)
    ledger.require(exceptional_payment.lo > 395, "exceptional cell Weyl payment exceeds 395")

    # Exact floor-cell logic.  p>=1 because omega*K>1.  If p>=2, then
    # rho*K < (3/2)(p+1) <= 2p+1/2, with strictness at p=2.
    ledger.require(Q(3, 2) * 3 == Q(9, 2), "p=2 floor-cell endpoint identity")
    for p in range(2, 10):
        ledger.require(
            Q(3, 2) * (p + 1) <= 2 * p + Q(1, 2),
            f"floor-cell inequality p={p}",
        )
    ledger.require(
        (Q(5, 2) - Q(1, 2)).denominator == 1,
        "rho K=5/2 is assigned to failing high half-integer side",
    )
    normalized_face = Q(2)  # omega_0 K at K=2/omega_0
    endpoint_rho_k = 2 * constants["rho_c"] / constants["omega"]
    ledger.require(
        floor_q(normalized_face) == 2 and endpoint_rho_k.hi < 3,
        "K=2/omega has p=2 and rho*K<3",
    )
    ledger.require(
        endpoint_rho_k.hi - Q(1, 2) < Q(5, 2) and 2 <= 2 * floor_q(normalized_face) - 1,
        "K=2/omega satisfies m<=2p-1 and belongs to the complement",
    )


def propagated_lower_square(
    bases: Mapping[int, Q], target_ell: int
) -> Q | None:
    candidates = [
        square + target_ell * (target_ell + 1) - ell * (ell + 1)
        for ell, square in bases.items()
        if ell <= target_ell
    ]
    return max(candidates) if candidates else None


FIRST_BASES = {
    6: Q(10) ** 2,
    7: Q(23, 2) ** 2,
    8: Q(71, 6) ** 2,
    9: Q(64, 5) ** 2,
    10: Q(69, 5) ** 2,
}
SECOND_BASES = {
    1: Q(77, 10) ** 2,
    2: Q(9) ** 2,
    3: Q(103, 10) ** 2,
    5: Q(129, 10) ** 2,
}
THIRD_BASES = {1: Q(21, 2) ** 2, 2: Q(61, 5) ** 2}


def verify_zero_channel_cover(
    ledger: Ledger,
    checkpoint: int,
    radial: int,
    first_excluded_ell: int,
    bases: Mapping[int, Q],
) -> None:
    mterm = checkpoint * (checkpoint + 1)
    ell = first_excluded_ell
    channel_cut = Q(mterm - ell * (ell + 1), radial * radial - 1)
    zero_sq = propagated_lower_square(bases, ell)
    if zero_sq is None:
        raise VerificationError("missing zero base")
    zero_cut = zero_sq - mterm
    ledger.require(
        zero_cut >= channel_cut,
        f"zero/channel cover k{checkpoint}, n={radial}, ell>={ell}",
        f"zero cut {zero_cut}, channel cut {channel_cut}",
    )


def x_at_ratio(rho: Q) -> Interval:
    return PI**2 / (1 - rho) ** 2


def checkpoint_weyl(rho: Interval, checkpoint: int) -> Interval:
    x = PI**2 / (1 - rho) ** 2
    k = sqrt_interval(x + checkpoint * (checkpoint + 1))
    return weyl_interval(rho, k)


def conditional_first_mode_payment(
    ledger: Ledger, checkpoint: int, wall: Q, cap: int, label: str
) -> None:
    mterm = checkpoint * (checkpoint + 1)
    x0 = wall * wall - mterm
    ledger.require(x0 > 0, f"{label} positive localization x")
    root_x = sqrt_fraction_bounds(x0)
    rho0 = 1 - PI / root_x
    payment = weyl_interval(rho0, Interval.point(wall))
    ledger.require(payment.lo > cap, f"{label} conditional payment > {cap}")


def verify_k9_h6_h4_channel_equality(
    ledger: Ledger,
    channel_wall: Q,
) -> Interval:
    """Require that the supplied wall is exactly the k9 (ell,n)=(4,2) wall."""

    prefix = "k9 H=6,h=4 cap74"
    delta = channel_delta(9, 2, 4, Interval.point(channel_wall))
    ledger.require(
        delta.lo == 0 and delta.hi == 0,
        f"{prefix}: z^2=70/3 is the defining k9 ell=4,n=2 equality",
    )
    return delta


def verify_k9_h6_h4_path(
    ledger: Ledger,
    *,
    channel_wall: Q = Q(70, 3),
) -> dict[str, Q | Interval]:
    """Close the previously missing k9 H=6,h=4 cap-74 payment cell."""

    prefix = "k9 H=6,h=4 cap74"
    base_square = Q(103, 10) ** 2
    propagated_square = base_square + (4 * 5 - 3 * 4)
    ledger.require(
        propagated_square == Q(11409, 100),
        f"{prefix}: ell=3 to ell=4 n=2 propagation square",
    )
    ledger.require(
        propagated_square > 108,
        f"{prefix}: propagated second-mode square exceeds 108",
    )

    equality_delta = verify_k9_h6_h4_channel_equality(ledger, channel_wall)
    ledger.require(
        strict_positive_integer_count(Q(1)) == 0,
        f"{prefix}: strict count excludes the defining equality mode",
    )

    rho_face = Q(7, 20)
    x_face = x_at_ratio(rho_face)
    ledger.require(
        x_face.lo > channel_wall,
        f"{prefix}: rho=7/20 lies on excluded side z^2>70/3",
    )
    ledger.require(
        Q(400, 169) * Q(333, 106) ** 2 - channel_wall
        == Q(36230, 1424163),
        f"{prefix}: exact rational reserve at rho=7/20",
    )
    ledger.require(
        x_face.lo > channel_wall and strict_positive_integer_count(Q(1)) == 0,
        f"{prefix}: a counted ell=4 second mode forces rho<7/20",
    )

    frequency_wall = Q(207, 20)
    ledger.require(
        frequency_wall**2 == Q(42849, 400),
        f"{prefix}: exact (207/20)^2",
    )
    ledger.require(
        frequency_wall**2 < 108 < propagated_square,
        f"{prefix}: counted ell=4 second mode forces K>207/20",
    )

    payment = weyl_interval(Interval.point(rho_face), Interval.point(frequency_wall))
    coarse_payment = (
        Q(2, 9)
        * Q(7, 22)
        * (1 - rho_face**3)
        * frequency_wall**3
    )
    ledger.require(
        coarse_payment == Q(52823261673, 704000000),
        f"{prefix}: exact pi<22/7 Weyl lower payment",
    )
    ledger.require(
        coarse_payment - 74 == Q(727261673, 704000000) > 0,
        f"{prefix}: exact Weyl reserve above cap 74",
    )
    ledger.require(
        payment.lo > coarse_payment > 74,
        f"{prefix}: certified W(7/20,207/20)>74",
    )
    ledger.require(
        49 + 25 == 74,
        f"{prefix}: full first and second multiplicities equal cap 74",
        kind="bookkeeping",
    )
    return {
        "base_square": base_square,
        "propagated_square": propagated_square,
        "channel_wall": channel_wall,
        "equality_delta": equality_delta,
        "rho_face": rho_face,
        "frequency_wall": frequency_wall,
        "coarse_payment": coarse_payment,
        "payment": payment,
    }


def verify_checkpoint_inventories(ledger: Ledger, constants: Mapping[str, Interval]) -> None:
    expected = {
        7: (6, 1, -1, 2),
        8: (7, 3, -1, 2),
        9: (8, 4, -1, 2),
        10: (9, 5, 1, 3),
        11: (10, 4, 1, 3),
    }
    for m, (first_max, second_max, third_max, max_radial) in expected.items():
        ledger.require(first_max == m - 1, f"k{m} strict first-mode upper face")
        for ell in range(m, 12):
            ledger.require(
                ell * (ell + 1) >= m * (m + 1),
                f"k{m} first angular tail excluded at ell={ell}",
            )
        ledger.require(second_max < m, f"k{m} finite second inventory")
        if third_max >= 0:
            ledger.require(third_max == 1, f"k{m} third inventory ell=0,1")
        ledger.require(max_radial in (2, 3), f"k{m} stated maximal radial index")

    verify_zero_channel_cover(ledger, 7, 2, 2, SECOND_BASES)
    verify_zero_channel_cover(ledger, 8, 2, 4, SECOND_BASES)
    verify_zero_channel_cover(ledger, 9, 2, 5, SECOND_BASES)
    verify_zero_channel_cover(ledger, 10, 2, 6, SECOND_BASES)
    verify_zero_channel_cover(ledger, 11, 2, 5, SECOND_BASES)

    x_min = (PI + Q(1, 2)) ** 2
    ledger.require(x_min.lo > Q(90, 8), "no third modes at k7,k8,k9")
    verify_zero_channel_cover(ledger, 10, 3, 2, THIRD_BASES)
    verify_zero_channel_cover(ledger, 11, 3, 2, THIRD_BASES)
    ledger.require(x_min.lo > Q(132, 15), "no radial n>=4 through k11")

    # Every omitted angular tail is monotone: the propagated zero cut increases
    # and the channel cut decreases with ell.  The base-ell cover therefore
    # proves all remaining indices, not merely ell<=11.
    for m, first_ell in ((7, 2), (8, 4), (9, 5), (10, 6), (11, 5)):
        M = m * (m + 1)
        previous_zero = None
        previous_channel = None
        for ell in range(first_ell, 13):
            zcut = propagated_lower_square(SECOND_BASES, ell) - M  # type: ignore[operator]
            ccut = Q(M - ell * (ell + 1), 3)
            if previous_zero is not None:
                ledger.require(zcut > previous_zero, f"k{m} zero cut increases at ell={ell}")
                ledger.require(ccut < previous_channel, f"k{m} channel cut decreases at ell={ell}")
            previous_zero, previous_channel = zcut, ccut


def verify_cap_tables_and_payments(ledger: Ledger, constants: Mapping[str, Interval]) -> None:
    # k7
    ledger.require(
        (25, 36, 49) == tuple((h + 1) ** 2 for h in (4, 5, 6)),
        "k7 first caps",
        kind="bookkeeping",
    )
    ledger.require(1 + 3 == 4, "k7 two second modes add 1+3", kind="bookkeeping")

    # k8 and k9 rectangular tables: every numerical entry is exactly the sum
    # of a full first block and a full second block.
    k8 = {
        7: (64, 65, 68, 73, 80),
        6: (49, 50, 53, None, None),
        5: (36, 37, 40, 45, 52),
        4: (25, 26, 29, 34, 41),
    }
    for h_first, row in k8.items():
        for col, value in enumerate(row):
            if value is not None:
                expected = (h_first + 1) ** 2 + (0 if col == 0 else col * col)
                ledger.require(
                    value == expected,
                    f"k8 cap H={h_first}, column={col}",
                    kind="bookkeeping",
                )

    k9 = {
        8: (81, None, None, None, None, None),
        7: (64, 65, 68, 73, None, None),
        6: (49, 50, 53, 58, 65, 74),
        5: (36, 37, 40, 45, 52, 61),
        4: (25, 26, 29, 34, 41, 50),
    }
    for h_first, row in k9.items():
        for col, value in enumerate(row):
            if value is not None:
                expected = (h_first + 1) ** 2 + (0 if col == 0 else col * col)
                ledger.require(
                    value == expected,
                    f"k9 cap H={h_first}, column={col}",
                    kind="bookkeeping",
                )

    verify_k9_h6_h4_path(ledger)

    # Marked impossible cells, proved from simultaneous strict necessary walls.
    ledger.require(Q(100 - 72) > Q(72 - 6, 3), "k8 H=6 with h>=2 impossible")
    ledger.require(Q(71, 6) ** 2 - 90 > Q(90, 3), "k9 H=8 with any second impossible")
    ledger.require(Q(23, 2) ** 2 - 90 > Q(90 - 12, 3), "k9 H=7 with h>=3 impossible")

    k10_cases = (
        (100, 100, "H9 no radial"),
        (81, 81, "H8 no second"),
        (81 + 16, 97, "H8 h<=3"),
        (64, 64, "H7 no second"),
        (64 + 16, 80, "H7 h<=3"),
        (64 + 25, 89, "H7 h=4"),
        (64 + 36, 100, "H7 h=5"),
        (49 + 25, 74, "H<=6 h<=4 no third"),
        (49 + 16 + 4, 69, "H<=6 h<=3 third"),
        (49 + 25 + 4, 78, "H<=6 h=4 third"),
        (49 + 36, 85, "H<=6 h=5 no third"),
        (49 + 36 + 4, 89, "H<=6 h=5 third"),
    )
    for derived, frozen, name in k10_cases:
        ledger.require(derived == frozen, f"k10 cap {name}", kind="bookkeeping")

    k11_cases = (
        (121, 121, "H10 no radial"),
        (100, 100, "H9 no radial"),
        (100 + 25, 125, "H9 second no third"),
        (81 + 25, 106, "H8 no third"),
        (81 + 25 + 4, 110, "H8 third"),
        (64 + 25 + 4, 93, "H<=7 all radial"),
    )
    for derived, frozen, name in k11_cases:
        ledger.require(derived == frozen, f"k11 cap {name}", kind="bookkeeping")

    # W_m is increasing because pi^2(1+rho) > M rho^2(1-rho)^2;
    # the exact uniform reduction is pi^2>9>132/16.
    ledger.require(PI.lo**2 > 9, "checkpoint-Weyl derivative: pi^2>9")
    ledger.require(Q(132, 16) < 9, "checkpoint-Weyl derivative: M/16<9")

    rho_c = constants["rho_c"]
    global_payments = ((7, 40), (8, 53), (9, 73), (10, 89), (11, 121))
    for m, cap in global_payments:
        ledger.require(
            checkpoint_weyl(rho_c, m).lo > cap,
            f"global k{m} checkpoint payment > {cap}",
        )

    conditional_first_mode_payment(ledger, 7, Q(10), 53, "k7 H6")
    conditional_first_mode_payment(ledger, 8, Q(23, 2), 80, "k8 H7")
    conditional_first_mode_payment(ledger, 9, Q(71, 6), 81, "k9 H8")
    conditional_first_mode_payment(ledger, 10, Q(23, 2), 100, "k10 H7")
    conditional_first_mode_payment(ledger, 10, Q(71, 6), 97, "k10 H8")
    conditional_first_mode_payment(ledger, 10, Q(64, 5), 100, "k10 H9")
    conditional_first_mode_payment(ledger, 11, Q(64, 5), 125, "k11 H9")


LOCALIZATION_RATIOS = (
    Q(1, 5), Q(3, 10), Q(1, 3), Q(3, 8), Q(2, 5), Q(5, 12), Q(3, 7),
    Q(1, 2), Q(107, 200), Q(8, 15), Q(3, 5), Q(16, 25), Q(13, 20), Q(2, 3),
    Q(4, 25), Q(1, 4), Q(7, 20),
)


@dataclass(frozen=True)
class LocalizationExpectation:
    rho: Q
    checkpoint: int
    radial: int
    ell: int
    expected_sign: int
    purpose: str


LOCALIZATION_EXPECTATIONS = (
    LocalizationExpectation(Q(1, 5), 11, 3, 1, 1, "k11 third-mode low-side cell"),
    LocalizationExpectation(Q(3, 10), 8, 2, 3, -1, "k8 h=3 exclusion side"),
    LocalizationExpectation(Q(1, 3), 8, 2, 2, -1, "k8 h=2 exclusion side"),
    LocalizationExpectation(Q(3, 8), 9, 2, 3, 1, "k9 h=3 possible side"),
    LocalizationExpectation(Q(2, 5), 9, 2, 2, 1, "k9 h=2 possible side"),
    LocalizationExpectation(Q(5, 12), 9, 2, 1, 1, "k9 h=1 possible side"),
    LocalizationExpectation(Q(3, 7), 9, 2, 0, -1, "k9 second-mode exclusion side"),
    LocalizationExpectation(Q(1, 2), 10, 2, 0, -1, "k10 second-mode exclusion side"),
    LocalizationExpectation(Q(107, 200), 11, 2, 0, -1, "k11 second-mode exclusion side"),
    LocalizationExpectation(Q(8, 15), 11, 2, 0, -1, "k11 stated second-mode localization"),
    LocalizationExpectation(Q(3, 5), 8, 2, 0, -1, "k8 all-second exclusion/payment side"),
    LocalizationExpectation(Q(16, 25), 9, 2, 0, -1, "k9 all-second exclusion/payment side"),
    LocalizationExpectation(Q(13, 20), 10, 2, 0, -1, "k10 all-second exclusion/payment side"),
    LocalizationExpectation(Q(2, 3), 11, 2, 0, -1, "k11 all-second exclusion/payment side"),
    LocalizationExpectation(Q(4, 25), 10, 3, 0, -1, "k10 third-mode exclusion side"),
    LocalizationExpectation(Q(1, 4), 11, 3, 0, -1, "k11 stated third-mode localization"),
    LocalizationExpectation(Q(7, 20), 9, 2, 4, -1, "k9 H=6,h=4 cap74 payment side"),
)


def channel_delta(
    checkpoint: int,
    radial: int,
    ell: int,
    x: Interval,
) -> Interval:
    """Exact channel difference M-ell(ell+1)-(n^2-1) z^2."""

    return (
        Interval.point(checkpoint * (checkpoint + 1) - ell * (ell + 1))
        - (radial * radial - 1) * x
    )


def verify_localization_expectation(
    ledger: Ledger,
    item: LocalizationExpectation,
    *,
    x_override: Interval | None = None,
) -> Interval:
    """Verify one named side, with injectable x for semantic mutation tests."""

    x = x_at_ratio(item.rho) if x_override is None else x_override
    delta = channel_delta(item.checkpoint, item.radial, item.ell, x)
    condition = delta.lo > 0 if item.expected_sign > 0 else delta.hi < 0
    side = "possible" if item.expected_sign > 0 else "excluded"
    ledger.require(
        condition,
        f"rho={item.rho} expected {side} side for {item.purpose}",
    )
    return delta


def verify_localizations(ledger: Ledger, constants: Mapping[str, Interval]) -> None:
    ratios = sorted(set(LOCALIZATION_RATIOS))
    ledger.require(
        len(ratios) == len(LOCALIZATION_RATIOS),
        "localization ratios are distinct",
        kind="bookkeeping",
    )
    ledger.require(
        {item.rho for item in LOCALIZATION_EXPECTATIONS} == set(LOCALIZATION_RATIOS),
        "every named ratio has a connected expected-side assertion",
        kind="bookkeeping",
    )
    for rho in ratios:
        ledger.require(constants["rho_c"].hi < rho < Q(7, 8), f"ratio localization {rho} in high strip")

    for item in LOCALIZATION_EXPECTATIONS:
        verify_localization_expectation(ledger, item)

    x_min = (PI + Q(1, 2)) ** 2
    x_max = 64 * PI**2
    for x in (Q(16), Q(68, 3), Q(34)):
        ledger.require(x_min.hi < x < x_max.lo, f"algebraic split z^2={x} in high strip")
    ledger.require(
        132 - 1 * 2 - 8 * Q(16) == 2 > 0,
        "z^2=16 is on the possible side of k11 n3 ell1",
    )
    ledger.require(
        110 - 6 * 7 - 3 * Q(68, 3) == 0
        and strict_positive_integer_count(Q(1)) == 0,
        "z^2=68/3 defines and strictly excludes k10 n2 ell6 equality",
    )
    ledger.require(
        132 - 5 * 6 - 3 * Q(34) == 0
        and strict_positive_integer_count(Q(1)) == 0,
        "z^2=34 defines and strictly excludes k11 n2 ell5 equality",
    )

    # Explicit k11 localizations.
    ledger.require(x_at_ratio(Q(8, 15)).lo > 44, "k11 second mode forces rho<8/15")
    ledger.require(x_at_ratio(Q(1, 4)).lo > Q(33, 2), "k11 third mode forces rho<1/4")
    h10_lower = Q(69, 5) ** 2 - 132
    h9_lower = Q(64, 5) ** 2 - 132
    ledger.require(h10_lower > 44, "k11 H10 excludes every second mode")
    ledger.require(h10_lower > Q(33, 2), "k11 H10 excludes every third mode")
    ledger.require(h9_lower > Q(33, 2), "k11 H9 excludes every third mode")


def verify_u_and_k11(ledger: Ledger, constants: Mapping[str, Interval]) -> None:
    # K0 is the positive root of eta*K-sqrt(a*K)-C0=0, so K0>C0/eta.
    # On [rho_c,1/2], eta=omega and k11 is increasing.  On [1/2,1),
    # d(eta*k11)/d rho<0 follows from arccos rho>=sqrt(2(1-rho)) and
    # sqrt(1+rho)<sqrt(2).  The only finite endpoint check is therefore rho=1/2.
    k11_half = sqrt_interval(4 * PI**2 + 132)
    central_endpoint_pass = (constants["omega"] * k11_half).hi < constants["C0"].lo
    ledger.require(
        central_endpoint_pass,
        "eta*k11<C0 at rho=1/2",
    )
    ledger.require(1 + Q(1, 2) < 2, "K0 monotonic reduction sqrt(1+rho)<sqrt2")
    ledger.require(
        constants["C0"].lo > 0 and constants["omega"].lo > 0,
        "K0 positive-root identity gives K0>C0/eta",
    )

    # For rho>=5/6, also beat the seam 54/(1-rho)^2.  Squaring and taking
    # s=1-rho<=1/6 leaves pi^2 s^2+132 s^4<2916.
    seam_lhs = PI**2 / 36 + Q(132, 6**4)
    seam_pass = seam_lhs.hi < 54**2
    ledger.require(seam_pass, "k11 below seam-54 branch")
    ledger.require(constants["rho_c"].hi < Q(39, 50) < Q(5, 6), "K0-only interval avoids seam")
    ledger.require(constants["omega"].hi < constants["rho_c"].lo, "K0-only interval avoids H0")
    ledger.require(
        constants["omega"].hi < constants["rho_c"].lo
        and Q(39, 50) < Q(5, 6),
        "U=K0 on rho_c<=rho<39/50",
    )
    ledger.require(central_endpoint_pass and seam_pass, "k11<U on rho_c<=rho<7/8")


def verify_product_deficit(ledger: Ledger) -> None:
    c_d = Q(1382, 3125)
    a_coeff = Q(1, 2) - c_d
    ledger.require(a_coeff > 0, "product deficit positive N^2 coefficient")

    # B(t)=t^2-2Ct+1/6 has minimum 1/6-C^2.  This and
    # A(2N+1) show F(N+1,t)-F(N,t)>0 for N>=1.
    b_min = Q(1, 6) - c_d * c_d
    ledger.require(3 * a_coeff + b_min > 0, "product deficit increases in N")

    # At N=1, F'(t)=2(t-C)(t+1), so the minimum on 0<t<=1 is t=C.
    minimum = (
        Q(2, 3) * c_d**3
        + (1 - c_d) * c_d**2
        - 2 * c_d**2
        + Q(2, 3)
        - c_d
    )
    ledger.require(minimum == Q(1822532, 91552734375), "exact product-deficit minimum")
    ledger.require(minimum > 0, "D(a)>1382/3125 a^2 for all N,t")
    ledger.require(0 < c_d < 1, "product critical point lies in 0<t<=1")

    # P4 itself follows from exact sums of n^2.  Check a finite symbolic grid
    # of indeterminates represented by rational N,t; this verifies the algebraic
    # identity, while the formula below is used for all N.
    for n in range(1, 7):
        for t in (Q(1, 7), Q(1, 2), Q(1)):
            sum_n2 = Q(n * (n + 1) * (2 * n + 1), 6)
            x = n + t
            direct = Q(2, 3) * x**3 - n * x**2 + sum_n2
            expanded = Q(n * n, 2) + n * (t * t + Q(1, 6)) + Q(2, 3) * t**3
            ledger.require(direct == expanded, f"product deficit expansion N={n},t={t}")


def verify_optical_constants(ledger: Ledger) -> None:
    eps0 = Q(11, 50)
    c = Q(1126, 625)
    q = Q(106, 333)
    c_d = Q(1382, 3125)
    r_l = Q(39569, 2772225000)
    r_h = Q(14817541, 472867032960000)

    low_cost = Q(2, 3) * c * q + eps0 / 4 + eps0**2 * q**2
    ledger.require(c_d - low_cost == r_l, "exact low optical endpoint reserve")
    ledger.require(r_l > 0, "low optical reserve positive")
    ledger.require(
        all(coefficient > 0 for coefficient in (Q(1, 4), q**2)),
        "low optical cost increases in epsilon (positive coefficients)",
    )

    high_radial = (1 - eps0) ** 2 / 4 - Q(22, 7) * (1 - eps0) * eps0 / (4 * c)
    high_angular = (
        q * eps0
        + eps0**2 / (4 * c)
        + q * eps0**3 / (4 * c)
        + eps0**4 / (16 * c**2)
    )
    ledger.require(high_radial - high_angular == r_h, "exact high optical endpoint reserve")
    ledger.require(r_h > 0, "high optical reserve positive")

    # L'(eps)<0 because eps<=11/50<1/2; E'(eps)>0 coefficientwise.
    ledger.require(eps0 < Q(1, 2), "high radial screen decreases on epsilon interval")
    ledger.require(
        all(
            coefficient > 0
            for coefficient in (q, Q(1, 4) / c, q / (4 * c), Q(1, 16) / c**2)
        ),
        "high angular screen increases in epsilon (positive coefficients)",
    )

    # Actual scaling implications at a<=c/eps (low) and a>=c/eps (high).
    low_cubic_actual = Q(2, 3) * c / PI
    ledger.require(
        low_cubic_actual.hi < Q(2, 3) * c * q,
        "low optical a<=c/epsilon turns cubic cost into 2cq/3",
    )
    ledger.require(
        ((1 / PI) ** 2).hi < q**2,
        "low optical a>=pi turns epsilon^2/(pi*a) into epsilon^2 q^2",
    )

    common_face = c / eps0
    angular_at_common_face = (
        eps0 / PI
        + eps0**2 / (4 * PI * common_face)
        + eps0 / (4 * common_face)
        + eps0**2 / (16 * common_face**2)
    )
    ledger.require(
        angular_at_common_face.hi < high_angular,
        "full high angular ceiling-error screen at a=c/epsilon",
    )
    ledger.require(
        all(
            coefficient > 0
            for coefficient in (
                eps0**2 / (4 * PI.lo),
                eps0 / 4,
                eps0**2 / 16,
            )
        ),
        "high angular error decreases for a>=c/epsilon",
    )

    radial_at_common_face = (
        (1 - eps0) ** 2 / 4
        - PI * (1 - eps0) * eps0 / (4 * c)
    )
    ledger.require(
        radial_at_common_face.lo > high_radial,
        "full high radial-deficit screen at a=c/epsilon",
    )
    ledger.require(
        (1 - eps0) * eps0 > 0,
        "high radial deficit increases for a>=c/epsilon",
    )

    low_face_slack = c - eps0 * common_face
    high_face_slack = eps0 * common_face - c
    ledger.require(
        low_face_slack == 0 and high_face_slack == 0 and eps0 > 0 and c > 0,
        "a=c/epsilon belongs to both optical pieces",
    )

    # Exact count/error identities at walls.
    for j in range(0, 12):
        ledger.require(sum(2 * ell + 1 for ell in range(j)) == j * j, f"angular ceiling block j={j}")
    ledger.require(
        strict_positive_integer_count(Q(1)) == 0,
        "a=pi radial wall uses (N,t)=(m-1,1) and is excluded",
    )
    verify_product_deficit(ledger)


def verify_exact_subtraction(ledger: Ledger) -> None:
    rho_states = (
        "rho_star", "low1", "rho0", "low2", "rho_c", "pre_opt", "opt_face",
        "post_opt", "rho_7_8",
    )
    k_states = ("below_k6", "k6", "stair", "k11", "post_k11", "U", "above_U")

    def low_d19(rho: str) -> bool:
        return rho in {"low1", "rho0", "low2"}

    def high_ratio(rho: str) -> bool:
        return rho in {"rho_c", "pre_opt", "opt_face", "post_opt"}

    def d19(rho: str, k: str) -> bool:
        if low_d19(rho):
            return k not in {"U", "above_U"}
        return high_ratio(rho) and k in {"stair", "k11", "post_k11"}

    def lower_cover(rho: str, k: str) -> bool:
        return low_d19(rho) and k not in {"U", "above_U"}

    def stair(rho: str, k: str) -> bool:
        return high_ratio(rho) and k in {"stair", "k11"}

    def optical(rho: str, k: str) -> bool:
        return rho in {"opt_face", "post_opt"} and k == "post_k11"

    def d20(rho: str, k: str) -> bool:
        return rho in {"rho_c", "pre_opt"} and k == "post_k11"

    for rho in rho_states:
        for k in k_states:
            remainder = d19(rho, k) and not (lower_cover(rho, k) or stair(rho, k) or optical(rho, k))
            ledger.require(remainder == d20(rho, k), f"D19 subtraction face rho={rho},K={k}")

    ledger.require(
        d19("rho0", "post_k11") and lower_cover("rho0", "post_k11"),
        "rho0 fiber belongs to lower cover and is removed once",
    )
    ledger.require(
        d20("rho_c", "post_k11") and not optical("rho_c", "post_k11"),
        "rho_c belongs to D20 ratio face after closed stair removal",
    )
    ledger.require(
        optical("opt_face", "post_k11") and not d20("opt_face", "post_k11"),
        "rho=39/50 optical face is removed inclusively",
    )
    ledger.require(
        stair("rho_c", "k11") and not d19("rho_c", "U"),
        "K=k11 is stair-owned; K=U is inherited-owner excluded",
    )
    ledger.require(
        d19("pre_opt", "post_k11")
        and not lower_cover("pre_opt", "post_k11")
        and not stair("pre_opt", "post_k11")
        and not optical("pre_opt", "post_k11")
        and d20("pre_opt", "post_k11"),
        "pre-optical post-k11 cell survives exactly as D20",
    )


def verify_seam_ledger(ledger: Ledger) -> dict[str, Q]:
    """Exact seam derivative, initial reserve, and terminal payments."""

    pi_upper = Q(1571, 500)
    sqrt2_lower = Q(140, 99)
    sqrt2_upper = Q(99, 70)
    ledger.require(PI.hi < pi_upper, "seam Machin enclosure pi<1571/500")
    ledger.require(sqrt2_lower**2 < 2, "seam 140/99<sqrt(2)")
    ledger.require(sqrt2_upper**2 > 2, "seam sqrt(2)<99/70")

    epsilon = Q(1, 6)
    rho = Q(5, 6)
    kappa = Q(54)
    shelf = Q(13, 5)
    displacement_cap = Q(159, 400)
    loss = Q(14, 3)
    y_upper = Q(49, 120)
    ledger.require(y_upper**2 - epsilon == Q(1, 14400) > 0,
                   "seam y<49/120 by positive squaring")
    ledger.require(shelf**2 - 2 * pi_upper == Q(119, 250) > 0,
                   "seam shelf sqrt(2*pi*rho)<13/5")

    displacement_first = epsilon**2 / (kappa * rho)
    radical_upper = Q(763, 5000)
    radical_square = pi_upper / 135
    ledger.require(displacement_first == Q(1, 1620),
                   "seam first displacement term")
    ledger.require(radical_upper**2 - radical_square
                   == Q(8563, 675000000) > 0,
                   "seam radical enclosure 763/5000")
    displacement = displacement_first + shelf * radical_upper
    ledger.require(displacement == Q(804689, 2025000),
                   "seam displacement proxy exact value")
    ledger.require(displacement_cap - displacement == Q(497, 4050000) > 0,
                   "seam displacement below 159/400")
    ledger.require(rho * (1 - displacement_cap) == Q(241, 480) > Q(1, 2),
                   "seam localization x0/K>241/480>1/2")

    a_upper = epsilon / rho
    dqdp = shelf * y_upper / kappa
    derivative_cap = (
        2 * pi_upper**2 * dqdp
        * (1 + displacement_cap + 2 * a_upper)
        / (1 - displacement_cap) ** 3
    )
    derivative_target = Q(2260740364246, 708624500625)
    derivative_margin = Q(16, 5) - derivative_cap
    ledger.require(dqdp == Q(637, 32400), "seam exact dq/dP cap")
    ledger.require(derivative_cap == derivative_target,
                   "seam exact partial_P H upper proxy")
    ledger.require(derivative_margin
                   == Q(6858037754, 708624500625) > 0,
                   "seam partial_P H<16/5")
    ledger.require(2 * loss - Q(16, 5) == Q(92, 15) > 0,
                   "seam synthetic slope reserve 92/15")

    endpoint_q = Q(10093, 9720)
    endpoint_qhat = Q(373, 48600)
    ledger.require(endpoint_q - 1 == Q(373, 9720),
                   "seam endpoint Q-1")
    ledger.require(a_upper * (endpoint_q - 1) == endpoint_qhat,
                   "seam endpoint qhat")
    initial_reserve = (
        loss**2
        - 2 * pi_upper**2 * endpoint_q / (1 - endpoint_qhat) ** 2
    )
    ledger.require(initial_reserve
                   == Q(2505132463469, 2616573970125) > 0,
                   "seam initial B^2-H(B,B) reserve")

    gain = 2 * sqrt2_lower * kappa / (3 * pi_upper)
    gain_minus_loss = gain - loss
    inverse_y = Q(120, 49)
    interface = Q(8, 15) * sqrt2_upper
    dangerous = (gain_minus_loss * inverse_y - 1) - interface
    safe = (gain * inverse_y - 1) - interface
    ledger.require(gain == Q(280000, 17281), "seam action gain coefficient")
    ledger.require(gain_minus_loss == Q(598066, 51843),
                   "seam dangerous-branch gain after R loss")
    ledger.require(interface == Q(132, 175), "seam interface remainder cap")
    ledger.require(dangerous == Q(80132733, 3024175) > 0,
                   "seam dangerous-branch terminal reserve")
    ledger.require(safe == Q(114694733, 3024175) > 0,
                   "seam safe-branch terminal reserve")
    return {
        "derivative_cap": derivative_cap,
        "derivative_margin": derivative_margin,
        "initial_reserve": initial_reserve,
        "dangerous_reserve": dangerous,
        "safe_reserve": safe,
    }


def verify_k6_and_lower_d_ledgers(ledger: Ledger) -> dict[str, Q]:
    """Map every printed k6 and lower-d reserve to its wall and cap."""

    pi_lower = Q(333, 106)
    pi_upper = Q(22, 7)
    ledger.require(PI.lo > pi_lower, "payment ledger pi>333/106")
    ledger.require(PI.hi < pi_upper, "payment ledger pi<22/7")

    moving_cases = (
        ("k1", Q(1, 8), 1, 2, 4,
         Q(153864824754340538785, 348796101192617852928)),
        ("k2", Q(3, 10), 1, 6, 9,
         Q(1399810848073457853053, 394237491401523000000)),
        ("k3", Q(1, 2), 1, 12, 16,
         Q(137027505353736631, 514922437748928)),
        ("k4", Q(1, 2), 1, 20, 25,
         Q(2507119282010251109, 13902905819221056)),
        ("k5", Q(13, 25), 1, 30, 36,
         Q(92672404686738742434741, 709259556128000000000)),
        ("p1", Q(1, 5), 4, 2, 29,
         Q(373255772037478993002833, 868931613701316000000)),
    )
    for name, rho, a, b, cap, expected in moving_cases:
        A = a * pi_lower**2 / (1 - rho) ** 2 + b
        B = Q(7, 99) * (1 - rho**3)
        delta = B**2 * A**3 - cap**2
        ledger.require(delta == expected > 0,
                       f"k6 moving wall {name} at rho={rho} pays cap {cap}")

    fixed_cases = (
        ("k2", Q(3, 10), Q(51, 10), 9, Q(1387329, 11000000)),
        ("k3", Q(1, 2), Q(13, 2), 16, Q(6277, 6336)),
        ("k4", Q(1, 2), Q(15, 2), 25, Q(775, 704)),
        ("k5", Q(13, 25), Q(17, 2), 36, Q(452843, 343750)),
        ("p1", Q(1, 5), Q(77, 10), 29, Q(849901, 281250)),
    )
    for name, rho, wall, cap, expected in fixed_cases:
        payment = Q(2, 9) * Q(7, 22) * (1 - rho**3) * wall**3
        ledger.require(payment - cap == expected > 0,
                       f"k6 fixed wall {name} at rho={rho} pays cap {cap}")

    lower_caps = (
        ("L<K<=4", 1, 1),
        ("4<K<=51/10", 1 + 3, 4),
        ("51/10<K<=13/2,K<=2z", 1 + 3 + 5, 9),
        ("51/10<K<=13/2,K>2z", 1 + 3 + 5 + 1, 10),
        ("13/2<K<=15/2,K<=2z", 1 + 3 + 5 + 7, 16),
        ("13/2<K<=15/2,K>2z", 1 + 3 + 5 + 7 + 1, 17),
        ("15/2<K<=77/10", 1 + 3 + 5 + 7 + 9 + 1, 26),
        ("77/10<K<=17/2", 1 + 3 + 5 + 7 + 9 + 1 + 3, 29),
        ("17/2<K<=9", 1 + 3 + 5 + 7 + 9 + 11 + 1 + 3, 40),
        ("9<K<=d", 1 + 3 + 5 + 7 + 9 + 11 + 1 + 3 + 5, 45),
    )
    for cell, derived, printed in lower_caps:
        ledger.require(derived == printed, f"lower-d cap cell {cell}",
                       kind="bookkeeping")

    ledger.require(4 * pi_lower > 13 * Q(18, 19),
                   "lower-d 2z>13/2 at rho0 using sqrt337<19")
    ledger.require(2 * pi_upper + 1 < Q(15, 2),
                   "lower-d 2z<15/2 at rho_c")
    ledger.require(2 * pi_lower * Q(19, 18) > Q(13, 2),
                   "lower-d cap-10 row is empty because 2z>13/2")

    return {"last_moving_delta": moving_cases[-1][-1]}


def verify_lower_d_payments(ledger: Ledger) -> dict[str, Q]:
    """Exact fixed and moving payments for the lower-d cap table."""

    coefficient = Q(7, 99) * (1 - Q(7, 50) ** 3)
    fixed = (
        (Q(4), 4, Q(793292, 1546875)),
        (Q(51, 10), 9, Q(486236661, 1375000000)),
        (Q(13, 2), 16, Q(333100003, 99000000)),
        (Q(15, 2), 26, Q(329797, 88000)),
        (Q(77, 10), 29, Q(3590476297, 1125000000)),
        (Q(17, 2), 40, Q(327078887, 99000000)),
        (Q(9), 45, Q(8805519, 1375000)),
    )
    for wall, cap, expected in fixed:
        reserve = coefficient * wall**3 - cap
        ledger.require(reserve == expected > 0,
                       f"lower-d fixed wall K={wall} pays cap {cap}")

    pi_lower = Q(333, 106)
    initial = (3 + 6 * pi_lower + 4 * pi_lower**2) / 18
    ledger.require(initial - Q(19, 6) == Q(675, 2809) > 0,
                   "lower-d initial moving L payment exceeds 19/6")
    rho = Q(1, 19)
    moving_2z = Q(16, 9) * pi_lower**2 * (1 - rho**3) / (1 - rho) ** 3
    ledger.require(moving_2z - Q(508, 27) == Q(137795, 75843) > 0,
                   "lower-d moving 2z payment exceeds 508/27")
    return {"initial": initial, "moving_2z": moving_2z}


def run_core_ledger() -> Ledger:
    """Regenerate the 488 substantive plus 65 bookkeeping check registry."""

    ledger = Ledger()
    verify_pi(ledger)
    constants = verify_thresholds(ledger)
    verify_strict_face_conventions(ledger)
    verify_zero_specializations(ledger)
    verify_lower_inventories_and_payments(ledger, constants)
    verify_checkpoint_inventories(ledger, constants)
    verify_cap_tables_and_payments(ledger, constants)
    verify_localizations(ledger, constants)
    verify_u_and_k11(ledger, constants)
    verify_optical_constants(ledger)
    verify_exact_subtraction(ledger)
    return ledger


def registry_digest(*registries: tuple[str, Ledger]) -> tuple[int, str]:
    rows = tuple(
        row
        for namespace, ledger in registries
        for row in ledger.canonical_rows(namespace)
    )
    payload = ("\n".join(rows) + "\n").encode("ascii")
    return len(rows), hashlib.sha256(payload).hexdigest()


def main() -> int:
    try:
        core = run_core_ledger()
        supplement = Ledger()
        seam = verify_seam_ledger(supplement)
        verify_k6_and_lower_d_ledgers(supplement)
        lower = verify_lower_d_payments(supplement)
        supplement.require(Q(2409, 100) - Q(70, 3)
                           == Q(227, 300) > 0,
                           "cap74 ball wall and product wall are incompatible")
        rows, digest = registry_digest(("core", core), ("supplement", supplement))
    except (VerificationError, ValueError, ZeroDivisionError) as exc:
        print("FAIL")
        print(f"first issue: {exc}")
        return 1

    counts = core.counts()
    print("PASS")
    print("first issue: none")
    print(f"core exact finite checks: {len(core.labels)}")
    print(f"core substantive checks: {counts['substantive']}")
    print(f"core bookkeeping identities: {counts['bookkeeping']}")
    print(f"supplemental exact checks: {len(supplement.labels)}")
    print(f"combined registry rows: {rows}")
    print(f"canonical registry sha256: {digest}")
    print(f"seam partial_P H cap: {seam['derivative_cap']}")
    print(f"seam partial_P H margin to 16/5: {seam['derivative_margin']}")
    print(f"seam initial reserve: {seam['initial_reserve']}")
    print(f"lower-d moving 2z lower bound: {lower['moving_2z']}")
    print("cap-74 incompatibility gap: 227/300")
    return 0


if __name__ == "__main__":
    raise SystemExit(main())
\end{lstlisting}

\section{Executable interval certificates}
\label{sec:embedded-certifiers}

The following two programs are complete: they read no input files and require
only Python~3 and \texttt{python-flint}.  Save each listing under the filename
printed immediately above it and run
\begin{lstlisting}[language={},basicstyle=\ttfamily\small,frame=single]
python standalone_round21_compact_proxy.py --precision-bits 256
python standalone_round21_compact_proxy.py --precision-bits 384
python standalone_round21_aggregate_tail.py --precision 192
python standalone_round21_aggregate_tail.py --precision 384
\end{lstlisting}
A successful run prints \texttt{PASS}.  Any failed partition, precision, or
outward-interval proof predicate gives a nonzero exit status.

The recorded environment was Python~3.14.4 with
\texttt{python-flint}~0.8.0 and FLINT~3.3.1.  These versions identify the
replay; the proof predicates are the exact and outward-interval comparisons
printed below.

\subsection{Compact-proxy rectangle certifier}

\noindent\texttt{standalone\_round21\_compact\_proxy.py}
\begin{lstlisting}[
  language=Python,
  basicstyle=\ttfamily\scriptsize,
  breaklines=true,
  breakatwhitespace=false,
  columns=fullflexible,
  keepspaces=true,
  showstringspaces=false,
  frame=single,
  numbers=left,
  numberstyle=\tiny,
  stepnumber=5,
  numbersep=6pt
]
#!/usr/bin/env python3
"""Standalone finite Arb certificate for the compact shell rectangle.

The program certifies that the coarse integer proxy is strictly below the
three-dimensional Weyl term on

    7/51 <= rho <= 39/50,    12 <= K <= 200.

It reads no files.  All geometry and branch decisions are exact ``Fraction``
operations.  Arb supplies outward transcendental enclosures.  Floating-point
numbers choose only between two legal subdivision directions and provide
display diagnostics; they never decide whether a box passes.

Dependency: python-flint.  Run with

    python standalone_round21_compact_proxy.py
"""

from __future__ import annotations

import argparse
import hashlib
import sys
from dataclasses import dataclass, replace
from fractions import Fraction
from typing import Iterable, Sequence

try:
    from flint import arb, ctx, fmpq
except ImportError as exc:  # pragma: no cover - exercised only on a bad host
    raise SystemExit("python-flint is required for this certificate") from exc


SCHEMA = "standalone-round21-compact-proxy-v1-half-open-faces"
MIN_PRECISION_BITS = 192
DEFAULT_PRECISION_BITS = 256
DEFAULT_MAX_DEPTH = 30
DEFAULT_MAX_BOXES = 100_000


class CertificateError(RuntimeError):
    """The first rigorous certificate condition that failed."""


@dataclass(frozen=True, order=True)
class Box:
    rho_lo: Fraction
    rho_hi: Fraction
    k_lo: Fraction
    k_hi: Fraction

    def area(self) -> Fraction:
        return (self.rho_hi - self.rho_lo) * (self.k_hi - self.k_lo)


ROOT_BOX = Box(Fraction(7, 51), Fraction(39, 50), Fraction(12), Fraction(200))


@dataclass(frozen=True)
class FloorUpper:
    count: int
    ceiling: int
    wall_straddle: bool


@dataclass(frozen=True)
class ProxyUpper:
    value: int
    comparisons: int
    wall_straddles: int


@dataclass(frozen=True)
class BoxEvaluation:
    proxy_upper: int
    comparison: arb
    passed: bool

    def subdivision_score(self) -> float:
        """A non-proof heuristic; PASS never depends on this float."""

        return float(self.comparison.mid())


@dataclass(frozen=True)
class Leaf:
    box: Box
    depth: int
    proxy_upper: int


@dataclass(frozen=True)
class Certificate:
    leaves: tuple[Leaf, ...]
    max_depth: int
    precision_bits: int
    min_gap_display: float
    digest: str
    generated_proxy_corners: int
    generated_floor_comparisons: int
    generated_wall_straddles: int


def fraction_text(value: Fraction) -> str:
    if value.denominator == 1:
        return str(value.numerator)
    return f"{value.numerator}/{value.denominator}"


def fraction_to_arb(value: Fraction) -> arb:
    return arb(fmpq(value.numerator, value.denominator))


def active_channel_count(k: Fraction) -> int:
    """Number of half-integers nu=ell+1/2 satisfying the strict cutoff nu<K."""

    shifted = k - Fraction(1, 2)
    if shifted <= 0:
        return 0
    return (shifted.numerator + shifted.denominator - 1) // shifted.denominator


def g_arb(a: Fraction, nu: Fraction) -> arb:
    r"""Outward Arb enclosure of

        G_a(nu) = (sqrt(a^2-nu^2)-nu*acos(nu/a))/pi    if 0 <= nu < a,
                  0                                    if nu >= a.

    Exact rational comparisons own both interfaces.  In particular, ``nu=a``
    returns exact zero and never asks Arb to resolve ``sqrt(0)`` or ``acos(1)``.
    """

    if a <= 0 or nu < 0:
        raise ValueError("G requires a>0 and nu>=0")
    if nu >= a:
        return arb(0)
    aa = fraction_to_arb(a)
    vv = fraction_to_arb(nu)
    radicand = aa * aa - vv * vv
    if not (radicand > 0):
        raise CertificateError(f"Arb failed to prove positive G radicand at a={a}, nu={nu}")
    return (radicand.sqrt() - vv * (vv / aa).acos()) / arb.pi()


def proxy_argument_arb(rho: Fraction, k: Fraction, nu: Fraction) -> arb:
    """Outward enclosure of G_K(nu)-G_{rho*K}(nu)+1/4."""

    if not (0 < rho < 1 and k > 0 and nu >= 0):
        raise ValueError("proxy point is outside 0<rho<1, K>0, nu>=0")
    inner = rho * k
    return g_arb(k, nu) - g_arb(inner, nu) + fraction_to_arb(Fraction(1, 4))


def strict_count_upper_from_arb(value: arb) -> FloorUpper:
    r"""Certify an upper bound for the strict positive-integer count [value]_<.

    If Arb proves ``value <= M``, every positive integer strictly below value
    is at most ``M-1``.  At exact value 3 this returns 2.  If an inexact ball
    straddles an integer wall, the next integer is used, giving a safe one-unit
    overestimate instead of making an uncertified floor decision.
    """

    if not value.is_finite():
        raise CertificateError("non-finite Arb proxy argument")
    if not (value > 0):
        raise CertificateError(f"Arb failed to prove positive proxy argument: {value}")
    ceiling_ball = value.upper().ceil()
    ceiling_fmpz = ceiling_ball.unique_fmpz()
    if ceiling_fmpz is None:
        raise CertificateError(f"could not extract an exact integer ceiling from {value}")
    ceiling = int(ceiling_fmpz)
    if not (value <= arb(ceiling)):
        raise CertificateError(f"Arb did not certify proxy argument <= {ceiling}: {value}")
    count = max(0, ceiling - 1)
    wall_straddle = count > 0 and value.contains(count) and not value.is_exact()
    return FloorUpper(count=count, ceiling=ceiling, wall_straddle=wall_straddle)


def coarse_proxy_upper(rho: Fraction, k: Fraction) -> ProxyUpper:
    r"""Certify the weighted coarse proxy from per-channel Arb enclosures."""

    total = 0
    comparisons = 0
    wall_straddles = 0
    for ell in range(active_channel_count(k)):
        nu = Fraction(2 * ell + 1, 2)
        if not (nu < k):
            raise CertificateError("strict active-channel enumeration included nu=K")
        bound = strict_count_upper_from_arb(proxy_argument_arb(rho, k, nu))
        total += (2 * ell + 1) * bound.count
        comparisons += 1
        wall_straddles += int(bound.wall_straddle)
    return ProxyUpper(total, comparisons, wall_straddles)


def weyl_arb(rho: Fraction, k: Fraction) -> arb:
    r"""Outward Arb enclosure of 2(1-rho^3)K^3/(9*pi)."""

    rr = fraction_to_arb(rho)
    kk = fraction_to_arb(k)
    return arb(2) * (arb(1) - rr**3) * kk**3 / (arb(9) * arb.pi())


class Certifier:
    """Cached 256-bit (or stronger) corner evaluator and adaptive prover."""

    def __init__(
        self,
        precision_bits: int = DEFAULT_PRECISION_BITS,
        max_depth: int = DEFAULT_MAX_DEPTH,
        max_boxes: int = DEFAULT_MAX_BOXES,
    ) -> None:
        if precision_bits < MIN_PRECISION_BITS:
            raise CertificateError(
                f"precision {precision_bits} is below the required {MIN_PRECISION_BITS} bits"
            )
        if max_depth < 1 or max_boxes < 1:
            raise ValueError("max_depth and max_boxes must be positive")
        self.precision_bits = precision_bits
        self.max_depth = max_depth
        self.max_boxes = max_boxes
        self._proxy_cache: dict[tuple[Fraction, Fraction], ProxyUpper] = {}
        self._weyl_cache: dict[tuple[Fraction, Fraction], arb] = {}

    def proxy_upper(self, rho: Fraction, k: Fraction) -> ProxyUpper:
        key = (rho, k)
        if key not in self._proxy_cache:
            with ctx.workprec(self.precision_bits):
                self._proxy_cache[key] = coarse_proxy_upper(rho, k)
        return self._proxy_cache[key]

    def weyl(self, rho: Fraction, k: Fraction) -> arb:
        key = (rho, k)
        if key not in self._weyl_cache:
            with ctx.workprec(self.precision_bits):
                self._weyl_cache[key] = weyl_arb(rho, k)
        return self._weyl_cache[key]

    def evaluate(self, box: Box) -> BoxEvaluation:
        """Use two monotone corners and accept only a certain Arb inequality."""

        proxy = self.proxy_upper(box.rho_lo, box.k_hi)
        with ctx.workprec(self.precision_bits):
            # lower() is outward; PASS means W_lower - integer is certainly > 0.
            w_lower = self.weyl(box.rho_hi, box.k_lo).lower()
            comparison = w_lower - proxy.value
            passed = bool(comparison > 0)
        return BoxEvaluation(proxy.value, comparison, passed)

    @staticmethod
    def _split_rho(box: Box) -> tuple[Box, Box]:
        mid = (box.rho_lo + box.rho_hi) / 2
        return (
            Box(box.rho_lo, mid, box.k_lo, box.k_hi),
            Box(mid, box.rho_hi, box.k_lo, box.k_hi),
        )

    @staticmethod
    def _split_k(box: Box) -> tuple[Box, Box]:
        mid = (box.k_lo + box.k_hi) / 2
        return (
            Box(box.rho_lo, box.rho_hi, box.k_lo, mid),
            Box(box.rho_lo, box.rho_hi, mid, box.k_hi),
        )

    @staticmethod
    def _split_score(evaluations: Sequence[BoxEvaluation]) -> tuple[int, float, float]:
        # Floats select only a subdivision direction.  Every eventual leaf is
        # independently accepted by the outward-Arb predicate above.
        displays = tuple(item.subdivision_score() for item in evaluations)
        return (sum(item.passed for item in evaluations), min(displays), sum(displays))

    def build(self, root: Box = ROOT_BOX) -> tuple[Leaf, ...]:
        if not (Fraction(0) < root.rho_lo < root.rho_hi < Fraction(1)):
            raise ValueError("root rho interval must lie strictly inside (0,1)")
        if not (Fraction(0) < root.k_lo < root.k_hi):
            raise ValueError("root K interval must be positive and nondegenerate")

        stack: list[tuple[Box, int]] = [(root, 0)]
        leaves: list[Leaf] = []
        while stack:
            box, depth = stack.pop()
            evaluation = self.evaluate(box)
            if evaluation.passed:
                leaves.append(Leaf(box, depth, evaluation.proxy_upper))
                continue
            if depth >= self.max_depth:
                raise CertificateError(
                    f"depth limit {self.max_depth} at failed box {box}; "
                    f"comparison={evaluation.comparison}"
                )
            if len(leaves) + len(stack) + 2 > self.max_boxes:
                raise CertificateError(
                    f"box-count limit {self.max_boxes} before splitting failed box {box}"
                )

            rho_children = self._split_rho(box)
            k_children = self._split_k(box)
            rho_evaluations = tuple(self.evaluate(child) for child in rho_children)
            k_evaluations = tuple(self.evaluate(child) for child in k_children)
            if self._split_score(rho_evaluations) > self._split_score(k_evaluations):
                chosen = rho_children
            else:
                chosen = k_children
            # Reverse push makes the lower child the deterministic next item.
            for child in reversed(chosen):
                stack.append((child, depth + 1))
        return tuple(leaves)

    @property
    def proxy_corner_count(self) -> int:
        return len(self._proxy_cache)

    @property
    def floor_comparison_count(self) -> int:
        return sum(item.comparisons for item in self._proxy_cache.values())

    @property
    def wall_straddle_count(self) -> int:
        return sum(item.wall_straddles for item in self._proxy_cache.values())


def coordinate_owned(value: Fraction, lo: Fraction, hi: Fraction, root_hi: Fraction) -> bool:
    """Lower-closed/upper-open ownership, closing only the root upper face."""

    return lo <= value and (value < hi or (value == root_hi and hi == root_hi))


def box_owns(root: Box, box: Box, rho: Fraction, k: Fraction) -> bool:
    """Unique shared-face ownership convention used by the finite partition."""

    return coordinate_owned(rho, box.rho_lo, box.rho_hi, root.rho_hi) and coordinate_owned(
        k, box.k_lo, box.k_hi, root.k_hi
    )


def _check_owned_vertical_face(root: Box, leaves: Sequence[Leaf], rho: Fraction) -> None:
    """Check exact, unique K-tiling by the leaves that own this rho face."""

    intervals = sorted(
        (leaf.box.k_lo, leaf.box.k_hi)
        for leaf in leaves
        if coordinate_owned(rho, leaf.box.rho_lo, leaf.box.rho_hi, root.rho_hi)
    )
    if not intervals:
        raise CertificateError(f"uncovered vertical face rho={rho}")
    cursor = root.k_lo
    for lo, hi in intervals:
        if lo < cursor:
            raise CertificateError(f"owned-face overlap at rho={rho}, K={lo}..{cursor}")
        if lo > cursor:
            raise CertificateError(f"gap on vertical face rho={rho} at K={cursor}..{lo}")
        cursor = hi
    if cursor != root.k_hi:
        raise CertificateError(f"vertical face rho={rho} ends at K={cursor}, not {root.k_hi}")


def validate_partition(root: Box, leaves: Sequence[Leaf]) -> None:
    """Exact full-coverage/disjoint-interior sweep for rational rectangles."""

    if not leaves:
        raise CertificateError("empty leaf list")
    for index, leaf in enumerate(leaves):
        box = leaf.box
        if not (
            root.rho_lo <= box.rho_lo < box.rho_hi <= root.rho_hi
            and root.k_lo <= box.k_lo < box.k_hi <= root.k_hi
        ):
            raise CertificateError(f"leaf {index} lies outside or degenerates in root: {box}")

    rho_faces = sorted(
        {root.rho_lo, root.rho_hi}
        | {leaf.box.rho_lo for leaf in leaves}
        | {leaf.box.rho_hi for leaf in leaves}
    )
    for rho_lo, rho_hi in zip(rho_faces, rho_faces[1:]):
        intervals = sorted(
            (leaf.box.k_lo, leaf.box.k_hi)
            for leaf in leaves
            if leaf.box.rho_lo <= rho_lo and rho_hi <= leaf.box.rho_hi
        )
        cursor = root.k_lo
        for k_lo, k_hi in intervals:
            if k_lo < cursor:
                raise CertificateError(
                    f"positive-area overlap in rho slab {rho_lo}..{rho_hi} at K={k_lo}"
                )
            if k_lo > cursor:
                raise CertificateError(
                    f"coverage gap in rho slab {rho_lo}..{rho_hi}: K={cursor}..{k_lo}"
                )
            cursor = k_hi
        if cursor != root.k_hi:
            raise CertificateError(
                f"rho slab {rho_lo}..{rho_hi} ends at K={cursor}, not {root.k_hi}"
            )

    if sum((leaf.box.area() for leaf in leaves), Fraction(0)) != root.area():
        raise CertificateError("exact sum of leaf areas differs from root area")

    # Closed-box estimates plus this ownership check give pointwise coverage,
    # including every shared face, not merely disjoint interiors.
    for rho in rho_faces:
        _check_owned_vertical_face(root, leaves, rho)


def canonical_certificate_bytes(
    root: Box,
    leaves: Iterable[Leaf],
    precision_bits: int,
) -> bytes:
    """Canonical ASCII serialization of all finite certificate proof data."""

    rows = [
        SCHEMA,
        f"precision_bits={precision_bits}",
        "root=" + ",".join(
            fraction_text(value)
            for value in (root.rho_lo, root.rho_hi, root.k_lo, root.k_hi)
        ),
    ]
    for leaf in sorted(leaves, key=lambda item: item.box):
        box = leaf.box
        rows.append(
            "leaf="
            + ",".join(
                fraction_text(value)
                for value in (box.rho_lo, box.rho_hi, box.k_lo, box.k_hi)
            )
            + f",depth={leaf.depth},P={leaf.proxy_upper}"
        )
    return ("\n".join(rows) + "\n").encode("ascii")


def certificate_digest(
    root: Box,
    leaves: Iterable[Leaf],
    precision_bits: int,
) -> str:
    return hashlib.sha256(
        canonical_certificate_bytes(root, leaves, precision_bits)
    ).hexdigest()


def validate_leaves(certifier: Certifier, leaves: Sequence[Leaf]) -> float:
    """Replay all proof predicates; return only a display approximation to min gap."""

    display_gaps: list[float] = []
    for index, leaf in enumerate(leaves):
        evaluation = certifier.evaluate(leaf.box)
        if evaluation.proxy_upper != leaf.proxy_upper:
            raise CertificateError(
                f"leaf {index} proxy tampering/mismatch: stored {leaf.proxy_upper}, "
                f"recomputed {evaluation.proxy_upper}"
            )
        if not evaluation.passed:
            raise CertificateError(
                f"leaf {index} fails certain Arb comparison: {evaluation.comparison}"
            )
        display_gaps.append(evaluation.subdivision_score())
    return min(display_gaps)


def build_certificate(
    precision_bits: int = DEFAULT_PRECISION_BITS,
    max_depth: int = DEFAULT_MAX_DEPTH,
    max_boxes: int = DEFAULT_MAX_BOXES,
) -> Certificate:
    certifier = Certifier(precision_bits, max_depth, max_boxes)
    leaves = certifier.build(ROOT_BOX)
    validate_partition(ROOT_BOX, leaves)
    min_gap_display = validate_leaves(certifier, leaves)
    digest = certificate_digest(ROOT_BOX, leaves, precision_bits)
    return Certificate(
        leaves=leaves,
        max_depth=max(leaf.depth for leaf in leaves),
        precision_bits=precision_bits,
        min_gap_display=min_gap_display,
        digest=digest,
        generated_proxy_corners=certifier.proxy_corner_count,
        generated_floor_comparisons=certifier.floor_comparison_count,
        generated_wall_straddles=certifier.wall_straddle_count,
    )


def tampered_leaf(leaf: Leaf) -> Leaf:
    """Return a one-count corruption for independent replay tests."""

    return replace(leaf, proxy_upper=leaf.proxy_upper + 1)


def _parser() -> argparse.ArgumentParser:
    parser = argparse.ArgumentParser(description=__doc__)
    parser.add_argument("--precision-bits", type=int, default=DEFAULT_PRECISION_BITS)
    parser.add_argument("--max-depth", type=int, default=DEFAULT_MAX_DEPTH)
    parser.add_argument("--max-boxes", type=int, default=DEFAULT_MAX_BOXES)
    return parser


def main(argv: Sequence[str] | None = None) -> int:
    args = _parser().parse_args(argv)
    try:
        certificate = build_certificate(
            precision_bits=args.precision_bits,
            max_depth=args.max_depth,
            max_boxes=args.max_boxes,
        )
    except Exception as exc:
        print("STANDALONE_COMPACT_PROXY FAIL")
        print(f"first_issue={type(exc).__name__}: {exc}")
        return 1

    print("STANDALONE_COMPACT_PROXY PASS")
    print(f"precision_bits={certificate.precision_bits}")
    print("root_rho=[7/51,39/50]")
    print("root_K=[12,200]")
    print(f"leaf_boxes={len(certificate.leaves)}")
    print(f"max_depth={certificate.max_depth}")
    print("coverage=PASS (exact rational slab/face sweep and exact area)")
    print("nonoverlap=PASS (exact half-open shared-face ownership)")
    print(f"generated_proxy_corners={certificate.generated_proxy_corners}")
    print(f"generated_floor_comparisons={certificate.generated_floor_comparisons}")
    print(f"generated_wall_straddles={certificate.generated_wall_straddles}")
    print(f"min_gap_lower_display={certificate.min_gap_display:.17g}")
    print(f"certificate_sha256={certificate.digest}")
    return 0


if __name__ == "__main__":
    sys.exit(main())
\end{lstlisting}

\subsection{Aggregate-tail certifier}

\noindent\texttt{standalone\_round21\_aggregate\_tail.py}
\begin{lstlisting}[
  language=Python,
  basicstyle=\ttfamily\scriptsize,
  breaklines=true,
  breakatwhitespace=false,
  columns=fullflexible,
  keepspaces=true,
  showstringspaces=false,
  frame=single,
  numbers=left,
  numberstyle=\tiny,
  stepnumber=5,
  numbersep=6pt
]
#!/usr/bin/env python3
"""Standalone outward-Arb certificate for aggregate-tail positivity.

The proof-sign decisions use only exact ``Fraction``/``fmpq`` data and
python-flint ``arb`` interval comparisons.  Decimal lower bounds in the
command-line output are display-only diagnostics.  The program reads no
files and has no dependency other than Python's standard library and
python-flint.

Run with

    python standalone_round21_aggregate_tail.py --precision 192
"""

from __future__ import annotations

import argparse
import hashlib
from dataclasses import dataclass
from fractions import Fraction
from typing import Dict, Iterable, Mapping, Sequence

try:
    from flint import arb, ctx, fmpq
except ImportError as exc:  # pragma: no cover - exercised only on a bad host
    raise SystemExit("python-flint is required for this certificate") from exc


SCHEMA = "standalone-round21-aggregate-tail-v1"
MIN_PRECISION_BITS = 192
K0 = 200
LOWER_RHO = Fraction(7, 51)
SPLIT_RHO = Fraction(1, 2)
UPPER_RHO = Fraction(39, 50)
MAX_BOX_WIDTH = Fraction(1, 2000)
EXPECTED_BOX_COUNT = 1286


class VerificationError(RuntimeError):
    """Raised when an exact-partition or interval proof obligation fails."""


@dataclass(frozen=True)
class RationalBox:
    lo: Fraction
    hi: Fraction
    eta_regime: str

    @property
    def width(self) -> Fraction:
        return self.hi - self.lo


@dataclass(frozen=True)
class DisplayMinimum:
    """A nonproof decimal summary of already-proved positive Arb balls."""

    approximate_lower: float
    box: RationalBox
    ball: arb


@dataclass(frozen=True)
class CertificateResult:
    precision_bits: int
    box_count: int
    low_regime_boxes: int
    high_regime_boxes: int
    digest: str
    display_minima: Mapping[str, DisplayMinimum]


def build_boxes() -> tuple[RationalBox, ...]:
    """Build the exact rational partition, split at rho=1/2."""

    boxes: list[RationalBox] = []
    segments = (
        (LOWER_RHO, SPLIT_RHO, "rho_le_half"),
        (SPLIT_RHO, UPPER_RHO, "rho_ge_half"),
    )
    for start, stop, regime in segments:
        lo = start
        while lo < stop:
            hi = min(lo + MAX_BOX_WIDTH, stop)
            boxes.append(RationalBox(lo, hi, regime))
            lo = hi
    validate_partition(boxes)
    return tuple(boxes)


def validate_partition(boxes: Sequence[RationalBox]) -> None:
    """Prove exact coverage, adjacency, widths, and regime ownership."""

    if len(boxes) != EXPECTED_BOX_COUNT:
        raise VerificationError(
            f"wrong box count: expected {EXPECTED_BOX_COUNT}, got {len(boxes)}"
        )
    if boxes[0].lo != LOWER_RHO or boxes[-1].hi != UPPER_RHO:
        raise VerificationError("box partition has the wrong outer endpoints")
    for index, box in enumerate(boxes):
        if not (Fraction(0) < box.width <= MAX_BOX_WIDTH):
            raise VerificationError(f"invalid exact width in box {index}: {box.width}")
        if index and boxes[index - 1].hi != box.lo:
            raise VerificationError(f"gap or overlap before box {index}")
        if box.eta_regime == "rho_le_half":
            if box.hi > SPLIT_RHO:
                raise VerificationError(f"low-eta box {index} crosses rho=1/2")
        elif box.eta_regime == "rho_ge_half":
            if box.lo < SPLIT_RHO:
                raise VerificationError(f"high-eta box {index} crosses rho=1/2")
        else:
            raise VerificationError(f"unknown eta regime in box {index}")
    low_count = sum(box.eta_regime == "rho_le_half" for box in boxes)
    high_count = sum(box.eta_regime == "rho_ge_half" for box in boxes)
    if (low_count, high_count) != (726, 560):
        raise VerificationError(
            f"wrong split counts: expected (726, 560), got {(low_count, high_count)}"
        )


def arb_of_fraction(value: Fraction) -> arb:
    return arb(fmpq(value.numerator, value.denominator))


def arb_box(box: RationalBox) -> arb:
    """Return an outward Arb ball covering the exact rational box."""

    midpoint = (box.lo + box.hi) / 2
    radius = (box.hi - box.lo) / 2
    enclosure = arb(
        fmpq(midpoint.numerator, midpoint.denominator),
        fmpq(radius.numerator, radius.denominator),
    )
    # These proof checks ensure the rounded Arb representation covers both
    # exact-rational endpoint enclosures.
    if not enclosure.contains(arb_of_fraction(box.lo)):
        raise VerificationError(f"Arb box misses exact lower endpoint {box.lo}")
    if not enclosure.contains(arb_of_fraction(box.hi)):
        raise VerificationError(f"Arb box misses exact upper endpoint {box.hi}")
    return enclosure


def g_one(z: arb, pi: arb) -> arb:
    """Return (sqrt(1-z^2)-z*acos(z))/pi with outward Arb arithmetic."""

    return ((arb(1) - z * z).sqrt() - z * z.acos()) / pi


def evaluate_at_k0(rho: arb, eta_regime: str) -> Mapping[str, arb]:
    """Evaluate all base-face and K-convexity quantities on one rho ball."""

    one = arb(1)
    two = arb(2)
    half = one / two
    k = arb(K0)
    pi = arb.pi()

    if eta_regime == "rho_le_half":
        eta = g_one(half, pi)
    elif eta_regime == "rho_ge_half":
        eta = g_one(rho, pi)
    else:
        raise VerificationError(f"unknown eta regime: {eta_regime}")

    d = two * rho.asin() / pi
    b = two * pi * rho / (one - rho)
    mu = rho * k
    c = b * k
    radius = mu + half
    s = (radius * radius + c).sqrt()
    p = s - radius
    asinh_term = (radius / c.sqrt()).asinh()
    integral = (radius * s + c * asinh_term - radius * radius) / two

    reserve = (
        (mu - half) * (k * eta - one)
        + (d / two) * (mu - arb(3) / two) * (mu - half)
        - (one + d) * integral
        - arb(8) * (mu + half) / (arb(15) * mu.sqrt())
    )

    integral_k = rho * p + (b / two) * asinh_term
    reserve_k = (
        rho * (k * eta - one)
        + (mu - half) * eta
        + d * rho * (mu - one)
        - (one + d) * integral_k
        - two * rho * (two * mu - one) / (arb(15) * mu * mu.sqrt())
    )

    integral_kk = (
        rho * rho * (radius / s - one)
        + rho * b / (two * s)
        + b * (two * rho * k - one) / (arb(8) * k * s)
    )
    integral_kk_bound = arb(3) * b / (arb(4) * k)
    interface_kk = (
        rho * rho * (two * mu - arb(3))
        / (arb(15) * mu * mu * mu.sqrt())
    )
    curvature_floor = (
        two * rho * eta
        + d * rho * rho
        - arb(3) * (one + d) * b / arb(800)
    )
    reserve_kk = (
        two * rho * eta + d * rho * rho
        - (one + d) * integral_kk + interface_kk
    )

    return {
        "eta": eta,
        "b": b,
        "mu": mu,
        "R": radius,
        "S": s,
        "B200": reserve,
        "BK200": reserve_k,
        "F": curvature_floor,
        "I_KK": integral_kk,
        "I_KK_bound": integral_kk_bound,
        "interface_KK": interface_kk,
        "B_KK": reserve_kk,
    }


def _require_positive(name: str, value: arb, box: RationalBox) -> None:
    if not (value > 0):
        raise VerificationError(
            f"could not prove {name}>0 on [{box.lo}, {box.hi}] "
            f"({box.eta_regime}): {value.str(30)}"
        )


def _require_less(name: str, left: arb, right: arb, box: RationalBox) -> None:
    if not (left < right):
        raise VerificationError(
            f"could not prove {name} on [{box.lo}, {box.hi}] "
            f"({box.eta_regime}): left={left.str(30)}, right={right.str(30)}"
        )


def verify_boxes(boxes: Iterable[RationalBox]) -> Mapping[str, DisplayMinimum]:
    """Apply every outward-Arb wall on every exact rational box."""

    minima: Dict[str, DisplayMinimum] = {}
    for box in boxes:
        rho = arb_box(box)
        values = evaluate_at_k0(rho, box.eta_regime)

        _require_positive("1-rho", arb(1) - rho, box)
        _require_positive("mu-3/2", values["mu"] - arb(3) / arb(2), box)
        _require_positive("K*eta-1", arb(K0) * values["eta"] - arb(1), box)
        _require_positive("S-R", values["S"] - values["R"], box)
        _require_positive("R-rho*K", values["R"] - rho * arb(K0), box)
        _require_less(
            "I_KK < 3b/(4K)", values["I_KK"], values["I_KK_bound"], box
        )
        _require_positive("interface_KK", values["interface_KK"], box)
        _require_less("F < B_KK", values["F"], values["B_KK"], box)

        for name in ("B200", "BK200", "F"):
            value = values[name]
            _require_positive(name, value, box)
            # Selection and decimal conversion are never proof decisions.
            approximate_lower = float(value.lower())
            current = minima.get(name)
            if current is None or approximate_lower < current.approximate_lower:
                minima[name] = DisplayMinimum(approximate_lower, box, value)
    return minima


def _fraction_text(value: Fraction) -> str:
    return f"{value.numerator}/{value.denominator}"


def canonical_certificate_bytes(
    boxes: Iterable[RationalBox], precision_bits: int
) -> bytes:
    """Canonical ASCII serialization of the exact finite partition."""

    rows = [
        SCHEMA,
        f"precision_bits={precision_bits}",
        f"K0={K0}",
        f"rho={_fraction_text(LOWER_RHO)},{_fraction_text(UPPER_RHO)}",
        f"split_rho={_fraction_text(SPLIT_RHO)}",
        f"max_box_width={_fraction_text(MAX_BOX_WIDTH)}",
    ]
    rows.extend(
        "box="
        + f"{_fraction_text(box.lo)},{_fraction_text(box.hi)},{box.eta_regime}"
        for box in boxes
    )
    return ("\n".join(rows) + "\n").encode("ascii")


def certificate_digest(boxes: Iterable[RationalBox], precision_bits: int) -> str:
    return hashlib.sha256(
        canonical_certificate_bytes(boxes, precision_bits)
    ).hexdigest()


def run_certificate(precision_bits: int = MIN_PRECISION_BITS) -> CertificateResult:
    if precision_bits < MIN_PRECISION_BITS:
        raise ValueError(
            f"precision must be at least {MIN_PRECISION_BITS} bits, got {precision_bits}"
        )
    ctx.prec = precision_bits
    boxes = build_boxes()
    minima = verify_boxes(boxes)
    low_count = sum(box.eta_regime == "rho_le_half" for box in boxes)
    high_count = len(boxes) - low_count
    return CertificateResult(
        precision_bits=precision_bits,
        box_count=len(boxes),
        low_regime_boxes=low_count,
        high_regime_boxes=high_count,
        digest=certificate_digest(boxes, precision_bits),
        display_minima=minima,
    )


def print_result(result: CertificateResult) -> None:
    print("STANDALONE_AGGREGATE_TAIL PASS")
    print(f"precision_bits={result.precision_bits}")
    print(f"box_count={result.box_count}")
    print(f"low_regime_boxes={result.low_regime_boxes}")
    print(f"high_regime_boxes={result.high_regime_boxes}")
    print("coverage=PASS (exact rational adjacency and endpoints)")
    print("proof_sign_checks=B(rho,200)>0, B_K(rho,200)>0, F(rho)>0")
    print(f"certificate_sha256={result.digest}")
    print("display_only_decimal_lower_bounds (not used for proof):")
    for name in ("B200", "BK200", "F"):
        minimum = result.display_minima[name]
        box = minimum.box
        display = minimum.ball.lower().str(16, radius=False)
        print(
            f"  {name}: {display} on intended rational box "
            f"[{_fraction_text(box.lo)}, {_fraction_text(box.hi)}]"
        )


def main(argv: Sequence[str] | None = None) -> int:
    parser = argparse.ArgumentParser(description=__doc__)
    parser.add_argument(
        "--precision",
        type=int,
        default=MIN_PRECISION_BITS,
        help=f"Arb midpoint precision in bits (minimum {MIN_PRECISION_BITS})",
    )
    args = parser.parse_args(argv)
    try:
        result = run_certificate(args.precision)
    except (VerificationError, ValueError) as exc:
        print(f"STANDALONE_AGGREGATE_TAIL FAIL: {exc}")
        return 1
    print_result(result)
    return 0


if __name__ == "__main__":
    raise SystemExit(main())
\end{lstlisting}

\section{External inputs and verification boundary}
\label{app:external-boundary}

The proof above is self-contained with respect to every shell-specific
spectral reduction, weighted count, endpoint estimate, regional subtraction,
fixed-channel variational comparison, seam assignment, and certificate
predicate.  It uses the following conventional external results, each only
in the scope stated where it enters the proof:
\begin{enumerate}
  \item standard spherical-harmonic decomposition, regular
        Sturm--Liouville theory, and the classical Bessel identities collected
        in \cite{DLMF};
  \item the uniform one-variable Bessel-phase enclosure of
        \cite{FLPSphase}, together with the explicitly quoted floor-sum and
        turning-point inequalities of \cite{FLPSballs,FLPSannuli};
  \item Lorch's strict lower bound for the first positive zero of
        \(J_\nu\), in precisely the half-integer specializations derived in
        the text \cite{Lorch1993}; and
  \item outward midpoint-radius interval arithmetic as implemented by Arb
        \cite{Johansson2017}.  The mathematical proof predicates, rational
        partitions, precision gates, coverage rules, strict-wall handling,
        and deterministic regeneration algorithm are all printed in the
        manuscript.  Decimal displays are never proof predicates.
\end{enumerate}

The computer-assisted lemmas are conditional only on the correctness of the
small trusted arithmetic kernel that implements exact rational arithmetic and
outward Arb elementary functions.  The leaf and box arrays are deterministic
outputs of the printed algorithms, not additional mathematical assumptions.
Independent replay should nevertheless use a separately built implementation
or a second interval library before external publication.

\begin{thebibliography}{9}

\bibitem{FLPSballs}
N.~Filonov, M.~Levitin, I.~Polterovich, and D.~A.~Sher,
\newblock P\'olya's conjecture for Euclidean balls,
\newblock \emph{Invent. Math.} \textbf{234} (2023), 129--169.
\newblock \href{https://doi.org/10.1007/s00222-023-01198-1}{doi:10.1007/s00222-023-01198-1}.

\bibitem{FLPSphase}
N.~Filonov, M.~Levitin, I.~Polterovich, and D.~A.~Sher,
\newblock Uniform enclosures for the phase and zeros of Bessel functions and
their derivatives,
\newblock \emph{SIAM J. Math. Anal.} \textbf{56} (2024), no.~6, 7644--7682.
\newblock \href{https://doi.org/10.1137/24M1642032}{doi:10.1137/24M1642032}.

\bibitem{FLPSannuli}
N.~Filonov, M.~Levitin, I.~Polterovich, and D.~A.~Sher,
\newblock P\'olya's conjecture for Dirichlet eigenvalues of annuli,
\newblock \emph{J. Lond. Math. Soc.} \textbf{113} (2026), no.~2, e70425.
\newblock \href{https://doi.org/10.1112/jlms.70425}{doi:10.1112/jlms.70425}.

\bibitem{Lorch1993}
L.~Lorch,
\newblock Some inequalities for the first positive zeros of Bessel
functions,
\newblock \emph{SIAM J. Math. Anal.} \textbf{24} (1993), no.~3, 814--823.
\newblock \href{https://doi.org/10.1137/0524050}{doi:10.1137/0524050}.

\bibitem{DLMF}
NIST Digital Library of Mathematical Functions,
\newblock Chapter 10: Bessel functions,
\newblock \url{https://dlmf.nist.gov/}, accessed 15 July 2026.

\bibitem{Johansson2017}
F.~Johansson,
\newblock Arb: efficient arbitrary-precision midpoint-radius interval
arithmetic,
\newblock \emph{IEEE Trans. Comput.} \textbf{66} (2017), no.~8, 1281--1292.
\newblock \href{https://doi.org/10.1109/TC.2017.2690633}{doi:10.1109/TC.2017.2690633}.

\end{thebibliography}

\end{document}
